### 2014-11-19 Paper/model0.tex
Added our plan of action

\documentclass{article}
\usepackage{amsmath}
\begin{document}
\def\blw{\boldsymbol{w}}
\def\blf{\boldsymbol{f}}
\def\blphi{\boldsymbol{\phi}}
\renewcommand\phi\varphi

\textbf{Notation:}
\begin{table}[h]
\begin{tabular}{ll}
$N$                   & number of VSO triples (indexed by $i$)                      \\
$F$                   & number of frames (indexed by $f$)                       \\
$V$                   & vocabulary size (indexed by $w$)\footnotemark\\
$\blf$                   & the sequence of frames (one for each triple)        \\
$f_i$                 & $1\leq f_i\leq F$ is the frame assigned to the $i$th triple      \\
$\blw$           & the sequence of VSO triples (this is our data)                               \\
$ w_i$            & $i$th triple                                            \\
$w_i^{(a)}$           & the word with syntactic role $a$ ($a\in\{s,v,o\}$) in the $i$th triple \\
$\blphi$          & sequence probability distributions characterizing frames    \\
$\phi_f$          & probability distributions for frame $f$                  \\
$\phi_f^{(a)}$        & probability distribution for syntactic role $a$ in frame $f$ \\
$C(w,f,a)$          & number of times that $w$ appears in position $a$ in triples assigned to frame $f$\\
\end{tabular}
\end{table}
\footnotetext{We may want to have a separate vocabulary for each syntactic role
($V^{(s)},V^{(v)},V^{(o)}$)... for now lump them all together and make use of 0 counts.}

The generative story for model 0 is
\[
P(\blf,\blw,\blphi|\theta,\beta)
= P(\blf|\theta)P(\blw|\blphi)P(\blphi|\beta)
\]

\begin{align*}
p(f|\theta)      =& \prod_{i=1}^{N}\theta(f_i)\\
p(w|\blphi,\blf) =& \prod_{i=1}^N\prod_{a}^{\{v,s,o\}}\phi_{f_i}^a(w_i^a)\\
                 =& \prod_{f=1}^{F}\prod_{w=1}^{V}\prod_{a}^{\{s,v,o\}}\phi_f^a(w)^{C(w,f,a)}\\
p(\phi|\beta)    =& (\frac{3}{B(\beta)})^K\prod_{f=1}^{F}\prod_{w=1}^{V}\prod_{a}^{\{s,v,o\}}\phi_f^a(w)
\end{align*}

So we have...

\begin{align*}
\prod_{i=1}^{N}\theta(f_i) \times
\prod_{f=1}^{F}\prod_{w=1}^{V}\prod_{a}^{\{s,v,o\}}\phi_f^a(w)^{C(w,f,a)} \times
& (\frac{3}{B(\beta)})^K\prod_{f=1}^{F}\prod_{w=1}^{V}\prod_{a}^{\{s,v,o\}}\phi_f^a(w)\\
= \prod_{i=1}^{N}\theta(f_i) \times
(\frac{3}{B(\beta)})^K
\prod_{f=1}^{F}\prod_{w=1}^{V}\prod_{a}^{\{s,v,o\}}\phi_f^a(w)^{(C(w,f,a) + 1)}
\end{align*}

\begin{align*}
p(\blf,\blw|\theta,\beta) =& \int p(\blf,\blw,\blphi|\theta,\beta) d\phi\\
=& 
\prod_{i=1}^{N}\theta(f_i) \times
\int\prod_{f=1}^{F}\prod_{w=1}^{V}\prod_{a}^{\{s,v,o\}}\phi_f^a(w)^{(C(w,f,a) + 1)}d\phi
\end{align*}

\end{document}

### 2014-11-20 Preprocessing/FilterNGrams.hs
Fix script to use verbargs.

@@ -64,13 +64,13 @@ logLn :: String -> IO ()
 logLn s = do
   time <- fmap show getCurrentTime
   let s' = time ++ "\t" ++ s ++ "\n"
-  appendFile "ParseLog" s'
+  appendFile "log" s'
   putStrLn $ s
 
 processFile :: String -> IO ()
 processFile inF = do
   let outF = inF ++ ".prep"
-  logLn $ "Processing file: " ++ inF 
+  logLn $ "Filtering file: " ++ inF ++ "for VSOs."
   result <- (try $ readFile inF) :: IO (Either SomeException String)
   case result of 
     Left ex -> logLn $ "File " ++ inF ++ " not parsed: " ++ show ex ++ "\n"

### 2014-11-20 Preprocessing/download.sh

@@ -1,4 +1,0 @@
-for i in $(seq -f "%02g" 0 98)
-do
-  wget http://commondatastorage.googleapis.com/books/syntactic-ngrams/eng/triarcs.$i-of-99.gz
-done

### 2014-11-20 Preprocessing/process_all.sh

@@ -1,7 +1,46 @@
-# this can be split into separate scripts to run concurently
-for i in $(seq -f "%02g" 00 98) # by edititng this line
-do
-  gunzip triarcs.$i-of-99.gz --keep
-  ./ParseNGram process triarcs.$i-of-99
-  rm triarcs.$i-of-99
-done
+
+DIR="verbargs"
+function file {
+  printf "$DIR/verbargs.%02g-of-99" $1
+}
+
+# Make the directory for verbargs (if it doesn't exsit)
+if [ ! -d $DIR ]; then mkdir $DIR; fi
+
+# Compile FilterNGram if it doesn't already exist.
+if [ ! -f "FilterNGrams" ]; then ghc FilterNGrams; fi
+
+# Compile ConcatVSO if it doesn't already exist.
+if [ ! -f "ConcatVSO" ]; then ghc FilterNGrams; fi
+
+function process {
+  # Download the .gz if we don't have it already.
+  if [ ! -f "$1.gz" ];
+  then
+    "wget http://ommondatastorage.googleapis.com/books/syntactic-ngrams/eng/$1.gz"
+  fi
+  # Unzip and filter for VSO n-grams
+  gunzip -f --keep "$1.gz" 
+  ./FilterNGrams $1 
+  rm $1 
+}
+
+# Do four of  at a time to speed things up.
+for i in $(seq  0 24); do process $(file $i); done &
+for i in $(seq 25 49); do process $(file $i); done &
+for i in $(seq 50 74); do process $(file $i); done &
+for i in $(seq 75 98); do process $(file $i); done
+wait
+
+# Sort all the resulting VSO files.
+rm -f "filenames.tmp"
+for i in $(seq 0 98); do; printf "$(file $i).prep" >> "filenames.tmp"; done
+echo "Sorting everything into all_VSOs.sorted..."
+sort --output="all_VSOs.sorted" --files0-from=filenames.tmp
+rm "filenames.tmp"
+
+# Concatenate like VSOs
+echo "Concatenating like VSOs in all_VSOs.sorted..."
+echo "$(date -u +"%F %T %Z") Found $(wc -l all_VSOs.sorted) VSOs in the n-grams files" >> log
+./ConcatVSO all_VSOs.sorted
+echo "$(date -u +"%F %T %Z") Found $(wc -l all_VSOs.sorted.concat) unique VSOs." >> log

### 2014-11-20 Preprocessing/sort.sh

@@ -1,7 +1,0 @@
-rm -f "filenames.tmp"
-for i in $(seq -f "%02g" 0 98)
-do
-  printf "triarcs.%s-of-99.prep\0" $i >> "filenames.tmp"
-done
-sort --output="all_VSOs.sorted" --files0-from=filenames.tmp
-rm "filenames.tmp"

### 2014-11-20 Preprocessing/process_all.sh
Fix filename bug.

@@ -34,7 +34,7 @@ wait
 
 # Sort all the resulting VSO files.
 rm -f "filenames.tmp"
-for i in $(seq 0 98); do; printf "$(file $i).prep" >> "filenames.tmp"; done
+for i in $(seq 0 98); do printf "$(file $i).prep\0" >> "filenames.tmp"; done
 echo "Sorting everything into all_VSOs.sorted..."
 sort --output="all_VSOs.sorted" --files0-from=filenames.tmp
 rm "filenames.tmp"

### 2014-11-22 Preprocessing/process_all.sh
Only proces ngram files if they haven't been done.

@@ -20,9 +20,12 @@ function process {
     "wget http://ommondatastorage.googleapis.com/books/syntactic-ngrams/eng/$1.gz"
   fi
   # Unzip and filter for VSO n-grams
-  gunzip -f --keep "$1.gz" 
-  ./FilterNGrams $1 
-  rm $1 
+  if [ ! -f "$1.gz" ];
+  then
+    gunzip -f --keep "$1.prep" 
+    ./FilterNGrams $1 
+  fi
+  rm -f $1 
 }
 
 # Do four of  at a time to speed things up.

### 2014-11-24 model0.py
First attempt at EM implementation.

@@ -1,0 +1,86 @@
+import numpy as np
+from collections import OrderedDict
+
+def em(F, alpha):
+    """
+    Uses EM to induce frames via the model 0 generative story.
+    Arguments:
+    F     - the number of frames to induce
+    alpha - the dirichlet prior for initializing word distributions (alhpa >= 1)
+    Other variables:
+    theta - distribution of frames
+    """
+
+    # load our tuples into temporary lists 
+    # also keep track of all the words it the vocabulary, so we
+    # know what the indexes refer to in the end
+    # TODO: if we end up using index arrays, some of this conversion
+    # to indices should be done in the preprocessing stage.
+    vocab = dict()
+    V = 0 # size of the vocabulary
+    verbs = []; subjects = []; objects = []
+    counts_v = dict(); counts_s = dict(); counts_o = dict();
+    with open("Preprocessing/test.concat") as f:
+        for v,s,o,c,_ in map(lambda x: x.split(' '), f.read().splitlines()):
+            if not v in vocab: vocab[v] = V; V += 1
+            if not s in vocab: vocab[s] = V; V += 1
+            if not o in vocab: vocab[o] = V; V += 1
+            verbs.append(vocab[v])
+            subjects.append(vocab[s])
+            objects.append(vocab[o])
+            c = int(c)
+            if vocab[v] in counts_v: counts_v[vocab[v]] += c
+            else: counts_v[vocab[v]] = c
+            if vocab[s] in counts_s: counts_s[vocab[s]] += c
+            else: counts_s[vocab[s]] = c
+            if vocab[o] in counts_o: counts_o[vocab[o]] += c
+            else: counts_o[vocab[o]] = c
+
+    for w in range(V):
+        if not w in counts_v: counts_v[w] = 0
+        if not w in counts_s: counts_s[w] = 0
+        if not w in counts_o: counts_o[w] = 0
+
+    # make the index arrays
+    N = len(verbs)
+    verbs = np.array(verbs)
+    subjects = np.array(subjects)
+    objects = np.array(objects)
+
+    # initialize theta to the uniform distribution
+    theta = np.ones(F) / F
+
+    # randomly initialize the argument distributions for each frame
+    phi_v = np.random.dirichlet(np.ones(V) * alpha, F).T
[…]

### 2014-11-24 model0.py
Separate vocabs.

@@ -16,58 +16,45 @@ def em(F, alpha):
     # know what the indexes refer to in the end
     # TODO: if we end up using index arrays, some of this conversion
     # to indices should be done in the preprocessing stage.
-    vocab = dict()
-    V = 0 # size of the vocabulary
-    verbs = []; subjects = []; objects = []
-    counts_v = dict(); counts_s = dict(); counts_o = dict();
+    vocab = {'v': {}, 's': {}, 'o': {}}
+    counts = {'v': {}, 's': {}, 'o': {}}
+    V = {'v': 0, 's': 0, 'o': 0}  # size of the vocabulary
+    data = [] 
     with open("Preprocessing/test.concat") as f:
-        for v,s,o,c,_ in map(lambda x: x.split(' '), f.read().splitlines()):
-            if not v in vocab: vocab[v] = V; V += 1
-            if not s in vocab: vocab[s] = V; V += 1
-            if not o in vocab: vocab[o] = V; V += 1
-            verbs.append(vocab[v])
-            subjects.append(vocab[s])
-            objects.append(vocab[o])
-            c = int(c)
-            if vocab[v] in counts_v: counts_v[vocab[v]] += c
-            else: counts_v[vocab[v]] = c
-            if vocab[s] in counts_s: counts_s[vocab[s]] += c
-            else: counts_s[vocab[s]] = c
-            if vocab[o] in counts_o: counts_o[vocab[o]] += c
-            else: counts_o[vocab[o]] = c
-
-    for w in range(V):
-        if not w in counts_v: counts_v[w] = 0
-        if not w in counts_s: counts_s[w] = 0
-        if not w in counts_o: counts_o[w] = 0
+        for v,s,o,c in map(lambda x: x.split(' ')[:-1], f.read().splitlines()):
+            for (w, a) in zip((v,s,o), ('v','s','o')):
+                if not w in vocab[a]: 
+                    vocab[a][w] = V[a]
+                    V[a] += 1
+                if vocab[a][w] in counts[a]: 
+                    counts[a][vocab[a][w]] += int(c)
+                else:
+                    counts[a][vocab[a][w]] = int(c)
+            data.append((vocab['v'][v], vocab['s'][s], vocab['o'][o]))
 
     # make the index arrays
-    N = len(verbs)
-    verbs = np.array(verbs)
[…]

### 2014-11-24 model0.py
Vectorize phi calculations in M-step.

@@ -17,19 +17,18 @@ def em(F, alpha):
     # TODO: if we end up using index arrays, some of this conversion
     # to indices should be done in the preprocessing stage.
     vocab = {'v': {}, 's': {}, 'o': {}}
-    counts = {'v': {}, 's': {}, 'o': {}}
+    counts = {'v': [], 's': [], 'o': []}
     V = {'v': 0, 's': 0, 'o': 0}  # size of the vocabulary
     data = [] 
-    with open("Preprocessing/test.concat") as f:
+    with open("Preprocessing/all_VSOs.sorted.concat") as f:
         for v,s,o,c in map(lambda x: x.split(' ')[:-1], f.read().splitlines()):
             for (w, a) in zip((v,s,o), ('v','s','o')):
                 if not w in vocab[a]: 
                     vocab[a][w] = V[a]
                     V[a] += 1
-                if vocab[a][w] in counts[a]: 
+                    counts[a].append(int(c))
+                else: 
                     counts[a][vocab[a][w]] += int(c)
-                else:
-                    counts[a][vocab[a][w]] = int(c)
             data.append((vocab['v'][v], vocab['s'][s], vocab['o'][o]))
 
     # make the index arrays
@@ -52,22 +51,21 @@ def em(F, alpha):
 
         # M-step
         theta_new = mu.sum(axis=0) 
-        phi_v_new = np.array([[mu.sum(axis=0)[f] * counts['v'][w] for f in range(F)] for w in range(V['v'])])
-        phi_s_new = np.array([[mu.sum(axis=0)[f] * counts['s'][w] for f in range(F)] for w in range(V['s'])])
-        phi_o_new = np.array([[mu.sum(axis=0)[f] * counts['o'][w] for f in range(F)] for w in range(V['o'])])
+        phi_v_new = np.outer(counts['v'], mu.sum(axis=0))
+        phi_s_new = np.outer(counts['s'], mu.sum(axis=0))
+        phi_o_new = np.outer(counts['o'], mu.sum(axis=0))
 
         delta = (abs(np.subtract(phi_v, phi_v_new).sum()) +
-                abs(np.subtract(phi_s, phi_s_new).sum()) +
-                abs(np.subtract(phi_o, phi_o_new).sum()) +
-                abs(np.subtract(theta, theta_new).sum()))
+                 abs(np.subtract(phi_s, phi_s_new).sum()) +
+                 abs(np.subtract(phi_o, phi_o_new).sum()) +
[…]

### 2014-11-24 model0.py
Parametrize phi.

@@ -1,6 +1,8 @@
 import numpy as np
 from collections import OrderedDict
 
+args = ('v','s','o')
+
 def em(F, alpha):
     """
     Uses EM to induce frames via the model 0 generative story.
@@ -16,13 +18,13 @@ def em(F, alpha):
     # know what the indexes refer to in the end
     # TODO: if we end up using index arrays, some of this conversion
     # to indices should be done in the preprocessing stage.
-    vocab = {'v': {}, 's': {}, 'o': {}}
-    counts = {'v': [], 's': [], 'o': []}
-    V = {'v': 0, 's': 0, 'o': 0}  # size of the vocabulary
+    vocab = {a: {} for a in args}
+    counts = {a: [] for a in args}
+    V = {a: 0 for a in args}  # size of the vocabulary
     data = [] 
     with open("Preprocessing/all_VSOs.sorted.concat") as f:
         for v,s,o,c in map(lambda x: x.split(' ')[:-1], f.read().splitlines()):
-            for (w, a) in zip((v,s,o), ('v','s','o')):
+            for (w, a) in zip((v,s,o), args):
                 if not w in vocab[a]: 
                     vocab[a][w] = V[a]
                     V[a] += 1
@@ -40,32 +42,27 @@ def em(F, alpha):
     theta = np.ones(F) / F
 
     # randomly initialize the argument distributions for each frame
-    phi_v = np.random.dirichlet(np.ones(V['v']) * alpha, F).T
-    phi_s = np.random.dirichlet(np.ones(V['s']) * alpha, F).T
-    phi_o = np.random.dirichlet(np.ones(V['o']) * alpha, F).T
-
+    phi = {a: np.random.dirichlet(np.ones(V[a]) * alpha, F).T for a in args}
+    
     mu = np.zeros([N,F])
     while True:
         # E-step
-        mu = phi_v[data[0]] * phi_s[data[1]] * phi_o[data[2]] * theta
+        mu = phi['v'][data[0]] * phi['s'][data[1]] * phi['o'][data[2]] * theta
 
         # M-step
         theta_new = mu.sum(axis=0) 
-        phi_v_new = np.outer(counts['v'], mu.sum(axis=0))
-        phi_s_new = np.outer(counts['s'], mu.sum(axis=0))
-        phi_o_new = np.outer(counts['o'], mu.sum(axis=0))
+        phi_new = {a: np.outer(counts[a], mu.sum(axis=0)) for a in args}
 
[…]

### 2014-12-08 evaluation.py
more sensible testing + plotting

@@ -8,29 +8,36 @@ def frame_coherency(model, data):
     (frame_dists, frame_assign, theta) = model
     results = []
 
+    total = 0
     coh = 0
     N = len(data)
     probs = []
-    probsR= []
-    #    for (v,s,o,c) in data:
+    probsR = []
 
-    #print("************\n frame_assign len: \t%d\n data len: %d\n************\n" %(len(frame_assign),N))
 
     
     probs = [frame_dists[frame_assign[(v,s,o)]]['v'][v]*frame_dists[frame_assign[(v,s,o)]]['s'][s]*frame_dists[frame_assign[(v,s,o)]]['o'][o]*theta[frame_assign[(v,s,o)]] for(v,s,o,_) in data ]
-    print("tst*",end="", flush=True)     
     
     tstD = [(data[rnd.randint(0,N-1)][0],data[i][0],data[i][1],data[i][2]) for i in range(N) ]
-    
-    probsR = [frame_dists[ frame_assign[(v,s,o)]]['v'][rV]*frame_dists[frame_assign[(v,s,o)]]['s'][s]*frame_dists[frame_assign[(v,s,o)]]['o'][o]*theta[frame_assign[(v,s,o)]] for (rV,v,s,o) in tstD]
+
+    for (rV,v,s,o) in tstD:
+         if (rV,s,o) in frame_assign: #frame_assign.has_key():
+             probsR.append(frame_dists[ frame_assign[(rV,s,o)]]['v'][rV]*frame_dists[frame_assign[(rV,s,o)]]['s'][s]* frame_dists[frame_assign[(rV,s,o)]]['o'][o]*theta[frame_assign[(rV,s,o)]])
+         else:
+             probsR.append(0)
+
+
+    #probsR = [frame_dists[ frame_assign[(rV,s,o)]]['v'][rV]*frame_dists[frame_assign[(rV,s,o)]]['s'][s]*frame_dists[frame_assign[(rV,s,o)]]['o'][o]*theta[frame_assign[(rV,s,o)]] for (rV,v,s,o) in tstD]
     #probsR = [np.argmax([frame_dists[frm]['v'][rV]*frame_dists[frm]['s'][s]*frame_dists[frm]['o'][o]*theta[frm] for frm in frame_dists]) for (rV,s,o) in tstD]
-    print("tst*",end="", flush=True)     
+    
     
 
     
     for i in range(N):
+        (_,_,_,c) = data[i]
+        total += c
         if probs[i] > probsR[i]:
[…]

### 2014-12-08 semanticFrameInduction.py

@@ -52,8 +52,8 @@ def runTests(*params):
         frames = params[0]
         alphas = params[1]
     else:
-        frames = [5*(n+1) for n in range(10)]
-        alphas = [1+0.1*n for n in range(11)]
+        frames = [25, 35, 45, 55, 70 ]#10*(n+1) for n in range(100)]
+        alphas = [1.3, 1.5 , 1.7 ]#1+0.1*n for n in range(11)]
 
     print("\n ==================================\n Running tests with: \n frames:\t", frames, "\n alpha's:\t ", alphas, "\n")
 
@@ -62,20 +62,35 @@ def runTests(*params):
     
     results = {(f,a): [] for f in frames for a in alphas}
     resCur = 0
+    result_plots = plt.figure()
+
+    i=1
     for a in alphas:
         for f in frames:
             print( "\n training with: f=%d , a=%f" %(f,a)  )
             model = mod0.em(f,a,*trnData)
             print("\n testing...")
             res = evalu.frame_coherency(model, xvData)
-            results[(f,a)] = [model, res]
+            #results[(f,a)] = [model, res]
             print(" coherency: ", res)
             if res > resCur :
+                bestMod = model
                 resCur = res
                 best = (f,a)
-    
-    print(" Best coherence with: \n frames: ", best[0], "\n alpha: ", best[1] ,"\n coherency on xValidation set: ", results[best][1],
-                  "\n coherency on testset: ", evalu.frame_coherency(model, tstData) )
+            results[(f,a)] = res
+        y = [results[(f,a)] for f in frames ]
+
+        
+        plt.subplot(a+1,1,i)
+        plt.plot(frames,y,marker='o', linestyle='--')
+        plt.ylabel('coherency')
+        plt.xlabel('frames, with alpha=%f' %a)
+        i += 1
+
+    result_plots.tight_layout()
+    result_plots.show()
+#    print(" Best coherence with: \n frames: ", best[0], "\n alpha: ", best[1] ,"\n coherency on xValidation set: ", results[best][1],
+#                  "\n coherency on testset: ", evalu.frame_coherency(model, tstData) )
 
 
 runTests()

### 2014-12-09 semanticFrameInduction.py
save results to file - to be testd

@@ -52,8 +52,8 @@ def runTests(*params):
         frames = params[0]
         alphas = params[1]
     else:
-        frames = [25, 35, 45, 55, 70 ]#10*(n+1) for n in range(100)]
-        alphas = [1.3, 1.5 , 1.7 ]#1+0.1*n for n in range(11)]
+        frames = [25, 35]#, 45, 55, 70 ]#10*(n+1) for n in range(100)]
+        alphas = [1.3, 1.5]# , 1.7 ]#1+0.1*n for n in range(11)]
 
     print("\n ==================================\n Running tests with: \n frames:\t", frames, "\n alpha's:\t ", alphas, "\n")
 
@@ -78,7 +78,13 @@ def runTests(*params):
                 resCur = res
                 best = (f,a)
             results[(f,a)] = res
-        y = [results[(f,a)] for f in frames ]
+
+    with open('results/'+ f +'-'+a + '.pkl', 'wb') as fl:
+        pickle.dump(results, fl, pickle.HIGHEST_PROTOCOL)
+"""
+
+
+            y = [results[(f,a)] for f in frames ]
 
         
         plt.subplot(a+1,1,i)
@@ -91,6 +97,6 @@ def runTests(*params):
     result_plots.show()
 #    print(" Best coherence with: \n frames: ", best[0], "\n alpha: ", best[1] ,"\n coherency on xValidation set: ", results[best][1],
 #                  "\n coherency on testset: ", evalu.frame_coherency(model, tstData) )
-
+"""
 
 runTests()

### 2014-12-09 model0.py
running tests with this settings

@@ -53,7 +53,7 @@ def em(F, alpha, counts, word_to_index, index_to_word, V, data):
 
         # E-step
         mu = phi['v'][data['v']] * phi['s'][data['s']] * phi['o'][data['o']] * theta
-        print("trn* ",end="", flush=True)
+        print(".",end="", flush=True)
         #print_clustering(F, mu)
 
         # M-step

### 2014-12-09 semanticFrameInduction.py

@@ -2,6 +2,7 @@ import model0 as mod0
 import evaluation as evalu
 import numpy as np
 import matplotlib.pyplot as plt
+import pickle
 
 args = ('v','s','o')
 
@@ -52,8 +53,8 @@ def runTests(*params):
         frames = params[0]
         alphas = params[1]
     else:
-        frames = [25, 35]#, 45, 55, 70 ]#10*(n+1) for n in range(100)]
-        alphas = [1.3, 1.5]# , 1.7 ]#1+0.1*n for n in range(11)]
+        frames = [10,15,20,25,30,35,40,45,50,55]#, 45, 55, 70 ]#10*(n+1) for n in range(100)]
+        alphas = [0.2,0.3]# , 1.7 ]#1+0.1*n for n in range(11)]
 
     print("\n ==================================\n Running tests with: \n frames:\t", frames, "\n alpha's:\t ", alphas, "\n")
 
@@ -79,10 +80,12 @@ def runTests(*params):
                 best = (f,a)
             results[(f,a)] = res
 
-    with open('results/'+ f +'-'+a + '.pkl', 'wb') as fl:
+    with open('results/1stFrms_0203alph.pkl', 'wb') as fl:
         pickle.dump(results, fl, pickle.HIGHEST_PROTOCOL)
 """
 
+with open('obj/' + name + '.pkl', 'rb') as f:
+        return pickle.load(f)
 
             y = [results[(f,a)] for f in frames ]
 

### 2014-12-11 Paper/presentation.tex
presentation start

\documentclass{beamer}

\mode<presentation> {

\usetheme{Madrid}

%\setbeamertemplate{footline} % To remove the footer line in all slides uncomment this line
%\setbeamertemplate{footline}[page number] % To replace the footer line in all slides with a simple slide count uncomment this line

%\setbeamertemplate{navigation symbols}{} % To remove the navigation symbols from the bottom of all slides uncomment this line
}

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{tikz}
\usetikzlibrary{bayesnet}

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title[Semantic Frame Induction]{Semantic Frame Induction} % The short title appears at the bottom of every slide, the full title is only on the title page

\author{Eli Drumm, Bill Noble, Jacob Verdegaal} % Your name
\institute[UvA] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
University of Amsterdam \\ % Your institution for the title page
\medskip

}
\date{12/16/14}

\begin{document}

\begin{frame}
\titlepage 
\end{frame}

\begin{frame}
\frametitle{Overview} 
\tableofcontents 
\end{frame}

%----------------------------------------------------------------------------------------
%	PRESENTATION SLIDES
%----------------------------------------------------------------------------------------

%------------------------------------------------
\section{Semantic frames}
%------------------------------------------------

\begin{frame}
  \frametitle{Semantic frames}
  An example\\
  \vspace{10pt}
\begin{tabular}{|l|}
  \hline
  \textit{\small predicate:\normalsize}~~~Transaction\\
  \hline
  \hline
  \textit{\small role 1:\normalsize}~~~ baker\\
  \textit{\small role 2:\normalsize}~~~ Alice\\
  \textit{\small role 3:\normalsize}~~~ bread\\
  \hline
\end{tabular}\\
\vfill
\begin{itemize}
\item Alice buys a bread from the baker
\item The baker sells Alice a bread
  \end{itemize}
\end{frame}

\section{Models}
\begin{frame}
  \frametitle{Model 0 - EM }
  \begin{tikzpicture}
    % Nodes
    \node[obs] (datapoint) {$w_v,w_s,w_o$} ; %
    \node[latent, above=of datapoint] (F) {$f$} ; %
    \node[latent, left=of F] (theta) {$\theta$}; %
    \node[latent, right=of datapoint] (phi) {$\varphi_v,\varphi_s,\varphi_o$}; %
    \edge {theta} {F} ; %
    \edge {F} {datapoint}
    \edge {phi} {datapoint} ; %
    \plate {tuples} { (datapoint) } {$N$}; %
    \plate {} { (tuples) (F) (phi)} {$F$} ; %
  \end{tikzpicture}
\begin{tabbing}
  $N$ \hspace{64pt}\= number of data points\\
  $F$\> number of frames\\
  $\theta$\> distribution over frames\\
  $\varphi_a$ \> distribution per argument $a$ (for frame $f$)\\
  $w_v,w_s,w_o$\> datapoint (verb, subject, object)\\
\end{tabbing}
\end{frame}

\section{Results}
\begin{frame}
  \frametitle{Evaluation metrics}
  \begin{itemize}
  \item Frame coherency: for a datapoint $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random choses verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$  
  \item Frame correctness: for the top 25 most probable verbs per frame $TV$ and framenet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Results EM - model 0}
\end{frame}

\begin{frame}
  \frametitle{Results Gibbs sampling - model 1}
\end{frame}

\end{document}

### 2014-12-12 semanticFrameInduction.py
some results

@@ -53,8 +53,8 @@ def runTests(*params):
         frames = params[0]
         alphas = params[1]
     else:
-        frames = [10,15,20,25,30,35,40,45,50,55]#, 45, 55, 70 ]#10*(n+1) for n in range(100)]
-        alphas = [0.2,0.3]# , 1.7 ]#1+0.1*n for n in range(11)]
+        frames = [60,65,70,75,80,85,90,95,100]#, 45, 55, 70 ]#10*(n+1) for n in range(100)]
+        alphas = [0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1,1.1,1.2,1.3]# , 1.7 ]#1+0.1*n for n in range(11)]
 
     print("\n ==================================\n Running tests with: \n frames:\t", frames, "\n alpha's:\t ", alphas, "\n")
 
@@ -80,8 +80,14 @@ def runTests(*params):
                 best = (f,a)
             results[(f,a)] = res
 
-    with open('results/1stFrms_0203alph.pkl', 'wb') as fl:
+    with open('results/2ndFrms_01-13alph.pkl', 'wb') as fl:
         pickle.dump(results, fl, pickle.HIGHEST_PROTOCOL)
+
+
+def show_results():
+
+    results =get_result_table()
+
 """
 
 with open('obj/' + name + '.pkl', 'rb') as f:
@@ -101,5 +107,23 @@ with open('obj/' + name + '.pkl', 'rb') as f:
 #    print(" Best coherence with: \n frames: ", best[0], "\n alpha: ", best[1] ,"\n coherency on xValidation set: ", results[best][1],
 #                  "\n coherency on testset: ", evalu.frame_coherency(model, tstData) )
 """
+
+def get_result_table():
+
+    files = []
+    files.append('1stFrms_0203alph')
+    files.append('1stFrms_0405alph')
+    files.append('1stFrms_067809alph')
+    files.append('1stFrms_10111213alph')
+    files.append('1stFrms_14-2alph')
+    files.append('2ndFrms_14-2alph')
+
+    results = {}
+    for f in files:
+        with open('results/'+ fl + '.pkl', 'rb') as f:
+            results.update(pickle.load(f))
+    
+    return results 
+    
 
 runTests()

### 2014-12-12 semanticFrameInduction.py
added plotting (not finished)

@@ -3,6 +3,7 @@ import evaluation as evalu
 import numpy as np
 import matplotlib.pyplot as plt
 import pickle
+import collections
 
 args = ('v','s','o')
 
@@ -86,27 +87,33 @@ def runTests(*params):
 
 def show_results():
 
-    results =get_result_table()
+    results = get_result_table()
+    srtRes = collections.OrderedDict(sorted(results.items()))
+    [frames,alphas] = [list(t) for t in zip(*srtRes)]
+ 
+    result_plots = plt.figure()
 
-"""
-
-with open('obj/' + name + '.pkl', 'rb') as f:
-        return pickle.load(f)
-
-            y = [results[(f,a)] for f in frames ]
-
-        
-        plt.subplot(a+1,1,i)
-        plt.plot(frames,y,marker='o', linestyle='--')
+    for a in alphas:
+        y = [results[(f,a)] for f in frames]
+        plt.subplot(2,1,1)
+        plt.plot(frames,y, label=str('alpha=%f'%a))
         plt.ylabel('coherency')
-        plt.xlabel('frames, with alpha=%f' %a)
-        i += 1
+        plt.xlabel('frames')
+        plt.legend(loc=3)
 
-    result_plots.tight_layout()
+    for f in frames:
+        y = [results[(f,a)] for a in alphas]
+        plt.subplot(2,1,2)
+        plt.plot(alphas,y, label=str('frames=%d'%f))
+        plt.ylabel('coherency')
+        plt.xlabel('alphas')
+        plt.legend(loc=3)
+
     result_plots.show()
+
+
 #    print(" Best coherence with: \n frames: ", best[0], "\n alpha: ", best[1] ,"\n coherency on xValidation set: ", results[best][1],
 #                  "\n coherency on testset: ", evalu.frame_coherency(model, tstData) )
-"""
 
 def get_result_table():
 
@@ -116,14 +123,14 @@ def get_result_table():
     files.append('1stFrms_067809alph')
     files.append('1stFrms_10111213alph')
     files.append('1stFrms_14-2alph')
-    files.append('2ndFrms_14-2alph')
+    #files.append('2ndFrms_14-2alph')
 
     results = {}
-    for f in files:
+    for fl in files:
         with open('results/'+ fl + '.pkl', 'rb') as f:
             results.update(pickle.load(f))
     
     return results 
     
 
-runTests()
+#runTests()

### 2014-12-12 Paper/model1GibbsDerivation.tex

\documentclass{article}

\usepackage{amsmath}
\usepackage{tikz}
\usetikzlibrary{bayesnet}

\renewcommand\phi\varphi

\begin{document}

Here is the derivation of Gibbs sampling for Model 1 of O'Connor 2013.
The model is adapted so that we consider all tuples with the same verb as coming
from the same ``document''.
This modification results in some simplification of the model (e.g. there are now
only $\phi$ distributions for subjects and objects as the verb argument is given).
Other than that it is intended to be the same...

Here is the generative story:

\begin{tikzpicture}[]
    \node[obs]                   (w)     {$(w_s,w_o)^v_i$}; %
    \node[latent, left=of w]     (f)     {$f^v$};
    \node[latent, left=of f]     (theta) {$\theta^v$};
    \node[latent, left=of theta] (alpha) {$\alpha$};
    \node[latent, right=of w]    (phi)   {$(\phi_s,\phi_o)^f$};
    \edge {alpha} {theta};
    \edge {theta} {f};
    \edge {f} {w};
    \edge {phi} {w};
    \plate {frames} {(phi)} {$F$};
    \plate {datapoints} {(f) (w)} {$N^v$};
    \plate {verbs} {(f) (w) (datapoints) (theta)} {$V$};
\end{tikzpicture}

\begin{table}[h]
\begin{tabular}{ll}
$V$ & is the verb-vocabulary (equivallent to the number of documents)\\
$F$ & is the number of frames\\
$N^v$ & is the number of data points with verb $v$\\
$(w^s, w^o)^v_i$ & is data point $i$ (with verb (document) = $v$, subject = $w^s$ and object = $w^o$).\\
etc...\\
\end{tabular}
\end{table}

By the independence assumptions built into the model, we have:
\[
P(f,w,\theta,\phi|\alpha,\beta) = P(w|\phi,f) \cdot P(f|\theta) \cdot P(\theta|\alpha) \cdot P(\phi|\beta).
\]

Integrating out the latent distributions, we get:

\[
P(w,f|\alpha,\beta) = \int_\theta P(f|\theta)\cdot P(\theta|\alpha) d\theta \times
                      \int_\phi   P(w|f,\phi)\cdot P(\phi|\beta) d\phi
\]

First look at the first integral...

\begin{align*}
\int_{\theta} P(f|\theta)\cdot P(\theta|\alpha)\ d\theta
    =& \prod_{v=1}^V \int_{\theta^v} P(\theta^v|\alpha), P(f|\alpha)\ d\theta^v\\
    =& \prod_{v=1}^V \int_{\theta^v} P(\theta^v,f^v|\alpha)\ d\theta^v\\
    =& \prod_{v=1}^V DCM_\alpha(f^v)\\
    =& \frac{\Gamma(F\cdot\alpha)}{\Gamma(\alpha)^F} \times
       \frac{\prod_{f=1}^F\Gamma(C^v(f) + \alpha)}{\Gamma(F\cdot\alpha +
       \sum_{f=1}^FC^v(f))}
\end{align*}

Where $C^v(f)$ is the number data points with verb $v$ assigned to frame $f$.

The second integral is trickier, but we can still use DCM (I think?).

\begin{align*}
&\int_{\phi} P(w|f)\cdot P(\phi|\beta)\ d\phi\\
    =& \prod_{k=1}^F\int_{\phi^k} P(\phi^k|\beta)\cdot P(w[k]|f)\ d\phi^k\\
    =& \prod_{k=1}^F\int_{\phi^k_s} P(\phi^k_s|\beta)\cdot P(w_s[k]|f)\ d\phi^k_s
             \times \int_{\phi^k_o} P(\phi^k_o|\beta)\cdot P(w_o[k]|f)\ d\phi^k_o\\
\intertext{Where $w[k]$ is the sequence of data points consiering only those with frame assignment $k$
and $w_s[k]$ is the sequence of subjects from those data points.}
    =& \prod_{k=1}^F DCM_\beta(w_s[k]) \times DCM_\beta(w_o[k])\\
    =& \prod_{k=1}^F \frac{\Gamma(V^s\cdot\beta)}{\Gamma(\beta)^{V^s}}
              \times \frac{\prod_{s=1}^{V^s}\Gamma(C^{w[k]}(s) + \beta)}
                          {\Gamma(V^s\cdot\beta +\sum_{s=1}^{V^s}C^{w[k]}(s))}
              \times \frac{\Gamma(V^o\cdot\beta)}{\Gamma(\beta)^{V^o}}
              \times \frac{\prod_{o=1}^{V^o}\Gamma(C^{w[k]}(o) + \beta)}
                          {\Gamma(V^o\cdot\beta +\sum_{o=1}^{V^o}C^{w[k]}(o))}
\intertext{Where $C^{w[k]}(s)$ is the number of tuples with subject $s$ and frame $k$.}
\end{align*}

Next I want to find
\[
P(f_i = k| f_{-i}, w, \alpha, \beta) 
    = \frac{P(f_{-1}, f_i=k,w|\alpha,\beta)}
           {\sum_{k'=1}^F P(f_{-1}, f_i=k,w|\alpha,\beta)}
\]

This is where I am lost. I know that

\[
P(f,w|\alpha,\beta) = \prod_v^V DCM_\alpha(f^v)\times 
                      \prod_{k=1}^F DCM_\beta(W_s[k])\cdot DCM_\beta(w_o[k])
\]

But I'm not sure how to break this down into the conditional probabilities that I need.

\end{document}

### 2014-12-13 semanticFrameInduction.py
-

@@ -24,7 +24,7 @@ def loadData( dataFile , trainPC, xvalidPC, testPC):
     nXval = 0
     nTst = 0
     
-    # Load the 
+
     
     with open( dataFile) as f:
         for v,s,o,c in map(lambda x: x.split(' ')[:-1], f.read().splitlines()):

### 2014-12-13 model1.py
initial model 1 implementation

@@ -1,0 +1,100 @@
+import numpy as np
+import random
+
+def normalize(array):
+    min_val = array.min()
+    if min_val < 0:
+        array -= min_val 
+    return array / sum(array)
+
+def gibbs(F, alpha, beta, dataFile):
+
+    data = {} # doc -> list of sentences
+    sentence_count = {} # (v,s,o) -> # of observations 
+    doc_count = {} # doc (verb) -> # of sentences in it 
+    doc_frame_count = {} # doc -> frame -> # of sentences in doc assigned to frame
+    frame_assign = {} # (v,s,o) -> frame assignment 
+    frame_count = {} # frame -> # of sentences assigned to it
+    frame_count_v = {} # frame -> verb -> # of verb assigned to frame
+    frame_count_w = {} # frame -> word -> # of words assigned to frame
+    W = set() # number of words (subject + verbs)
+    V = set() # number of verbs (documents)
+
+    # read data from file; place in documents
+    with open(dataFile) as f:
+        for v,s,o,c in map(lambda x: x.split(' ')[:-1], f.read().splitlines()):
+            V.add(v)
+            W.add(s)
+            W.add(o)
+            c = int(c)
+            if v in data:
+                data[v].append((s,o))
+                doc_count[v] += c
+            else:
+                data[v] = [(s,o)]
+                doc_count[v] = c
+            if (v,s,o) in sentence_count:
+                sentence_count[(v,s,o)] += c
+            else:
+                sentence_count[(v,s,o)] = c
+
+    W_count = len(W)
+    V_count = len(V)
+    
+    # initialize frame assignments and related counts
+    frame_count = {f: 0 for f in range(F)}
+    frame_count_v = {f: {v: 0 for v in V} for f in range(F)}
+    frame_count_w = {f: {w: 0 for w in W} for f in range(F)}
+    for v in data:
+        doc_frame_count[v] = {f: 0 for f in range(F)}
+        frame_count_v[v] = 0
+        for (s,o) in data[v]:
+            f = random.randrange(F)
+            c = sentence_count[(v,s,o)]
+            frame_assign[(v,s,o)] = f
+            frame_count[f] += c
+            frame_count_v[f][v] += c
+            frame_count_w[f][s] += c
+            frame_count_w[f][o] += c
+            doc_frame_count[v][f] += c
+
+    def posterior(f, v,s,o):
+        v_term  = ( (beta + frame_count_v[f][v]) 
+                  / (V_count + frame_count[f]) )
[…]

### 2014-12-13 model1.py
remove numpy dependency so for use pypy

@@ -1,11 +1,21 @@
-import numpy as np
 import random
+from itertools import accumulate
 
-def normalize(array):
-    min_val = array.min()
+def normalize(dist):
+    min_val = min(dist) 
     if min_val < 0:
-        array -= min_val 
-    return array / sum(array)
+        dist = [x - min_val for x in dist]
+        #dist -= min_val 
+    normalizer = sum(dist)
+    return [x/normalizer for x in dist]
+
+
+def choose_from_dist(dist):
+    cumulative = list(accumulate(dist))
+    val = random.random()
+    for i in range(len(dist)):
+        if val < cumulative[i]:
+            return i
 
 def gibbs(F, alpha, beta, dataFile):
 
@@ -69,8 +79,7 @@ def gibbs(F, alpha, beta, dataFile):
 
     t = 0
     while True:
-        #print('t =',t,end='\r')
-        print('.')
+        print('t =',t,end='\r')
         t += 1 # #iteration
         for v in data: # iterate through documents (verbs) 
             for (s,o) in data[v]: # iterate through sentences
@@ -83,9 +92,10 @@ def gibbs(F, alpha, beta, dataFile):
                 frame_count_w[f][o] -= c
                 doc_frame_count[v][f] -= c
                 # calculate the posterior for frames
-                dist = normalize(np.array([posterior(f, v,s,o) for f in range(F)]))
+                dist = normalize([posterior(f, v,s,o) for f in range(F)])
                 # assign a new label to the sentence
-                f = np.random.choice(range(F), p=dist)
+                #f = np.random.choice(range(F), p=dist)
+                f = choose_from_dist(dist)
                 # modify counts to reflect (v,s,o)'s new frame
                 frame_count[f] += c
                 frame_count_v[f][v] += c

### 2014-12-14 model1.py
clarifying comments

@@ -17,7 +17,7 @@ def choose_from_dist(dist):
         if val < cumulative[i]:
             return i
 
-def gibbs(F, alpha, beta, dataFile):
+def gibbs(F, alpha, beta, T, dataFile):
 
     data = {} # doc -> list of sentences
     sentence_count = {} # (v,s,o) -> # of observations 
@@ -68,17 +68,21 @@ def gibbs(F, alpha, beta, dataFile):
             frame_count_w[f][o] += c
             doc_frame_count[v][f] += c
 
+    # Calculates the probablitiy that (v,s,o) should be assigned frame f
+    # given the current counts.
     def posterior(f, v,s,o):
+        # how well the verb fits the frame
         v_term  = ( (beta + frame_count_v[f][v]) 
                   / (V_count + frame_count[f]) )
+        # how well the subject & object fit the frame
         so_term = ( (2*beta + frame_count_w[f][s] + frame_count_w[f][o]) 
                   / (W_count + frame_count[f]) )
+        # how likely the frame is in the document (verb) 
         f_term  = ( (alpha + doc_frame_count[v][f])
                   / (F*alpha + sentence_count[(v,s,o)]) )
         return v_term * so_term * f_term
 
-    t = 0
-    while True:
+    for t in range(T):
         print('t =',t,end='\r')
         t += 1 # #iteration
         for v in data: # iterate through documents (verbs) 
@@ -102,9 +106,5 @@ def gibbs(F, alpha, beta, dataFile):
                 frame_count_w[f][s] += c
                 frame_count_w[f][o] += c
                 doc_frame_count[v][f] += c
-        if t == 10: 
-            break
+
     return frame_assign
-
-gibbs(5, .5, .5, 'Preprocessing/all_VSOs.sorted.concat')
-

### 2014-12-15 Paper/presentation.tex
standardize plate diagrams
add EM and Gibbs steps

@@
 \documentclass{beamer}
+
+\usepackage{natbib}
+\bibliographystyle{plain}
+\renewcommand\phi\varphi
 
@@
 \section{Models}
+
 \begin{frame}
   \frametitle{Model 0 - EM }
-  \begin{tikzpicture}
-    % Nodes
-    \node[obs] (datapoint) {$w_v,w_s,w_o$} ; %
-    \node[latent, above=of datapoint] (F) {$f$} ; %
-    \node[latent, left=of F] (theta) {$\theta$}; %
-    \node[latent, right=of datapoint] (phi) {$\varphi_v,\varphi_s,\varphi_o$}; %
-    \edge {theta} {F} ; %
-    \edge {F} {datapoint}
-    \edge {phi} {datapoint} ; %
-    \plate {tuples} { (datapoint) } {$N$}; %
-    \plate {} { (tuples) (F) (phi)} {$F$} ; %
-  \end{tikzpicture}
+  \begin{columns}
+  \column{.5\textwidth}
+    \begin{figure}
+    \input{model0plate.tex}
+    \end{figure}
+  \column{.5\textwidth} 
+  \begin{scriptsize}
   \begin{tabbing}
-  $N$ \hspace{64pt}\= number of data points\\
-  $F$\> number of frames\\
-  $\theta$\> distribution over frames\\
-  $\varphi_a$ \> distribution per argument $a$ (for frame $f$)\\
-  $w_v,w_s,w_o$\> datapoint (verb, subject, object)\\
+    $N$ \hspace{10pt}\= number of data points\\
+    $F$              \> number of frames\\
+    $\theta$         \> distribution over frames\\
+    $\varphi_a$      \> distributions (for each frame) over \\ 
+                     \> vocabulary of argument $a$\\
+    $w_a$            \> datapoint (verb, subject, object)\\
   \end{tabbing}
+  \end{scriptsize}
+  \end{columns}
+\footnotesize{E-Step:}
+\[
+P(f|w_i) = \frac{\prod_a^{\{v,s,o\}}P(w_i^a|\phi_f^a) P(f|\theta)}{\sum_{f'}^F\prod_a^{\{v,s,o\}}P(w_i^a|\phi_{f'}^a)}
+\]
+\footnotesize{M-Step:}
+\begin{columns}
+\column{.5\textwidth}
+\[
+P(f|\theta) = \frac{\sum_{i=1}^N \mu_i(f)}{\sum_{f'=1}^F\sum_{i=1}^N\mu_i(f')}
+\]
+\column{.5\textwidth}
+\[
+P(w|\phi_f^a) = \frac{\sum_{i=1}^N \mu_i(f) C(w,a)}{\sum_{w'=1}^{V^a}\sum_{i=1}^N \mu_i(f) C(w',a)}
+\]
+\end{columns}
+\end{frame}
+
+\begin{frame}
+  \begin{columns}
+  \column{.5\textwidth}
+  \frametitle{Model 1 - Gibbs Sampling}
+  \begin{figure}
+  \input{model1plate.tex}
+  \end{figure}
+  \column{.5\textwidth}
+  \begin{scriptsize}
+  \begin{tabbing}
+    $N$ \hspace{10pt}\= number of data points\\
+    $F$              \> number of frames\\
+    $V$              \> number of documents (= verb vocabulary)\\
+    $\theta$         \> distribution over frames\\
+    $\varphi_a$      \> distributions (for each frame) over \\ 
+                     \> vocabulary of argument $a$\\
+    $w_a$            \> datapoint (verb, subject, object)\\
+    $\beta$          \> hyperprior for $\varphi$ (for each argument)\\
+    $\alpha$         \> hyperprior for $\theta$ \\
+  \end{tabbing}
+  \end{scriptsize}
+  \end{columns}
+\footnotesize{Gibbs:}
+\[
+P(z_{ij} = f| \mathbf{f}_{-ij},\alpha,\beta,w)
+\propto \prod_a^{\{v,s,o\}}\frac{\beta^a + \tilde{C}(f,w_{ij})}{V^a + \tilde{C}(f)}
+        \cdot \frac{\alpha + \tilde{C}(i,f)}{F\alpha+\tilde{C}(i)}
+\]
+\begin{scriptsize}
+  \begin{tabbing}
+    $\tilde{C}(f,w_{ij})$ \hspace{10pt}\= count times $w_{ij}$ is assigned to frame $f$\\
+    $\tilde{C}(f)$                     \> count total data points assigend to $f$\\
+    $\tilde{C}(i,f)$                   \> count sentences in document $i$ assigned to $f$\\
+    $\tilde{C}(i)$                     \> count sentences in document $i$\\ 
+  \end{tabbing}
+  \end{scriptsize}
+
 \end{frame}
@@
 \section{Results}
+
 \begin{frame}
@@
 
+\section{References}
+\begin{frame}[t,allowframebreaks]
+\nocite{*}
+\bibliography{refs.bib}
+\end{frame}
+
 \end{document}

### 2014-12-15 model1.py
merge doc_frame_count and frame_count_v

@@ -22,7 +22,6 @@ def gibbs(F, alpha, beta, T, dataFile):
     data = {} # doc -> list of sentences
     sentence_count = {} # (v,s,o) -> # of observations 
     doc_count = {} # doc (verb) -> # of sentences in it 
-    doc_frame_count = {} # doc -> frame -> # of sentences in doc assigned to frame
     frame_assign = {} # (v,s,o) -> frame assignment 
     frame_count = {} # frame -> # of sentences assigned to it
     frame_count_v = {} # frame -> verb -> # of verb assigned to frame
@@ -56,7 +55,6 @@ def gibbs(F, alpha, beta, T, dataFile):
     frame_count_v = {f: {v: 0 for v in V} for f in range(F)}
     frame_count_w = {f: {w: 0 for w in W} for f in range(F)}
     for v in data:
-        doc_frame_count[v] = {f: 0 for f in range(F)}
         frame_count_v[v] = 0
         for (s,o) in data[v]:
             f = random.randrange(F)
@@ -66,7 +64,6 @@ def gibbs(F, alpha, beta, T, dataFile):
             frame_count_v[f][v] += c
             frame_count_w[f][s] += c
             frame_count_w[f][o] += c
-            doc_frame_count[v][f] += c
 
     # Calculates the probablitiy that (v,s,o) should be assigned frame f
     # given the current counts.
@@ -78,7 +75,7 @@ def gibbs(F, alpha, beta, T, dataFile):
         so_term = ( (2*beta + frame_count_w[f][s] + frame_count_w[f][o]) 
                   / (W_count + frame_count[f]) )
         # how likely the frame is in the document (verb) 
-        f_term  = ( (alpha + doc_frame_count[v][f])
+        f_term  = ( (alpha + frame_count_v[f][v])
                   / (F*alpha + sentence_count[(v,s,o)]) )
         return v_term * so_term * f_term
 
@@ -94,7 +91,6 @@ def gibbs(F, alpha, beta, T, dataFile):
                 frame_count_v[f][v] -= c
                 frame_count_w[f][s] -= c
                 frame_count_w[f][o] -= c
-                doc_frame_count[v][f] -= c
                 # calculate the posterior for frames
                 dist = normalize([posterior(f, v,s,o) for f in range(F)])
                 # assign a new label to the sentence
@@ -105,6 +101,5 @@ def gibbs(F, alpha, beta, T, dataFile):
                 frame_count_v[f][v] += c
[…]

### 2014-12-15 model0.py
split split data

@@ -2,7 +2,7 @@ import numpy as np
 
 args = ('v','s','o')
 
-def em(F, alpha, counts, word_to_index, index_to_word, V, data):
+def em(F, alpha, data):
     """
     Uses EM to induce frames via the model 0 generative story.
 
@@ -33,6 +33,18 @@ def em(F, alpha, counts, word_to_index, index_to_word, V, data):
     frame_assign  - a map from data points (string triples) to frame indetifiers (integers)
     theta         - (as above)
     """
+
+
+    ############ TODO
+    inData = list(data.keys)
+    inCounts = [data[vso] for vso in data]
+
+    data = {a:arra}
+    for (v,s,o) in inData:
+        data
+counts, word_to_index, index_to_word, V, 
+    ###################3
+
 
     N = len(data['v'])
     #print(" *** in mod0: data len: ", N)

### 2014-12-15 semanticFrameInduction.py

@@ -4,8 +4,67 @@ import numpy as np
 import matplotlib.pyplot as plt
 import pickle
 import collections
+import os
+from probfuncs import normalize, cumulative, cum_dist_choice
 
 args = ('v','s','o')
+
+def pruneData( dataFile, verbPC):
+    V = {}
+    data = {}
+    with open(dataFile) as f:
+        # build the verb vocabulary
+        for v,s,o,c in map(lambda x: x.split(' ')[:-1], f.read().splitlines()):
+            c = int(c)
+            if v in V:
+                V[v] += c
+            else: 
+                V[v] = c
+            if (v,s,o) in data:
+                data[(v,s,o)] += c
+            else:
+                data[(v,s,o)] = c
+
+    # determine the cutoff 
+    counts = list(V.values())
+    counts.sort(reverse=True)
+    cutoff = counts[int(len(counts) * verbPC/100)]
+    # pop off the data with low counts
+    for (v,s,o) in data.copy():
+        if V[v] < cutoff:
+            data.pop((v,s,o))
+
+    pickle.dump((verbPC, data), open("allData.pkl", 'wb'))
+
+def splitData( dataFile, verbPC, testPC):
+
+    # load up all the data
+    if not os.path.isfile("allData.pkl"):
+        pruneData(dataFile, verbPC)
+    checkVerbPC, data = pickle.load(open("allData.pkl", 'rb'))
+    if not (checkVerbPC == verbPC):
+        raise ValueError ("Verb frequency cutoffs do not match. Re/move allData.pkl and try again.")
+
+    dataList = [s for s in data]
+    testData = {}
+    for i in range(int(len(data) * testPC/100)): 
+        # create a distribution to sample from
+        countList = [data[s] for s in dataList]
+        dist = cumulative(normalize(countList))
+        # sample the test data subtract it from the training data
+        vso = dataList[cum_dist_choice(dist)]
+        if vso in testData:
+            testData[vso] += 1
+        else:
+            testData[vso] = 1
+        if data[vso] == 1:
+            data.pop(vso)
+            dataList.remove(vso)
+        else: 
+            data[vso] -= 1
+
+    pickle.dump(data, open("trainingData.pkl", 'wb'))
+    pickle.ump(testData, open("testingData.pkl", 'wb'))
 
 
 def loadData( dataFile , trainPC, xvalidPC, testPC):

### 2014-12-15 Paper/presentation.tex
Add ngrams slide.

@@
 %------------------------------------------------
-\section{Semantic frames}
+\section{Semantic Frames}
 %------------------------------------------------
@@
 \begin{frame}
-  \frametitle{Semantic frames}
-  An example\\
+  \frametitle{Semantic Frames}
+  \begin{itemize}
+  \item Frame semantics -- Charles J. Fillmore (1976).
+  \item A semantic frame is ``a description of a type of event, relation, 
+  or entity and the participants in it.'' (Framenet)
+  \item There is no mapping between frames and verbs.
+  \end{itemize}
+  An example:\\
   \vspace{10pt}
@@
 \section{Models}
+
+\begin{frame}
+  \frametitle{Google Syntactic-Ngrams}
+  \begin{itemize}
+  \item A syntactic-ngram is a $k$-word rooted subtree for some sentence. 
+  \item Google ngrams come from a corpus of 3.5 million English books.
+  \item We trimmed the ``verb args'' dataset to consider only subject-verb-object triples (VSO's).
+  \item The dataset contains 1,629,120 unique VSO's with a total of 96,245,401 by count.
+  \item In our final results we may only use the most common \%20 of these...
+  \end{itemize}
+
+\end{frame}
 

### 2014-12-16 model0.py
use weighted_sample routine from the internet -- super fast!

@@ -36,13 +36,13 @@ def em(F, alpha, data):
 
 
     ############ TODO
-    inData = list(data.keys)
-    inCounts = [data[vso] for vso in data]
+    #inData = list(data.keys)
+    #inCounts = [data[vso] for vso in data]
 
-    data = {a:arra}
-    for (v,s,o) in inData:
-        data
-counts, word_to_index, index_to_word, V, 
+    #data = {a:arra}
+    #for (v,s,o) in inData:
+        #data
+#counts, word_to_index, index_to_word, V, 
     ###################3
 
 

### 2014-12-16 semanticFrameInduction.py

@@ -5,11 +5,12 @@ import matplotlib.pyplot as plt
 import pickle
 import collections
 import os
-from probfuncs import normalize, cumulative, cum_dist_choice
+from probfuncs import weighted_sample
 
 args = ('v','s','o')
 
-def pruneData( dataFile, verbPC):
+def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', verbPC=20):
+    print('Pruning to %', verbPC, '... ', end='')
     V = {}
     data = {}
     with open(dataFile) as f:
@@ -29,42 +30,44 @@ def pruneData( dataFile, verbPC):
     counts = list(V.values())
     counts.sort(reverse=True)
     cutoff = counts[int(len(counts) * verbPC/100)]
+    print("The cutoff for verb frequency will be", cutoff)
     # pop off the data with low counts
     for (v,s,o) in data.copy():
         if V[v] < cutoff:
             data.pop((v,s,o))
 
-    pickle.dump((verbPC, data), open("allData.pkl", 'wb'))
+    pickle.dump(data, open("allData.pkl", 'wb'))
+    print('Done.')
 
-def splitData( dataFile, verbPC, testPC):
+def splitData( dataFile='allData.pkl', testPC=10):
+
+    print('Splitting off %', testPC, '...')
 
     # load up all the data
-    if not os.path.isfile("allData.pkl"):
-        pruneData(dataFile, verbPC)
-    checkVerbPC, data = pickle.load(open("allData.pkl", 'rb'))
-    if not (checkVerbPC == verbPC):
-        raise ValueError ("Verb frequency cutoffs do not match. Re/move allData.pkl and try again.")
+    if not os.path.isfile(dataFile):
+        raise ValueError ("must run pruneData first.")
+    data = pickle.load(open(dataFile, 'rb'))
 
+    # make a weighted sample of data
     dataList = [s for s in data]
+    weights = [data[s] for s in dataList]
+    testSize = int(len(data) * testPC/100) 
+    testDataList = weighted_sample(dataList, weights, testSize)
+
+    # put the sample in a good format and adjust the training data counts
     testData = {}
-    for i in range(int(len(data) * testPC/100)): 
-        # create a distribution to sample from
-        countList = [data[s] for s in dataList]
-        dist = cumulative(normalize(countList))
-        # sample the test data subtract it from the training data
-        vso = dataList[cum_dist_choice(dist)]
+    while testDataList:
[…]

### 2014-12-16 model0.py
doing data init

@@ -2,7 +2,7 @@ import numpy as np
 
 args = ('v','s','o')
 
-def em(F, alpha, data):
+def em(F, alpha, inData):
     """
     Uses EM to induce frames via the model 0 generative story.
 
@@ -33,16 +33,29 @@ def em(F, alpha, data):
     frame_assign  - a map from data points (string triples) to frame indetifiers (integers)
     theta         - (as above)
     """
+    data = {a: [] for a in args}
+    counts = []
+    word_to_index = {a: {} for a in args}
+    index_to_word = {a: {} for a in args}
+    V =  {a: 0 for a in args}
+    for ws in inData:
+        for (a, w) in zip(args, w):
+            if not w in word_to_index[a]:
+            data[a].append(w)
+            word_to_index[a][w] = i
+            index_to_word[a][i] = w
+        counts.append(inData[ws])
+    data = {a:np.array(data[a]) for a in args}
 
 
     ############ TODO
-    #inData = list(data.keys)
-    #inCounts = [data[vso] for vso in data]
+    inData = list(data.keys)
+    inCounts = [data[vso] for vso in data]
 
-    #data = {a:arra}
-    #for (v,s,o) in inData:
-        #data
-#counts, word_to_index, index_to_word, V, 
+    data = {a:arra}
+    for (v,s,o) in inData:
+        data
+counts, word_to_index, index_to_word, V, 
     ###################3
 
 

### 2014-12-16 model0.py
Model 0 using generic input.

@@ -33,34 +33,24 @@ def em(F, alpha, inData):
     frame_assign  - a map from data points (string triples) to frame indetifiers (integers)
     theta         - (as above)
     """
+
+    # Put the data in the right format for EM
     data = {a: [] for a in args}
     counts = []
+    V =  {a: 0 for a in args}
     word_to_index = {a: {} for a in args}
     index_to_word = {a: {} for a in args}
-    V =  {a: 0 for a in args}
     for ws in inData:
-        for (a, w) in zip(args, w):
+        for (a, w) in zip(args, ws):
             if not w in word_to_index[a]:
-            data[a].append(w)
-            word_to_index[a][w] = i
-            index_to_word[a][i] = w
+                word_to_index[a][w] = V[a]
+                index_to_word[a][V[a]] = w
+                V[a] += 1
+            data[a].append(word_to_index[a][w])
         counts.append(inData[ws])
     data = {a:np.array(data[a]) for a in args}
+    N = len(counts)
 
-
-    ############ TODO
-    inData = list(data.keys)
-    inCounts = [data[vso] for vso in data]
-
-    data = {a:arra}
-    for (v,s,o) in inData:
-        data
-counts, word_to_index, index_to_word, V, 
-    ###################3
-
-
-    N = len(data['v'])
-    #print(" *** in mod0: data len: ", N)
     # Initialize theta to the uniform distribution.
     theta = np.ones(F) / F
     # Draw from a dirichlet distribution to randomly initialize each frame.
@@ -68,9 +58,8 @@ counts, word_to_index, index_to_word, V,
     # Create the array for storing posterior estimates.
     mu = np.zeros([N,F])
 
-    t = 0
+    t = 0 # iteration
     while True:
-        t += 1 # iteration
 
         # Check that all our distributions still sum to 1.
         assert(is_prob_dist(theta, .01))
@@ -78,8 +67,6 @@ counts, word_to_index, index_to_word, V,
 
         # E-step
         mu = phi['v'][data['v']] * phi['s'][data['s']] * phi['o'][data['o']] * theta
-        print(".",end="", flush=True)
-        #print_clustering(F, mu)
 
         # M-step
         theta_new = mu.sum(axis=0) / mu.sum()
@@ -91,13 +78,14 @@ counts, word_to_index, index_to_word, V,
         # Measure how much the distributions have changed from in the previous step.
[…]

### 2014-12-16 semanticFrameInduction.py
Fix fence post.

@@ -41,7 +41,7 @@ def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', verbPC=20):
 
 def splitData( dataFile='allData.pkl', testPC=10):
 
-    print('Splitting off %', testPC, '...')
+    print('Splitting off %', testPC, ' for training data...')
 
     # load up all the data
     if not os.path.isfile(dataFile):
@@ -58,9 +58,9 @@ def splitData( dataFile='allData.pkl', testPC=10):
     testData = {}
     while testDataList:
         vso = testDataList.pop()
+        data[vso] -= 1
         if vso in testData:
             testData[vso] += 1
-            data[vso] -= 1
             if data[vso] == 0:
                 data.pop(vso)
         else: 
@@ -196,5 +196,8 @@ def get_result_table():
     
 
 #runTests()
+
 pruneData()
 splitData()
+
+#mod0.em(20, 1.5, pickle.load(open('trainingData.pkl', 'rb')))

### 2014-12-16 probfuncs.py
cleaning up

@@ -1,0 +1,37 @@
+from itertools import accumulate
+import random
+import bisect
+from collections import Sequence
+
+def normalize(dist):
+    min_val = min(dist) 
+    if min_val < 0:
+        dist = [x - min_val for x in dist]
+        #dist -= min_val 
+    normalizer = sum(dist)
+    return [x/normalizer for x in dist]
+
+def cumulative(dist):
+    return list(accumulate(dist))
+
+def cum_dist_choice(dist):
+    val = random.random()
+    for i in range(len(dist)):
+        if val < dist[i]:
+            return i
+
+# http://stackoverflow.com/a/13052108/2224317
+def weighted_sample(population, weights, k):
+    return random.sample(WeightedPopulation(population, weights), k)
+
+class WeightedPopulation(Sequence):
+    def __init__(self, population, weights):
+        assert len(population) == len(weights) > 0
+        self.population = population
+        self.cumweights = cumulative(weights)
+    def __len__(self):
+        return self.cumweights[-1]
+    def __getitem__(self, i):
+        if not 0 <= i < len(self):
+            raise IndexError(i)
+        return self.population[bisect.bisect(self.cumweights, i)]

### 2014-12-16 semanticFrameInduction.py

@@ -9,8 +9,8 @@ from probfuncs import weighted_sample
 
 args = ('v','s','o')
 
-def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', verbPC=20):
-    print('Pruning to %', verbPC, '... ', end='')
+def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', cutoffPC=20):
+    print('Pruning to %', cutoffPC, '... ', end='')
     V = {}
     data = {}
     with open(dataFile) as f:
@@ -29,8 +29,8 @@ def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', verbPC=20):
     # determine the cutoff 
     counts = list(V.values())
     counts.sort(reverse=True)
-    cutoff = counts[int(len(counts) * verbPC/100)]
-    print("The cutoff for verb frequency will be", cutoff)
+    cutoff = counts[int(len(counts) * cutoffPC/100)]
+    print("The absolute cutoff for verb frequency will be", cutoff)
     # pop off the data with low counts
     for (v,s,o) in data.copy():
         if V[v] < cutoff:
@@ -39,76 +39,57 @@ def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', verbPC=20):
     pickle.dump(data, open("allData.pkl", 'wb'))
     print('Done.')
 
-def splitData( dataFile='allData.pkl', testPC=10):
-
-    print('Splitting off %', testPC, ' for training data...')
+def splitData( dataFile='allData.pkl', testPC=10, xvPC=20):
 
     # load up all the data
     if not os.path.isfile(dataFile):
         raise ValueError ("must run pruneData first.")
     data = pickle.load(open(dataFile, 'rb'))
+    trainingData = data.copy()
 
     # make a weighted sample of data
     dataList = [s for s in data]
     weights = [data[s] for s in dataList]
-    testSize = int(len(data) * testPC/100) 
-    testDataList = weighted_sample(dataList, weights, testSize)
 
-    # put the sample in a good format and adjust the training data counts
-    testData = {}
-    while testDataList:
-        vso = testDataList.pop()
-        data[vso] -= 1
-        if vso in testData:
-            testData[vso] += 1
-            if data[vso] == 0:
-                data.pop(vso)
-        else: 
-            testData[vso] = 1
+    # genenic function for generating the samples from w/o replacement
+    def sample_from_data(PC): 
+        size = int(len(data) * PC/100) 
[…]

### 2014-12-16 model1.py
Return the right types of things.

@@ -25,7 +25,7 @@ def gibbs(F, alpha, beta, T, dataFile):
     frame_assign = {} # (v,s,o) -> frame assignment 
     frame_count = {} # frame -> # of sentences assigned to it
     frame_count_v = {} # frame -> verb -> # of verb assigned to frame
-    frame_count_w = {} # frame -> word -> # of words assigned to frame
+    frame_count_w = {} # frame -> word -> # of subjects/verbs assigned to frame
     W = set() # number of words (subject + verbs)
     V = set() # number of verbs (documents)
 
@@ -102,4 +102,20 @@ def gibbs(F, alpha, beta, T, dataFile):
                 frame_count_w[f][s] += c
                 frame_count_w[f][o] += c
 
-    return frame_assign
+    # infer the frame prior from assignments
+    theta = normalize([frame_count[f] for f in range(F)])
+    # infer frame's argument distributons from assignments
+    frame_dists = construct_frame_dists(frame_assign, F, sentence_count)
+
+    return (frame_dists, frame_assign, theta)
+
+# questionable.
+def construct_frame_dists(frame_assign, F, counts):
+    totals_in_frame{f: {a: 0 for a in args} for f in range(F)}
+    frame_dists = {f: {a: {} for a in args} for f in range(F)}
+    for ((v,s,o), f) in frame_assign.items():
+        for (a,w) in zip(args, (v,s,o)):
+            if w in frame_dists[f][a]:
+                frame_dists[f][a][w] += counts[(v,s,o)]
+            else:
+                frame_dists[f][a][w] = counts[(v,s,o)]

### 2014-12-16 semanticFrameInduction.py
fixed weighted sample wierdness

@@ -2,10 +2,12 @@ import model0 as mod0
 import evaluation as evalu
 import numpy as np
 import matplotlib.pyplot as plt
+import random as rnd
 import pickle
 import collections
 import os
 from probfuncs import weighted_sample
+import itertools
 
 args = ('v','s','o')
 
@@ -45,35 +47,33 @@ def splitData( dataFile='allData.pkl', testPC=10, xvPC=20):
     if not os.path.isfile(dataFile):
         raise ValueError ("must run pruneData first.")
     data = pickle.load(open(dataFile, 'rb'))
-    trainingData = data.copy()
+ 
+    # put it all in a big long list and shuffle
+    dataList = list(itertools.chain(*([vso for i in range(data[vso])] for vso in data)))
+    rnd.shuffle(dataList)
 
-    # make a weighted sample of data
-    dataList = [s for s in data]
-    weights = [data[s] for s in dataList]
+    print("Splitting off %", testPC, "for testing data and %", xvPC, "for cross verb data...")
+    # split accordingly
+    N = len(dataList)
+    split1 = int(N*testPC/100)
+    split2 = split1 + int(N*xvPC/100)
+    print("Total of ", N, "items. 0 to", split1, "to testList,", split1, "to", split2, "to xvList.")
+    testList       = dataList[:split1]
+    xvList         = dataList[split1:split2]
+    trainingList   = dataList[split2:]
 
-    # genenic function for generating the samples from w/o replacement
-    def sample_from_data(PC): 
-        size = int(len(data) * PC/100) 
-        sampleList = weighted_sample(dataList, weights, size)
-
-        # put the sample in a good format and adjust the data counts
-        sampleData = {}
-        while sampleList:
-            vso = sampleList.pop()
-            trainingData[vso] -= 1
-            if vso in sampleData: 
-                sampleData[vso] += 1
-                if trainingData[vso] == 0:
-                    trainingData.pop(vso)
-            else: 
-                sampleData[vso] = 1
-        return sampleData
-
-    # generate both samples
-    print('Splitting off %', testPC, ' for training data...')
-    testData = sample_from_data(testPC)
-    print('Splitting off %', xvPC, ' for cross verb data...')
-    xvData   = sample_from_data(xvPC)
+    # make the lists into multisets
+    def to_multiset(bigList):
+        multiset = {}
+        for item in bigList:
[…]

### 2014-12-16 semanticFrameInduction.py
comments for safety

@@ -178,7 +178,7 @@ def get_result_table():
     return results 
     
 
-pruneData()
-splitData()
+#pruneData()
+#splitData()
 #runTests()
 

### 2014-12-16 model1.py
fix bug

@@ -95,7 +95,7 @@ def gibbs(F, alpha, beta, T, dataFile):
 
 # questionable.
 def construct_frame_dists(frame_assign, F, counts):
-    totals_in_frame{f: {a: 0 for a in args} for f in range(F)}
+    totals_in_frame = {f: {a: 0 for a in args} for f in range(F)}
     frame_dists = {f: {a: {} for a in args} for f in range(F)}
     for ((v,s,o), f) in frame_assign.items():
         for (a,w) in zip(args, (v,s,o)):

### 2014-12-16 model1.py
fix gibbs inputs

@@ -1,10 +1,10 @@
 import random
 from probfuncs import normalize, cumulative, cum_dist_choice
 
-def gibbs(F, alpha, beta, T, dataFile):
+def gibbs(F, alpha, beta, T, inData):
 
     data = {} # doc -> list of sentences
-    sentence_count = {} # (v,s,o) -> # of observations 
+    sentence_count = inData # (v,s,o) -> # of observations 
     doc_count = {} # doc (verb) -> # of sentences in it 
     frame_assign = {} # (v,s,o) -> frame assignment 
     frame_count = {} # frame -> # of sentences assigned to it
@@ -13,23 +13,16 @@ def gibbs(F, alpha, beta, T, dataFile):
     W = set() # number of words (subject + verbs)
     V = set() # number of verbs (documents)
 
-    # read data from file; place in documents
-    with open(dataFile) as f:
-        for v,s,o,c in map(lambda x: x.split(' ')[:-1], f.read().splitlines()):
-            V.add(v)
-            W.add(s)
-            W.add(o)
-            c = int(c)
-            if v in data:
-                data[v].append((s,o))
-                doc_count[v] += c
-            else:
-                data[v] = [(s,o)]
-                doc_count[v] = c
-            if (v,s,o) in sentence_count:
-                sentence_count[(v,s,o)] += c
-            else:
-                sentence_count[(v,s,o)] = c
+    for ((v,s,o),c) in sentence_count.items():
+        V.add(v)
+        W.add(s)
+        W.add(o)
+        if v in data:
+            data[v].append((s,o))
+            doc_count[v] += c
+        else:
+            data[v] = [(s,o)]
+            doc_count[v] = c
 
     W_count = len(W)
     V_count = len(V)

### 2014-12-16 model1.py
added args

@@ -1,6 +1,8 @@
 import random
 from probfuncs import normalize, cumulative, cum_dist_choice
 
+args = ('v', 's', 'o')
+
 def gibbs(F, alpha, beta, T, inData):
 
     data = {} # doc -> list of sentences
@@ -57,7 +59,7 @@ def gibbs(F, alpha, beta, T, inData):
         return v_term * so_term * f_term
 
     for t in range(T):
-        print('t =',t,end='\r')
+        print('t =',t,'of',T,end='\r')
         t += 1 # #iteration
         for v in data: # iterate through documents (verbs) 
             for (s,o) in data[v]: # iterate through sentences
@@ -71,7 +73,6 @@ def gibbs(F, alpha, beta, T, inData):
                 # calculate the posterior for frames
                 dist = cumulative(normalize([posterior(f, v,s,o) for f in range(F)]))
                 # assign a new label to the sentence
-                #f = np.random.choice(range(F), p=dist)
                 f = cum_dist_choice(dist)
                 # modify counts to reflect (v,s,o)'s new frame
                 frame_count[f] += c

### 2014-12-16 semanticFrameInduction.py
also consider cutoffs for nouns; default to %2

@@ -11,9 +11,10 @@ import itertools
 
 args = ('v','s','o')
 
-def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', cutoffPC=20):
+def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', cutoffPC=2):
     print('Pruning to %', cutoffPC, '... ', end='')
-    V = {}
+    V  = {}
+    SO = {}
     data = {}
     with open(dataFile) as f:
         # build the verb vocabulary
@@ -23,19 +24,34 @@ def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', cutoffPC=20):
                 V[v] += c
             else: 
                 V[v] = c
+            if s in SO:
+                SO[s] += c
+            else:
+                SO[s] = c
+            if o in SO:
+                SO[o] += c
+            else:
+                SO[o] = c
             if (v,s,o) in data:
                 data[(v,s,o)] += c
             else:
                 data[(v,s,o)] = c
 
-    # determine the cutoff 
-    counts = list(V.values())
-    counts.sort(reverse=True)
-    cutoff = counts[int(len(counts) * cutoffPC/100)]
-    print("The absolute cutoff for verb frequency will be", cutoff)
+    # determine the cutoffs
+    countsV = list(V.values())
+    countsV.sort(reverse=True)
+
+    countsSO = list(SO.values())
+    countsSO.sort(reverse=True)
+
+    cutoffV = countsV[int(len(countsV) * cutoffPC/100)-1]
+    cutoffSO = countsSO[int(len(countsSO) * cutoffPC/100)-1]
+
+    print("The absolute cutoff for verb frequency will be", cutoffV)
+    print("The absolute cutoff for subject/object frequency will be", cutoffSO)
     # pop off the data with low counts
     for (v,s,o) in data.copy():
-        if V[v] < cutoff:
+        if V[v] < cutoffV or SO[s] < cutoffSO or SO[o] < cutoffSO:
             data.pop((v,s,o))
 
     pickle.dump(data, open("allData.pkl", 'wb'))
@@ -178,7 +194,7 @@ def get_result_table():
     return results 
     
 
-#pruneData()
-#splitData()
+pruneData()
+splitData()
 #runTests()
 

### 2014-12-17 model1.py
Actually return frame_dists...

@@ -97,3 +97,4 @@ def construct_frame_dists(frame_assign, F, counts):
                 frame_dists[f][a][w] += counts[(v,s,o)]
             else:
                 frame_dists[f][a][w] = counts[(v,s,o)]
+    return frame_dists

### 2014-12-17 model1.py
don't forget to normalize

@@ -83,12 +83,12 @@ def gibbs(F, alpha, beta, T, inData):
     # infer the frame prior from assignments
     theta = normalize([frame_count[f] for f in range(F)])
     # infer frame's argument distributons from assignments
-    frame_dists = construct_frame_dists(frame_assign, F, sentence_count)
+    frame_dists = construct_frame_dists(frame_assign, F, sentence_count, frame_count)
 
     return (frame_dists, frame_assign, theta)
 
 # questionable.
-def construct_frame_dists(frame_assign, F, counts):
+def construct_frame_dists(frame_assign, F, counts, frame_count):
     totals_in_frame = {f: {a: 0 for a in args} for f in range(F)}
     frame_dists = {f: {a: {} for a in args} for f in range(F)}
     for ((v,s,o), f) in frame_assign.items():
@@ -97,4 +97,9 @@ def construct_frame_dists(frame_assign, F, counts):
                 frame_dists[f][a][w] += counts[(v,s,o)]
             else:
                 frame_dists[f][a][w] = counts[(v,s,o)]
+    # normalize
+    for f in frame_dists:
+        for a in args:
+            for w in frame_dists[f][a]:
+                frame_dists[f][a][w] /= frame_count[f]
     return frame_dists

### 2014-12-17 evaluation.py
printing top words

@@ -3,6 +3,33 @@ import model0 as mod0
 import random as rnd
 import matplotlib.pyplot as pp
 
+args = ('v','s','o')
+
+def frames_by_frequency(frame_dists):
+
+    frame_freq = {f: {a:list(frame_dists[f][a].items()) for a in args} for f in frame_dists}
+    for f in frame_freq:
+        for a in args:
+            frame_freq[f][a].sort(key=lambda x: x[1], reverse=True)
+    return frame_freq
+
+
+def show_most_common(frame_freq, top=25):
+
+    for f in frame_freq:
+        print('----------- frame', f,'-------------')
+        print('verbs\t\tsubjects\tobjects')
+        for i in range(top):
+            for a in args:
+                if len(frame_freq[f][a][i][0]) >= 8:
+                    tabs = '\t'
+                else: 
+                    tabs = '\t\t'
+                print(frame_freq[f][a][i][0], end=tabs)
+            print()
+        print()
+
+
 def frame_coherency(model, data):
 
     (frame_dists, frame_assign, theta) = model

### 2014-12-17 semanticFrameInduction.py
extra prune

@@ -8,6 +8,7 @@ import collections
 import os
 from probfuncs import weighted_sample
 import itertools
+from operator import itemgetter
 
 args = ('v','s','o')
 
@@ -54,9 +55,18 @@ def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', cutoffPC=2):
         if V[v] < cutoffV or SO[s] < cutoffSO or SO[o] < cutoffSO:
             data.pop((v,s,o))
 
+
+    data = pruneData2(data, 25)
+    print("datapoints (after prune2) :  ", len(data), "first item:", next (iter (data.items())))
+    
     pickle.dump(data, open("allData.pkl", 'wb'))
     print('Done.')
 
+def pruneData2(data, PC):
+    print("datapoints (before prune2): ", len(data), "first item:", next (iter (data.items())))
+    return dict(sorted(data.items(), key=itemgetter(1))[int(len(data)*((100-PC)/100)):])
+
+     
 def splitData( dataFile='allData.pkl', testPC=10, xvPC=20):
 
     # load up all the data
@@ -194,7 +204,7 @@ def get_result_table():
     return results 
     
 
-pruneData()
-splitData()
+#pruneData()
+#splitData()
 #runTests()
 

### 2014-12-17 semanticFrameInduction.py
use the %1.5 cutoffs

@@ -11,7 +11,7 @@ import itertools
 
 args = ('v','s','o')
 
-def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', cutoffPC=2):
+def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', cutoffPC=1.5):
     print('Pruning to %', cutoffPC, '... ', end='')
     V  = {}
     SO = {}

### 2014-12-17 evaluation.py
Better formatting.

@@ -18,14 +18,16 @@ def show_most_common(frame_freq, top=25):
 
     for f in frame_freq:
         print('----------- frame', f,'-------------')
-        print('verbs\t\tsubjects\tobjects')
+        print('verbs\t\t\tsubjects\t\tobjects')
         for i in range(top):
             for a in args:
-                if len(frame_freq[f][a][i][0]) >= 8:
-                    tabs = '\t'
-                else: 
-                    tabs = '\t\t'
-                print(frame_freq[f][a][i][0], end=tabs)
+                try:
+                    tablen = ((7 + len(frame_freq[f][a][i][0])) // 8)
+                except IndexError:
+                    print(end='\t\t\t')
+                    continue
+                tabs = '\t' if tablen >= 2 else '\t\t'
+                print("%.4f"%frame_freq[f][a][i][1], frame_freq[f][a][i][0], end=tabs)
             print()
         print()
 

### 2014-12-17 model1.py
Fix bug where frames didn't receive their new assignments.

@@ -74,6 +74,7 @@ def gibbs(F, alpha, beta, T, inData):
                 dist = cumulative(normalize([posterior(f, v,s,o) for f in range(F)]))
                 # assign a new label to the sentence
                 f = cum_dist_choice(dist)
+                frame_assign[(v,s,o)] = f
                 # modify counts to reflect (v,s,o)'s new frame
                 frame_count[f] += c
                 frame_count_v[f][v] += c

### 2014-12-17 semanticFrameInduction.py
Give more information about pruning.

@@ -12,8 +12,8 @@ from operator import itemgetter
 
 args = ('v','s','o')
 
-def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', cutoffPC=1.5):
-    print('Pruning to %', cutoffPC, '... ', end='')
+def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', cutoffV_PC=1.5, cutoffSO_PC=1.5):
+    print('Pruning verbs to %', cutoffV_PC, 'subject/objects to %', cutoffSO_PC, '... ', end='')
     V  = {}
     SO = {}
     data = {}
@@ -37,6 +37,8 @@ def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', cutoffPC=1.5):
                 data[(v,s,o)] += c
             else:
                 data[(v,s,o)] = c
+    uniqueVSOs = len(data)
+    totalVSOs = sum(data.values())
 
     # determine the cutoffs
     countsV = list(V.values())
@@ -45,8 +47,11 @@ def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', cutoffPC=1.5):
     countsSO = list(SO.values())
     countsSO.sort(reverse=True)
 
-    cutoffV = countsV[int(len(countsV) * cutoffPC/100)-1]
-    cutoffSO = countsSO[int(len(countsSO) * cutoffPC/100)-1]
+    vocabV = int(len(countsV) * cutoffV_PC/100)
+    vocabSO = int(len(countsSO) * cutoffSO_PC/100)
+
+    cutoffV = countsV[vocabV-1]
+    cutoffSO = countsSO[vocabSO-1]
 
     print("The absolute cutoff for verb frequency will be", cutoffV)
     print("The absolute cutoff for subject/object frequency will be", cutoffSO)
@@ -55,9 +60,10 @@ def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', cutoffPC=1.5):
         if V[v] < cutoffV or SO[s] < cutoffSO or SO[o] < cutoffSO:
             data.pop((v,s,o))
 
+    print("There verb vocabulary is", vocabV, ". The subject/object vocabulary is", vocabSO)
+    print("The pruned data is %", (100 * len(data) / uniqueVSOs), "of the original by unique VSOs")
+    print("and it is %", (100 * sum(data.values()) / totalVSOs), "of the original by total counts.")
 
-    data = pruneData2(data, 25)
[…]

### 2014-12-18 gibbs_c.c
gibbs c function, with python wrapper

@@ -1,0 +1,112 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <time.h>
+
+enum {
+    VERB,
+    SUBJ,
+    OBJ,
+    COUNT,
+    FRAME,
+    M 
+};
+
+long random_weighted(double *weights, int len) {
+    double r = (double)rand() / (double)RAND_MAX;
+    double sum = 0;
+    for (int i = 0; i < len; i++) {
+        sum += weights[i];
+    }
+    double total = 0;
+    for (int i = 0; i < len; i++) {
+        total += weights[i] / sum; 
+        if (r < total) {
+            return i;
+        }
+    }
+}
+
+
+void gibbs(void *data_void, int F, int T, double alpha, double beta,
+        long N, long V, long W) {
+        
+
+    srand(time(NULL));
+
+
+    long *data = (long *) data_void;
+    long *frame_count = calloc(F, sizeof(long));
+    long *doc_count = calloc(V, sizeof(long));
+    long **frame_count_v = calloc(F, sizeof(long*));
+    long **frame_count_w = calloc(F, sizeof(long*));
+    double *posterior = calloc(F, sizeof(double));
+
+    for (int f = 0; f < F; f ++) {
+        frame_count_v[f] = calloc(V, sizeof(long));
+        frame_count_w[f] = calloc(W, sizeof(long));
+    }
+
+    for (int i = 0; i < N; i++) {
+        long v = data[M*i + VERB];
+        long s = data[M*i + SUBJ];
+        long o = data[M*i + OBJ];
+        long c = data[M*i + COUNT];
+        long f = data[M*i + FRAME];
+        frame_count[f] += c;
+        doc_count[v] += c;
+        frame_count_v[f][v] += c;
+        frame_count_w[f][s] += c;
+        frame_count_w[f][o] += c;
+    }
+
+    for (int t = 0; t < T; t++) {
+        printf("Iteration %d of %d.\n", t, T);
+        for (int i = 0; i < N; i++) {
+
+            long v = data[M*i + VERB];
+            long s = data[M*i + SUBJ];
+            long o = data[M*i + OBJ];
+            long c = data[M*i + COUNT];
+            long f = data[M*i + FRAME];
+            /*printf("here %d %lu %lu %lu %lu %lu\n", i, v,s,o,c,f);*/
+
+            // modify counts to exclude data point i
+            frame_count[f] -= c;
+            frame_count_v[f][v] -= c;
[…]

### 2014-12-18 model1_c_wrapper.py

@@ -1,0 +1,78 @@
+import numpy as np
+import ctypes
+from random import randrange
+from probfuncs import normalize
+
+gibbs_c = ctypes.CDLL('./gibbs_c.so').gibbs
+
+args = ('v', 's', 'o')
+
+def gibbs(F, alpha, beta, T, inData):
+
+    sentence_count = inData
+    N = len(inData)
+
+    # build translation maps
+    V = 0
+    verb_to_index = {}
+    index_to_verb = {}
+    W = 0
+    word_to_index = {}
+    index_to_word = {}
+    for (v,s,o) in inData:
+        if not v in verb_to_index:
+            verb_to_index[v] = V
+            index_to_verb[V] = v
+            V += 1
+        if not s in word_to_index:
+            word_to_index[s] = W
+            index_to_word[W] = s
+            W += 1
+        if not o in word_to_index:
+            word_to_index[o] = W
+            index_to_word[W] = o
+            W += 1
+
+    # turn the data into an array
+    arrData = np.array([[verb_to_index[v],word_to_index[s],word_to_index[o],
+        c, randrange(F)] for ((v,s,o),c) in inData.items()], dtype=np.long)
+
+
+    gibbs_c(ctypes.c_void_p(arrData.ctypes.data), ctypes.c_int(F), ctypes.c_int(T),
+            ctypes.c_double(alpha), ctypes.c_double(beta),
+            ctypes.c_long(N), ctypes.c_long(V), ctypes.c_long(W))
+
+    frame_assign = {}
+    frame_count = {f: 0 for f in range(F)}
+    for (v, s, o, c, f) in arrData:
+        v = index_to_verb[v]
+        s = index_to_word[s]
+        o = index_to_word[o]
+        assert sentence_count[(v,s,o)] == c # sanity check
+        frame_assign[(v,s,o)] = f
+        frame_count[f] += c
+    
+    # infer the frame prior from assignments
+    theta = normalize([frame_count[f] for f in range(F)])
+    # infer frame's argument distributons from assignments
+    frame_dists = construct_frame_dists(frame_assign, F, sentence_count, frame_count)
+
+    return (frame_dists, frame_assign, theta)
+
+# questionable.
+def construct_frame_dists(frame_assign, F, counts, frame_count):
+    totals_in_frame = {f: {a: 0 for a in args} for f in range(F)}
+    frame_dists = {f: {a: {} for a in args} for f in range(F)}
[…]

### 2014-12-18 gibbs_c.c
Save all samples (minus burn in).
TODO: write functions for converting the samples to assignments
(take the mode?) and to frame distributions (something smarter?).

@@ -1,0 +1,129 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <time.h>
+#inc
+
+
+enum {
+    VERB,
+    SUBJ,
+    OBJ,
+    COUNT,
+    FRAME,
+    M 
+};
+
+
+long random_weighted(double *weights, int len) {
+    double r = (double)rand() / (double)RAND_MAX;
+    double sum = 0;
+    for (int i = 0; i < len; i++) {
+        sum += weights[i];
+    }
+    double total = 0;
+    for (int i = 0; i < len; i++) {
+        total += weights[i] / sum; 
+        if (r < total) {
+            if (i >= len) { // check if this is the source of the segfault
+                printf("frame = %d\n", i);
+                printf("dist = ");
+                for (int j = 0; j < len; j++) {
+                    printf("%f ", weights[j]);
+                }
+                printf("\nsum = %f, total = %f, r = %f\n", sum, total, r);
+            }
+            return i;
+        }
+    }
+}
+
+
+void gibbs(void *data_void, void *sample_void, 
+        long N, long V, long W, int F, int T, 
+        double alpha, double beta, int(burnIn)) {
+        
+    srand(time(NULL));
+
+    printf("%d", INT_MAX);
+
+    long *data = (long *) data_void;
+    int *sample = (int *) sample_void;
+    long *frame_count = calloc(F, sizeof(long));
+    long *doc_count = calloc(V, sizeof(long));
+    long **frame_count_v = calloc(F, sizeof(long*));
+    long **frame_count_w = calloc(F, sizeof(long*));
+    double *posterior = calloc(F, sizeof(double));
+
+    for (int f = 0; f < F; f ++) {
+        frame_count_v[f] = calloc(V, sizeof(long));
+        frame_count_w[f] = calloc(W, sizeof(long));
+    }
+
+    for (int i = 0; i < N; i++) {
+        long v = data[M*i + VERB];
+        long s = data[M*i + SUBJ];
+        long o = data[M*i + OBJ];
+        long c = data[M*i + COUNT];
+        long f = data[M*i + FRAME];
+        frame_count[f] += c;
+        doc_count[v] += c;
+        frame_count_v[f][v] += c;
+        frame_count_w[f][s] += c;
+        frame_count_w[f][o] += c;
+    }
+
+    for (int t = 0; t < T; t++) {
+        printf("Iteration %d of %d.\n", t, T);
[…]

### 2014-12-18 model1.py

@@ -3,7 +3,7 @@ from probfuncs import normalize, cumulative, cum_dist_choice
 
 args = ('v', 's', 'o')
 
-def gibbs(F, alpha, beta, T, inData):
+def gibbs(F, alpha, beta, T, burnIn, inData):
 
     data = {} # doc -> list of sentences
     sentence_count = inData # (v,s,o) -> # of observations 
@@ -58,9 +58,10 @@ def gibbs(F, alpha, beta, T, inData):
                   / (F*alpha + sentence_count[(v,s,o)]) )
         return v_term * so_term * f_term
 
+    samples = {(v,s,o): {f: 0 for f in range(F)} for (v,s,o) in sentence_count}
+    
     for t in range(T):
         print('t =',t,'of',T,end='\r')
-        t += 1 # #iteration
         for v in data: # iterate through documents (verbs) 
             for (s,o) in data[v]: # iterate through sentences
                 c = sentence_count[(v,s,o)]
@@ -75,32 +76,12 @@ def gibbs(F, alpha, beta, T, inData):
                 # assign a new label to the sentence
                 f = cum_dist_choice(dist)
                 frame_assign[(v,s,o)] = f
+                if t > burnIn:
+                    samples[(v,s,o)][f] += 1
                 # modify counts to reflect (v,s,o)'s new frame
                 frame_count[f] += c
                 frame_count_v[f][v] += c
                 frame_count_w[f][s] += c
                 frame_count_w[f][o] += c
 
-    # infer the frame prior from assignments
-    theta = normalize([frame_count[f] for f in range(F)])
-    # infer frame's argument distributons from assignments
-    frame_dists = construct_frame_dists(frame_assign, F, sentence_count, frame_count)
-
-    return (frame_dists, frame_assign, theta)
-
-# questionable.
-def construct_frame_dists(frame_assign, F, counts, frame_count):
-    totals_in_frame = {f: {a: 0 for a in args} for f in range(F)}
-    frame_dists = {f: {a: {} for a in args} for f in range(F)}
-    for ((v,s,o), f) in frame_assign.items():
-        for (a,w) in zip(args, (v,s,o)):
-            if w in frame_dists[f][a]:
-                frame_dists[f][a][w] += counts[(v,s,o)]
-            else:
-                frame_dists[f][a][w] = counts[(v,s,o)]
-    # normalize
-    for f in frame_dists:
-        for a in args:
-            for w in frame_dists[f][a]:
[…]

### 2014-12-18 model1_c_wrapper.py

@@ -1,0 +1,45 @@
+import numpy as np
+import ctypes
+from random import randrange
+from probfuncs import normalize
+
+gibbs_c = ctypes.CDLL('./gibbs_c.so').gibbs
+
+args = ('v', 's', 'o')
+
+def gibbs(F, alpha, beta, T, burnIn, data):
+
+    listData = list(data.items())
+    N = len(data)
+
+    V = 0
+    verb_to_index = {}
+    W = 0
+    word_to_index = {}
+    for (v,s,o) in data:
+        if not v in verb_to_index:
+            verb_to_index[v] = V
+            V += 1
+        if not s in word_to_index:
+            word_to_index[s] = W
+            W += 1
+        if not o in word_to_index:
+            word_to_index[o] = W
+            W += 1
+
+    # turn the data into an array
+    arrData = np.array([[verb_to_index[v],word_to_index[s],word_to_index[o],
+        c, randrange(F)] for ((v,s,o),c) in listData], dtype=np.long)
+
+    # set up the array to storte the samples in
+    arrSamples = np.array([[0 for t in range(F)] for _ in range(N)], dtype=np.int)
+
+    gibbs_c(ctypes.c_void_p(arrData.ctypes.data), ctypes.c_void_p(arrSamples.ctypes.data),
+            ctypes.c_long(N), ctypes.c_long(V), ctypes.c_long(W), ctypes.c_int(F), ctypes.c_int(T),
+            ctypes.c_double(alpha), ctypes.c_double(beta), ctypes.c_int(burnIn))
+
+    samples = {(v,s,o): {f: int(arrSamples[i][f]) for f in range(F)} 
+            for i, ((v,s,o),_) in enumerate(listData)}
+
+    return samples 
+

### 2014-12-19 gibbs_c.c
Ignore latex stuff.

@@ -21,28 +21,20 @@ long random_weighted(double *weights, int len) {
     for (int i = 0; i < len; i++) {
         total += weights[i] / sum; 
         if (r < total) {
-            if (i >= len) { // check if this is the source of the segfault
-                printf("frame = %d\n", i);
-                printf("dist = ");
-                for (int j = 0; j < len; j++) {
-                    printf("%f ", weights[j]);
-                }
-                printf("\nsum = %f, total = %f, r = %f\n", sum, total, r);
-            }
             return i;
         }
     }
 }
 
 
-void gibbs(void *data_void, void *sample_void, 
+void gibbs(void *data_void, void *samples_void, 
         long N, long V, long W, int F, int T, 
         double alpha, double beta, int burnIn ) {
         
     srand(time(NULL));
 
     long *data = (long *) data_void;
-    int *sample = (int *) sample_void;
+    long *samples = (long *) samples_void;
 
     long *frame_count = calloc(F, sizeof(long));
     long *doc_count = calloc(V, sizeof(long));
@@ -69,7 +61,8 @@ void gibbs(void *data_void, void *sample_void,
     }
 
     for (int t = 0; t < T; t++) {
-        printf("Iteration %d of %d.\n", t, T);
+        int changes = 0;
+        printf("Iteration %d of %d. ", t+1, T);
         for (int i = 0; i < N; i++) {
 
             long v = data[M*i + VERB];
@@ -77,7 +70,6 @@ void gibbs(void *data_void, void *sample_void,
             long o = data[M*i + OBJ];
             long c = data[M*i + COUNT];
             long f = data[M*i + FRAME];
-            /*printf("here %d %lu %lu %lu %lu %lu\n", i, v,s,o,c,f);*/
 
             // modify counts to exclude data point i
             frame_count[f] -= c;
@@ -95,23 +87,29 @@ void gibbs(void *data_void, void *sample_void,
                                  / (F*alpha + c) );
                 posterior[f] = v_term * so_term * f_term;
             }
+
             // assign the new frame randomly
-            f = random_weighted(posterior, F);
-            data[M*i + FRAME] = f;
+            int f_new = random_weighted(posterior, F);
+            if (f != f_new) changes +=1;
+            if (f_new >= F) {
+               printf("Error: frame out of range.\n");
+               return;
+            }
+            data[M*i + FRAME] = f_new;
             // record the sample
             if (t >= burnIn) {
[…]

### 2014-12-19 model1_c_wrapper.py

@@ -1,7 +1,7 @@
 import numpy as np
 import ctypes
 from random import randrange
-from probfuncs import normalize
+import csv
 
 gibbs_c = ctypes.CDLL('./gibbs_c.so').gibbs
 
@@ -37,7 +37,7 @@ def gibbs(F, alpha, beta, T, burnIn, sentence_count):
         sentence_count[(v,s,o)], randrange(F)] for (v,s,o) in sentence_count], dtype=np.long)
 
     # set up the array to storte the samples in
-    arrSamples = np.zeros((N,F), dtype=np.int)
+    arrSamples = np.zeros((N,F), dtype=np.long)
 
     gibbs_c(ctypes.c_void_p(arrData.ctypes.data), ctypes.c_void_p(arrSamples.ctypes.data),
             ctypes.c_long(N), ctypes.c_long(V), ctypes.c_long(W), ctypes.c_int(F), ctypes.c_int(T),
@@ -49,6 +49,22 @@ def gibbs(F, alpha, beta, T, burnIn, sentence_count):
         s = index_to_word[arrData[i][1]]
         o = index_to_word[arrData[i][2]]
         samples[(v,s,o)] = list(arrSamples[i])
+        if any(x > T for x in arrSamples[i]):
+            print((v,s,o), arrSamples[i])
 
     return samples 
+
+def save_samples(samples, filename):
+    with open(filename, 'w', newline='') as csvfile:
+        writer = csv.writer(csvfile, delimiter='\t', quoting=csv.QUOTE_NONE)
+        for (v,s,o) in samples:
+            writer.writerow([v,s,o] + samples[(v,s,o)])
+
+def read_samples(filename):
+    samples = {}
+    with open(filename, newline='') as csvfile:
+        reader = csv.reader(csvfile, delimiter='\t', quoting=csv.QUOTE_NONE)
+        for row in reader:
+            samples[tuple(row[:3])] = [int(c) for c in row[3:]]
+    return samples
 

### 2014-12-20 Paper/paper.tex
start of paper

\documentclass[11pt,twocolumn]{scrartcl}

\usepackage{natbib}
\bibliographystyle{plain}

\author{
    Verdegaal Jacob \\
    \texttt{jacob.verdegaal@student.uva.nl}
    \and
    Drumm, Eli\\
    \texttt{etd@dte.li}
    \and
    Noble, Bill\\
    \texttt{winobes@gmail.com}
}

\title{Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams}

\renewcommand\phi\varphi

\begin{document}

\maketitle

\begin{abstract}
This is the abstract which we will write.
\end{abstract}

\section{Introduction}
Here we provide some background information about what are semantic frames and 
what it menas to induce them and stuff like that.

\section{Related Work}
Here we talk mostly about the O'Connor paper \cite{oconnor2013} and the Rooth 
paper \cite{rooth1999}.

\section{Induction Models}
\subsection{Model 0}
\subsection{Model 1}

\section{Data}
\subsection{Google Syntactic-ngrams}
Here we talk a bit about the syntactic n-grams and all that \cite{ngrams2013}.
\subsection{Pruning}

\section{Experiments}

\section{Results}

\section{Discussion}

\section{Future Work}

\section{Conclusion}

\bibliography{refs.bib}
\end{document}

### 2014-12-20 evaluation.py

@@ -7,28 +7,36 @@ args = ('v','s','o')
 
 def frames_by_frequency(frame_dists):
 
-    frame_freq = {f: {a:list(frame_dists[f][a].items()) for a in args} for f in frame_dists}
+    frame_freq = {f: list(frame_dists[f].items()) for f in frame_dists}
     for f in frame_freq:
-        for a in args:
-            frame_freq[f][a].sort(key=lambda x: x[1], reverse=True)
+        frame_freq[f].sort(key=lambda x: x[1], reverse=True)
     return frame_freq
 
+def show_most_common(frame_dists_v, frame_dists_w, top=25):
 
-def show_most_common(frame_freq, top=25):
+    frame_freq_v = frames_by_frequency(frame_dists_v)
+    frame_freq_w = frames_by_frequency(frame_dists_w)
 
-    for f in frame_freq:
+    stopwords = ['it', 'you', 'them', 'him', 'he', 'i', 'they', 'we', 'me', 'us', 'she', 'her', 'me'] 
+
+    for f in frame_freq_v:
         print('----------- frame', f,'-------------')
-        print('verbs\t\t\tsubjects\t\tobjects')
+        print('verbs\t\t\tsubjects/objects')
+        j = 0
         for i in range(top):
-            for a in args:
-                try:
-                    tablen = ((7 + len(frame_freq[f][a][i][0])) // 8)
-                except IndexError:
-                    print(end='\t\t\t')
-                    continue
+            if frame_freq_v[f][i][1] < 0.001:
+                print(end='\t\t\t')
+            else:
+                tablen = ((7 + len(frame_freq_v[f][i][0])) // 8)
                 tabs = '\t' if tablen >= 2 else '\t\t'
-                print("%.4f"%frame_freq[f][a][i][1], frame_freq[f][a][i][0], end=tabs)
+                print("%.4f"%frame_freq_v[f][i][1], frame_freq_v[f][i][0], end=tabs)
+            while frame_freq_w[f][j][0] in stopwords:
+                j += 1
+            tablen = ((7 + len(frame_freq_w[f][j][0])) // 8)
+            tabs = '\t' if tablen >= 2 else '\t\t'
+            print("%.4f"%frame_freq_w[f][j][1], frame_freq_w[f][j][0], end=tabs)
             print()
+            j += 1
         print()
 
 

### 2014-12-20 gibbs_c.c

@@ -34,7 +34,7 @@ void gibbs(void *data_void, void *samples_void,
     srand(time(NULL));
 
     long *data = (long *) data_void;
-    long *samples = (long *) samples_void;
+    int *samples = (int *) samples_void;
 
     long *frame_count = calloc(F, sizeof(long));
     long *doc_count = calloc(V, sizeof(long));
@@ -107,7 +107,7 @@ void gibbs(void *data_void, void *samples_void,
             frame_count_w[f_new][s] += c;
             frame_count_w[f_new][o] += c;
         }
-        printf("Had %i of %i VSOs change frame.\n", changes, N);
+        printf("Had %d of %lu VSOs change frame.\n", changes, N);
     }
 
     for (int f = 0; f < F; f++) {

### 2014-12-20 model1_c_wrapper.py

@@ -2,6 +2,7 @@ import numpy as np
 import ctypes
 from random import randrange
 import csv
+from probfuncs import increment
 
 gibbs_c = ctypes.CDLL('./gibbs_c.so').gibbs
 
@@ -33,28 +34,78 @@ def gibbs(F, alpha, beta, T, burnIn, sentence_count):
             W += 1
 
     # turn the data into an array
-    arrData = np.array([[verb_to_index[v],word_to_index[s],word_to_index[o],
+    data = np.array([[verb_to_index[v],word_to_index[s],word_to_index[o],
         sentence_count[(v,s,o)], randrange(F)] for (v,s,o) in sentence_count], dtype=np.long)
+   
+    # aliases of the array columns
+    verbs    = data[:,0]
+    subjects = data[:,1]
+    objects  = data[:,2]
+    counts   = data[:,3]
 
-    # set up the array to storte the samples in
-    arrSamples = np.zeros((N,F), dtype=np.long)
+    # set up the array to store the samples in
+    samples = np.zeros((N,F), dtype=np.int32)
 
-    gibbs_c(ctypes.c_void_p(arrData.ctypes.data), ctypes.c_void_p(arrSamples.ctypes.data),
+    gibbs_c(ctypes.c_void_p(data.ctypes.data), ctypes.c_void_p(samples.ctypes.data),
             ctypes.c_long(N), ctypes.c_long(V), ctypes.c_long(W), ctypes.c_int(F), ctypes.c_int(T),
             ctypes.c_double(alpha), ctypes.c_double(beta), ctypes.c_int(burnIn))
+   
+    samples *= counts.reshape((N,1))
+    frameTotals = samples.sum(axis=0)
 
-    samples = {}
-    for i in range(N):
-        v = index_to_verb[arrData[i][0]]
-        s = index_to_word[arrData[i][1]]
-        o = index_to_word[arrData[i][2]]
-        samples[(v,s,o)] = list(arrSamples[i])
-        if any(x > T for x in arrSamples[i]):
-            print((v,s,o), arrSamples[i])
+    verbDists =  np.zeros((V, F))
+    verbDists += np.apply_along_axis(lambda x: np.bincount(verbs, x, minlength=V), 0, samples)
+    verbDists /= frameTotals
 
-    return samples 
+    wordDists =  np.zeros((W, F))
+    wordDists += np.apply_along_axis(lambda x: np.bincount(subjects, x, minlength=W), 0, samples)
[…]

### 2014-12-20 probfuncs.py

@@ -35,3 +35,12 @@ class WeightedPopulation(Sequence):
         if not 0 <= i < len(self):
             raise IndexError(i)
         return self.population[bisect.bisect(self.cumweights, i)]
+
+def increment(counter, value, amount=1):
+    if value in counter:
+        counter[value] += amount
+    else:
+        counter[value] = amount
+
+def is_dist(distList):
+    return abs(sum(distList) - 1) < .001

### 2014-12-20 semanticFrameInduction.py

@@ -11,8 +11,9 @@ import itertools
 from operator import itemgetter
 
 args = ('v','s','o')
+dataFile = 'Preprocessing/all_VSOs.sorted.concat'
 
-def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', cutoffV_PC=1.5, cutoffSO_PC=1.5):
+def pruneData( dataFile=dataFile, cutoffV_PC=1.5, cutoffSO_PC=1.5):
     print('Pruning verbs to %', cutoffV_PC, 'subject/objects to %', cutoffSO_PC, '... ', end='')
     V  = {}
     SO = {}
@@ -68,9 +69,42 @@ def pruneData( dataFile='Preprocessing/all_VSOs.sorted.concat', cutoffV_PC=1.5, 
     pickle.dump(data, open("allData.pkl", 'wb'))
     print('Done.')
 
-def pruneData2(data, PC):
-    print("datapoints (before prune2): ", len(data), "first item:", next (iter (data.items())))
-    return dict(sorted(data.items(), key=itemgetter(1))[int(len(data)*((100-PC)/100)):])
+def pruneData2( dataFile=dataFile, cutoffV_PC=25, cutoffVSOs=1000):
+    print('Pruning to %', cutoffV_PC, 'of verbs with at most', cutoffVSOs, 'VOSs per verb.')
+    V  = {}
+    data = {}
+    with open(dataFile) as f:
+        # build the verb vocabulary
+        for v,s,o,c in map(lambda x: x.split(' ')[:-1], f.read().splitlines()):
+            c = int(c)
+            if v in V:
+                V[v] += c
+            else: 
+                V[v] = c
+            if (v,s,o) in data:
+                data[(v,s,o)] += c
+            else:
+                data[(v,s,o)] = c
+    uniqueVSOs = len(data)
+    totalVSOs = sum(data.values())
+    countsV = list(V.values())
+    countsV.sort(reverse=True)
+    vocabV = int(len(countsV) * cutoffV_PC/100)
+    cutoffV = countsV[vocabV-1]
+    print("The absolute cutoff for verb frequency will be", cutoffV)
+    print("There size of the verb vocabulary is", vocabV)  
+    dataList = list(data.items())
+    dataList.sort(key=lambda x: x[1], reverse=True)
+    verbVSOs = {v: 0 for v in V}
+    for ((v,s,o),_) in dataList: 
+        if v in V and verbVSOs[v] < 1000:
+            verbVSOs[v] += 1
[…]

### 2014-12-20 Paper/paper.tex
plates
Add stuff from presentation to paper.

@@
-\documentclass[11pt,twocolumn]{scrartcl}
+\documentclass[10pt,twocolumn]{scrartcl}
+
+\usepackage{amsmath}
 
@@
 \bibliographystyle{plain}
+
+\usepackage{tikz}
+\usetikzlibrary{bayesnet}
+
+\renewcommand\phi\varphi
 
@@
 \title{Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams}
-
-\renewcommand\phi\varphi
 
@@
 \section{Induction Models}
-\subsection{Model 0}
-\subsection{Model 1}
+
+\subsection{Model 0: Un-structured Tuples}
+\begin{tabbing}
+    $N$ \hspace{10pt}\= number of data points\\
+    $F$              \> number of frames\\
+    $\theta$         \> distribution over frames\\
+    $\varphi_a$      \> distributions (for each frame) over \\ 
+                     \> vocabulary of argument $a$\\
+    $w_a$            \> datapoint (verb, subject, object)\\
+\end{tabbing}
+E-Step:
+\begin{equation}
+P(f|w_i) = \frac{\prod_a^{\{v,s,o\}}P(w_i^a|\phi_f^a) P(f|\theta)}{\sum_{f'}^F\prod_a^{\{v,s,o\}}P(w_i^a|\phi_{f'}^a)}
+\end{equation}
+M-Step:
+\begin{equation}
+P(f|\theta) = \frac{\sum_{i=1}^N \mu_i(f)}{\sum_{f'=1}^F\sum_{i=1}^N\mu_i(f')}
+\end{equation}
+\begin{equation}
+P(w|\phi_f^a) = \frac{\sum_{i=1}^N \mu_i(f) C(w,a)}{\sum_{w'=1}^{V^a}\sum_{i=1}^N \mu_i(f) C(w',a)}
+\end{equation}
+\begin{tabbing}
+    $n$ \hspace{10pt}\= number of data points\\
+    $f$              \> number of frames\\
+    $v$              \> number of documents (= verb vocabulary)\\
+    $\theta$         \> distribution over frames\\
+    $\varphi_a$      \> distributions (for each frame) over \\ 
+                     \> vocabulary of argument $a$\\
+    $w_a$            \> datapoint (verb, subject, object)\\
+    $\beta$          \> hyperprior for $\varphi$ (for each argument)\\
+    $\alpha$         \> hyperprior for $\theta$ \\
+\end{tabbing}
+
+\begin{figure}
+\input{model0plate.tex}
+\caption{Model 0}
+\end{figure}
+
+\subsection{Model 1: Verb Documents}
+Gibbs:
+\begin{align}
+&p(z_{ij} = f| \mathbf{f}_{-ij},\alpha,\beta,\mathbf{w})\\
+\propto &\prod_a^{\{v,s,o\}}\frac{\beta^a + \tilde{c}(f,w_{ij})}{V^a + \tilde{c}(f)}
+        \cdot \frac{\alpha + \tilde{c}(i,f)}{f\alpha+\tilde{c}(i)}
+\end{align}
+
+\begin{tabbing}
+    $\tilde{c}(f,w_{ij})$ \hspace{10pt}\= times $w_{ij}$ is assigned to frame $f$\\
+    $\tilde{c}(f)$                     \> total data points assigend to $f$\\
+    $\tilde{c}(i,f)$                   \> VSOs in document $i$ assigned to $f$\\
+    $\tilde{c}(i)$                     \> VSOs in document $i$\\ 
+\end{tabbing}
+
+\begin{figure}
+    \input{model1plate.tex}
+    \caption{Model 1}
+\end{figure}
 
 \section{Data}
+
 \subsection{Google Syntactic-ngrams}
 Here we talk a bit about the syntactic n-grams and all that \cite{ngrams2013}.
+\begin{itemize}
+    \item A syntactic-ngram is a $k$-word rooted subtree for some sentence. 
+    \item Google ngrams come from a corpus of 3.5 million English books.
+    \item We trimmed the ``verb args'' dataset to consider only subject-verb-object triples (VSO's).
+    \item The dataset contains 1,629,120 unique VSO's with a total of 96,245,401 by count.
+    \item In our final results we may only use the most common \%20 of these...
+\end{itemize}
+
 \subsection{Pruning}
@@
 \section{Results}
+\subsection{Frame Coherency}
+rame coherency: for a datapoint $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random choses verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$  
+\subsection{Frame Correctness}
+Frame correctness: for the top 25 most probable verbs per frame $TV$ and framenet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
+\subsection{Model 0}
+\subsection{Model 1}
 

### 2014-12-20 gibbs_c.c
calculate s and o terms separately

@@ -80,12 +80,14 @@ void gibbs(void *data_void, void *samples_void,
             // calculate the posterior for frames on this data point
             for (int f = 0; f < F; f++) {
                 double v_term  = ( (beta + frame_count_v[f][v]) 
-                                 / (V + frame_count[f]) );
-                double so_term = ( (2*beta + frame_count_w[f][s] + frame_count_w[f][o])
-                                 / (W + frame_count[f]) );
+                                 / (beta*V + frame_count[f]) );
+                double s_term = ( (beta + frame_count_w[f][s])
+                                 / (beta*W + frame_count[f]) );
+                double o_term = ( (beta + frame_count_w[f][o])
+                                 / (beta*W + frame_count[f]) );
                 double f_term  = ( (alpha + frame_count_v[f][v])
                                  / (F*alpha + c) );
-                posterior[f] = v_term * so_term * f_term;
+                posterior[f] = v_term * s_term * o_term * f_term;
             }
 
             // assign the new frame randomly

### 2014-12-20 model1.py
c wrapper now the only model1

@@ -1,87 +1,120 @@
-import random
-from probfuncs import normalize, cumulative, cum_dist_choice
+import numpy as np
+import ctypes
+from random import randrange
+import csv
+from probfuncs import increment
+
+gibbs_c = ctypes.CDLL('./gibbs_c.so').gibbs
 
 args = ('v', 's', 'o')
 
-def gibbs(F, alpha, beta, T, burnIn, inData):
+def gibbs(F, alpha, beta, T, burnIn, sentence_count):
 
-    data = {} # doc -> list of sentences
-    sentence_count = inData # (v,s,o) -> # of observations 
-    doc_count = {} # doc (verb) -> # of sentences in it 
-    frame_assign = {} # (v,s,o) -> frame assignment 
-    frame_count = {} # frame -> # of sentences assigned to it
-    frame_count_v = {} # frame -> verb -> # of verb assigned to frame
-    frame_count_w = {} # frame -> word -> # of subjects/verbs assigned to frame
-    W = set() # number of words (subject + verbs)
-    V = set() # number of verbs (documents)
+    N = len(sentence_count)
 
-    for ((v,s,o),c) in sentence_count.items():
-        V.add(v)
-        W.add(s)
-        W.add(o)
-        if v in data:
-            data[v].append((s,o))
-            doc_count[v] += c
-        else:
-            data[v] = [(s,o)]
-            doc_count[v] = c
+    # build translation maps
+    V = 0
+    verb_to_index = {}
+    index_to_verb = {}
+    W = 0
+    word_to_index = {}
+    index_to_word = {}
+    for (v,s,o) in sentence_count:
+        if not v in verb_to_index:
+            verb_to_index[v] = V
+            index_to_verb[V] = v
+            V += 1
+        if not s in word_to_index:
+            word_to_index[s] = W
+            index_to_word[W] = s
+            W += 1
+        if not o in word_to_index:
+            word_to_index[o] = W
+            index_to_word[W] = o
+            W += 1
 
-    W_count = len(W)
-    V_count = len(V)
-    
-    # initialize frame assignments and related counts
-    frame_count = {f: 0 for f in range(F)}
-    frame_count_v = {f: {v: 0 for v in V} for f in range(F)}
-    frame_count_w = {f: {w: 0 for w in W} for f in range(F)}
-    for v in data:
-        frame_count_v[v] = 0
-        for (s,o) in data[v]:
-            f = random.randrange(F)
[…]

### 2014-12-20 model1_c_wrapper.py

@@ -1,120 +1,0 @@
-import numpy as np
-import ctypes
-from random import randrange
-import csv
-from probfuncs import increment
-
-gibbs_c = ctypes.CDLL('./gibbs_c.so').gibbs
-
-args = ('v', 's', 'o')
-
-def gibbs(F, alpha, beta, T, burnIn, sentence_count):
-
-    N = len(sentence_count)
-
-    # build translation maps
-    V = 0
-    verb_to_index = {}
-    index_to_verb = {}
-    W = 0
-    word_to_index = {}
-    index_to_word = {}
-    for (v,s,o) in sentence_count:
-        if not v in verb_to_index:
-            verb_to_index[v] = V
-            index_to_verb[V] = v
-            V += 1
-        if not s in word_to_index:
-            word_to_index[s] = W
-            index_to_word[W] = s
-            W += 1
-        if not o in word_to_index:
-            word_to_index[o] = W
-            index_to_word[W] = o
-            W += 1
-
-    # turn the data into an array
-    data = np.array([[verb_to_index[v],word_to_index[s],word_to_index[o],
-        sentence_count[(v,s,o)], randrange(F)] for (v,s,o) in sentence_count], dtype=np.long)
-   
-    # aliases of the array columns
-    verbs    = data[:,0]
-    subjects = data[:,1]
-    objects  = data[:,2]
-    counts   = data[:,3]
-
-    # set up the array to store the samples in
-    samples = np.zeros((N,F), dtype=np.int32)
-
-    gibbs_c(ctypes.c_void_p(data.ctypes.data), ctypes.c_void_p(samples.ctypes.data),
-            ctypes.c_long(N), ctypes.c_long(V), ctypes.c_long(W), ctypes.c_int(F), ctypes.c_int(T),
-            ctypes.c_double(alpha), ctypes.c_double(beta), ctypes.c_int(burnIn))
-   
-    samples *= counts.reshape((N,1))
-    frameTotals = samples.sum(axis=0)
-
-    verbDists =  np.zeros((V, F))
-    verbDists += np.apply_along_axis(lambda x: np.bincount(verbs, x, minlength=V), 0, samples)
-    verbDists /= frameTotals
-
-    wordDists =  np.zeros((W, F))
-    wordDists += np.apply_along_axis(lambda x: np.bincount(subjects, x, minlength=W), 0, samples)
-    wordDists += np.apply_along_axis(lambda x: np.bincount(objects, x, minlength=W), 0, samples)
[…]

### 2014-12-20 runmodel1.py

@@ -1,0 +1,13 @@
+import model1 
+import pickle
+
+data = pickle.load(open('trainingData.pkl', 'rb'))
+F = 100 
+T = 1000
+alpha = 0.50
+beta = 0.50
+burnIn = 50
+filename = 'sample_m1_F'+str(F)+'_alpha'+str(alpha)+'_beta'+str(beta)+'_T'+str(T)+'burnIn'+str(burnIn)+'.pkl'
+print("Running Gibbs for", F, "frames", "with alpha=", alpha, "beta=", beta)
+result = model1.gibbs(F, alpha, beta, T, burnIn, data)
+pickle.dump(result, open(filename, 'wb'))

### 2014-12-20 gibbs_c.c
confirmed source of probability bug; fixed.

@@ -24,6 +24,7 @@ long random_weighted(double *weights, int len) {
             return i;
         }
     }
+    return len - 1;
 }
 
 

### 2014-12-20 Paper/paper.tex
Model 0; start of model 1.

--- 2014-12-20 Paper/paper.tex
@@
-\documentclass[11pt,twocolumn]{scrartcl}
+\documentclass[11pt,twocolumn,DIV=11]{scrartcl}
+
+\usepackage{amsmath}
+\usepackage{framed}
+\usepackage{color}
+\definecolor{shadecolor}{gray}{0.8}
 
 \usepackage{natbib}
-\bibliographystyle{plain}
+\bibliographystyle{apalike}
+
+\usepackage{tikz}
+\usetikzlibrary{bayesnet}
+
+\renewcommand\phi\varphi
+\DeclareMathOperator*{\argmax}{arg\,max}
 
 \author{
-    Verdegaal Jacob \\
+    Verdegaal, Jacob\\
     \texttt{jacob.verdegaal@student.uva.nl}
@@
 
-\renewcommand\phi\varphi
-
 \begin{document}
@@
 \maketitle
-
-\begin{abstract}
-This is the abstract which we will write.
-\end{abstract}
 
@@
 \section{Related Work}
-Here we talk mostly about the O'Connor paper \cite{oconnor2013} and the Rooth 
-paper \cite{rooth1999}.
+Here we talk mostly about the O'Connor paper \citep{oconnor2013} and the Rooth 
+paper \citep{rooth1999}.
 
 \section{Induction Models}
+
+We consider two probabalistic latent-variable models that learn semantic frames
+from verb-subject-object tripples (VSO's).
+The goal of these models is to use th syntactic information give by a VSO to
+infer what kind of event it describes (i.e., to which semantic frame it belongs).
+
 \subsection{Model 0}
+
+The approach models each VSO independenly, without considering any further context.
+Word distributions are completely independent between arguments and accross frames.
+Tuples are clustered according to which frame's three distributions best fit the 
+three arguments.
+
+\begin{figure}[h]
+
+    \begin{snugshade}
+    \scriptsize
+    For each $i = 1..N$:\\
+    \hspace*{15pt} Draw a frame $f \sim \theta$.\\
+    \hspace*{15pt} Draw a verb $v \sim \phi_f^v$\\
+    \hspace*{15pt} Draw a subject $s \sim \phi_f^s$\\
+    \hspace*{15pt} Draw an object $o \sim \phi_f^o$
+    \end{snugshade}
+
+    \input{model0plate.tex}
+
+    \label{gen0}
+    \caption{Model 0 generative story}
+
+\end{figure}
+
+Model 0 is based on one originally proposed in \citet{rooth1999}, which 
+considers noun-verb pairs. Following \citet{oconnor2013}, we expand the model
+to use the limited syntax of VSOs.
+
+The generative story (fig. \ref{gen0}) gives us the following joint probability:
+\begin{align*}
+&P(\mathbf{f},\mathbf{w}|\phi,\theta) 
+  = P(\mathbf{f}|\theta)P(\mathbf{w}|\phi)\\
+  =& \prod_{i=1}^{N}\big[\theta(f_i) \prod_a^{\{v,s,o\}}\phi_{f_i}^a(w_i^a)\big]
+\end{align*}
+
+Therefore, the incomplete log-likelihood (i.e., where the sequence of frames
+is hidden) that we want to maximize is as follows:
+\[
+L(\theta,\phi) = \sum_{i=1}^N\big[\log \sum_{f_i=1}^F\theta(f_i)\prod_{a}^{\{v,s,o\}}\phi_{f_i}^a(w^a_i)\big]
+\]
+
+Expectation maximization can be used to maximize this likelihood.
+First we use the current estimates for $\theta$ and $\phi$ to infer a 
+distribution over possible choices of frame. This is the E-step.
+
+\begin{align}
+\mu_i(f) =& P(f_i=f, w_i|\phi,\theta)\nonumber\\
+=& \frac{\theta(f)\prod_a^{\{v,s,o\}}\phi_f^a(w^a_i)}
+                {\sum_{f'=1}^F\theta(f)\prod_a^{\{v,s,o\}}\phi_f^a(w^a_i)}\label{E}
+\end{align}
+
+Then in the M-step, we find $\theta$ and $\phi$ that maximize the expectation of
+the complete likelihood. In particular, we want to maximize
+
+\begin{align*}
+&E_\mu\big[\sum_{i=1}^N\log P(w_i,f_i|\theta,\phi) =\\
+=& \sum_{i=1}^N\sum_{f=1}^F\mu_i(f)\log\Big[\theta(f)\prod_a^{\{v,s,o\}}\phi_f^a(w_i^a)\Big]\\
+=& \sum_{i=1}^N\sum_{f=1}^F\mu_i(f)\log\theta(f)\\
++& \sum_a^{\{v,s,o\}} \sum_{i=1}^N\sum_{f=1}^F\mu_i(f)\log \phi_f^a(w_i^a)
+\end{align*}
+
+Thus the problem is reduced to maximizing each of the terms in the sum above. Fortunately
+these have closed for solutions using lagrangian multipliers.
+
+\begin{align}
+&\argmax_{\theta(f)}\sum_{i=1}^N\sum_{f=1}^F\mu_i(f)\log\theta(f)\nonumber\\
+&= \frac{\sum_{i=1}^N\mu_i(f)}{\sum_{f'}^F\sum_{i=1}^N\mu_i(f)}
+\end{align}
+
+and
+
+\begin{align}
+&\argmax_{\phi^a(w)}\sum_{i=1}^N\sum_{f=1}^F\mu_i(f)\log \phi_f^a(w_i,a)\nonumber\\
+&= \frac{\sum_{i=1}^N \mu_i(f)\,c(w^a)}{\sum_{w'=1}^{V^a}\sum_{i=1}^N \mu_i(f)\,c(w',a)}
+\end{align}
+
+Where $c(w,a)$ indicates the number of times word $w$ is observed as argument $a$.
+
 \subsection{Model 1}
 
+As we know from topic modeling, it is the nature of documents that they contain 
+sentences with related semantic content. Therefore, it is reasonable to assume 
+that semantic frames are not uniformly distributed within documents. Taking 
+advantage of this assumption, we can break drop model 0's assumption of independence 
+between tuples.
+
+\begin{figure}
+
+    \begin{snugshade}
+    \scriptsize
+    For each frame $f=1..F$:\\
+    \hspace*{15pt} For each argument $a\in\{v,s,o\}$:\\
+    \hspace*{30pt} Draw a distribution $\phi_f^a\sim Dirichlet(\beta)$\\
+    For each document $d=1..D$:\\
+    \hspace*{15pt} Draw a distrbution $\theta_d \sim Dirichlet(\alpha)$\\
+    \hspace*{30pt} For each $i = 1..N^d$:\\
+    \hspace*{30pt} Draw a frame $f \sim \theta^d$.\\
+    \hspace*{30pt} Draw a verb $v \sim \phi_f^v$\\
+    \hspace*{30pt} Draw a subject $s \sim \phi_f^s$\\
+    \hspace*{30pt} Draw an object $o \sim \phi_f^o$
+    \end{snugshade}
+
+    \input{model1plate.tex}
+
+    \caption{Model 1 generative story}
+
+\end{figure}
+
+The independence assumptions int the generative story for model 1 give us the 
+following joint distribution:
+
+\begin{align*}
+&P(\mathbf{w},\mathbf{f}|\theta,\phi,\alpha,\beta)\\
+&=P(\mathbf{w}|\mathbf{f},\phi)\,P(\mathbf{f}|\theta)\,P(\theta|\alpha)\,P(\phi|\beta)
+\end{align*}
+
+We can find the marginal distribution of the latent and observed variables by
+integrating over the priors:
+
+\begin{align*}
+& P(\mathbf{w},\mathbf{f}|\alpha,\beta)\\
+&=\int_\phi\int_\theta P(\mathbf{w},\mathbf{f}|\theta,\phi,\alpha,\beta)\\
+&=     \int_\phi P(\mathbf{w}|\mathbf{f},\phi )\,P(\phi|\beta)
+\times \int_\theta P(\mathbf{f}|\theta)\,P(\theta|\alpha)
+\end{align*}
+
+\begin{align}
+&p(z_{ij} = f| \mathbf{f}_{-ij},\alpha,\beta,\mathbf{w})\\
+&\propto \prod_a^{\{v,s,o\}}\frac{\beta^a + \tilde{c}(f,w_{ij})}{V^a + \tilde{c}(f)}
+        \cdot \frac{\alpha + \tilde{c}(i,f)}{f\alpha+\tilde{c}(i)}
+\end{align}
+
 \section{Data}
+
 \subsection{Google Syntactic-ngrams}
-Here we talk a bit about the syntactic n-grams and all that \cite{ngrams2013}.
+Here we talk a bit about the syntactic n-grams and all that \citep{ngrams2013}.
+\begin{itemize}
+    \item A syntactic-ngram is a $k$-word rooted subtree for some sentence. 
+    \item Google ngrams come from a corpus of 3.5 million English books.
+    \item We trimmed the ``verb args'' dataset to consider only subject-verb-object triples (VSO's).
+    \item The dataset contains 1,629,120 unique VSO's with a total of 96,245,401 by count.
+    \item In our final results we may only use the most common \%20 of these...
+\end{itemize}
+
 \subsection{Pruning}
@@
 \section{Future Work}
+\begin{itemize}
+\item Come up with models that are specifically for independent tuples.
+\item Use more of the arguments in verbargs.
+\item Use year information -- do frames change over time?
+\item Consider subjet/object pairs instead of independent.
+\end{itemize}
 

### 2014-12-21 Paper/paper.tex
Model 1.

@@
 
-\begin{figure}[h]
+\begin{figure}
 
@@
 
+    \caption{Model 0 generative story}
     \label{gen0}
-    \caption{Model 0 generative story}
 
@@
 
-The generative story (fig. \ref{gen0}) gives us the following joint probability:
+The generative story (figure \ref{gen0}) gives us the following joint probability:
 \begin{align*}
@@
 
-As we know from topic modeling, it is the nature of documents that they contain 
-sentences with related semantic content. Therefore, it is reasonable to assume 
-that semantic frames are not uniformly distributed within documents. Taking 
-advantage of this assumption, we can break drop model 0's assumption of independence 
-between tuples.
+It is in the nature of documents that they have some degree of internal semantic
+coherence. Put more plainly, a document is usually \emph{about} something. We
+know from topic modeling that LDA with Gibbs sampling can be very successful at
+classifying documents according to some semantic features \citep{griffiths2004}.
+Model 1 leverages this fact by making the assmumption that a given document is 
+likely to have a sparse distribution of frames. As in LDA, the document-level
+sparsity is enforced by a dirichlet prior on frame distributions (see figure
+\ref{gen1} for details). This assumption breaks the independence between tuples 
+that is maintained by Model 0 is dropped in Model 1.
 
@@
     \caption{Model 1 generative story}
+    \label{gen1}
 
@@
 
-The independence assumptions int the generative story for model 1 give us the 
+The independence assumptions in the generative story for model 1 give us the 
 following joint distribution:
@@
 
+These integrals are both dirichlet multinomials:
+
+\[
+\frac{DCM_i^{frames}(f_{ij}=f, \mathbf{f}_{-ij})}{DCM_i^{frames}(\mathbf{f}_{-ij})}
+\]
+
+and
+
+\[
+\prod_a^{\{v,s,o\}}\frac{DCM_i^{vocab^a}(f_{ij}=f, \mathbf{f}_{-ij})}{DCM_i^{vocab^a}(\mathbf{f}_{-ij})}
+\]
+
+We prefer not to consider the subject and object vocabularies independently 
+(i.e., $V^s = V^o$). This is more in line with the theory of semantic frames 
+since in principle, a noun playing a particlar semantic role may appear in either 
+syntactic position.
+
+Dropping terms not dependent on counts, we can calculate the probability 
+required for Gibbs sampling as follows:
+
 \begin{align}
-&p(z_{ij} = f| \mathbf{f}_{-ij},\alpha,\beta,\mathbf{w})\\
-&\propto \prod_a^{\{v,s,o\}}\frac{\beta^a + \tilde{c}(f,w_{ij})}{V^a + \tilde{c}(f)}
-        \cdot \frac{\alpha + \tilde{c}(i,f)}{f\alpha+\tilde{c}(i)}
+& P(f_{ij} = f|\mathbf{f}_{-ij},\mathbf{w}, \alpha,\beta)\nonumber\\
+&=\frac{\alpha + \tilde c(d_i,f)}{F\,\alpha + \tilde c(d_i)}
+\times \prod_a^{\{v,s,o\}}\frac{\beta+\tilde c(f,w_{ij}^a)}{V^a\beta+\tilde c(f)}
 \end{align}
+
+Where $\tilde c (d_i, f)$ is the number of VSO's in document $d_i$ assigned to frame $f$,
+$\tilde c(d_i)$ is the number of VSO's in document $i$,
+$\tilde c(f,w_{ij}^a)$ is the number of VSOs containing $w_{ij}^a$ as argument $a$ that are
+assigned to frame $f$, and
+$\tilde c(f)$ is the number of VSOs assigned to frame $f$.
+Note that $\tilde c$ indicates a count that does not consider the contribution of 
+VSO $w_{i,j}$.
+
+We will see that the data used in this probject doesn't contain any document-level
+information. As a result, we adapt model 1 by grouping VSOs with the same verb into ``documents''.
+This move leverages the dirichlet prior $\alpha$ to enforce sparcity of frames 
+accross verbs, but of course cannot capture the information given by the kind of
+document-level semantic sparsity seen in LDA.\footnote{When we use verbs as
+documents (i.e, $D = V^v$), since $w_{ij}^v$ is the same for all verbs in document $d_i$ 
+(and $d_i$ is the only document with that verb), it follows that the number of VSO's in document 
+$d_i$ belonging to frame $f$ is the same as the number of VSO's with $w_{ij}^v$ as their verb assigned to 
+frame $f$; that is, $\tilde c(d_i, f) = \tilde c(f, w_{ij}^v)$.}
 

### 2014-12-21 evaluation.py
grid_search - needs testing

@@ -42,48 +42,72 @@ def show_most_common(frame_dists_v, frame_dists_w, top=25):
 
 def frame_coherency(model, data):
 
-    (frame_dists, frame_assign, theta) = model
-    results = []
-
-    total = 0
-    coh = 0
+    # trained model
+    if len(model) == 3:
+        (frame_dists, frame_assign, theta) = model
+        M = 0
+    elif len(model) == 2:
+        (verb_dists, word_dists) = model
+        frame_assign  =  {(v,s,o): np.argmax([verb_dists[f][v]*word_dists[f][s]*word_dists[f][o] for f in verbs_dists],axis=0) for (v,s,o) in data}
+        M = 1
+    # initialize variables
+    total = 0            # actual number of tested examples (unique entries in model * counts)
+    coh = 0              # number of tuples with higher probability on model than with random verb
     N = len(data)
+
+    # lists to store results
     probs = []
     probsR = []
 
-    dataList = list(data.keys())
+    # calculate max probability of each tuple in testset (=data)    
+    if M == 0:
+        probs = [frame_dists[frame_assign[(v,s,o)]]['v'][v]*frame_dists[frame_assign[(v,s,o)]]['s'][s]*frame_dists[frame_assign[(v,s,o)]]['o'][o]*theta[frame_assign[(v,s,o)]] for(v,s,o) in data ]
+    elif M == 1:
+        frm = frame_assign[(v,s,o)]
+        probs = [verb_dists[frm][v]*word_dists[frm][s]*word_dists[frm][o] for (v,s,o) in data ]
+        #verbDists = {f: {index_to_verb[i]: verbDists[i][f] for i in range(V)} for f in range(F)}
 
-    
-    probs = [frame_dists[frame_assign[(v,s,o)]]['v'][v]*frame_dists[frame_assign[(v,s,o)]]['s'][s]*frame_dists[frame_assign[(v,s,o)]]['o'][o]*theta[frame_assign[(v,s,o)]] for(v,s,o) in data ]
-   
-    tstD = [(rnd.choice(dataList)[0], vso[0], vso[1], vso[2]) for vso in data]
+    # initialize tuples with verb replaced by random verb
+    verbs = []
+    for (v,s,o) in data.keys():
+        for i in range(data[(v,s,o)]):
+            verbs.append(v)
 
[…]

### 2014-12-21 grid_search.py

@@ -1,0 +1,56 @@
+import model1
+import model0
+import evaluation
+import pickle
+import operator
+
+
+trnData = pickle.load(open('trainingData.pkl', 'rb'))
+tstData = pickle.load(open('testingData.pkl', 'rb'))
+xvData  = pickle.load(open('xvData.pkl', 'rb'))
+
+
+def test():
+    
+    frames = [10,20]#5*(n+1) for n in range(50)]
+    alphas = [1] #[0.5,1,1.5,2]
+    betas = [0.5,1,1.5,2]
+
+    res_M0 = {}
+    res_M1 = {}
+    
+    for f in frames:
+        for a in alphas:
+            model = model0.em(f,a,trnData)
+            res_M0[(f,a)] = (evaluation.frame_coherency(model,xvData),0)#evaluation.frame_accuracy(model))
+            for b in betas:
+                model = model1.gibbs(f,a,b,1000, 1, trnData)
+                res_M1[(f,a,b)] = (evaluation.frame_coherency(model,xvData),0)#evaluation.frame_accuracy(model))
+
+    metrics = ['coh','acc','both']
+    i=0
+    for (f,a) in select_best(res_M0):
+        fl = open(str('mod0_%s_f%d_a%f.pkl'%(metrics[i],f,a)),'wb')
+        pickle.dump(model0.em(f,a,tstData), fl , pickle.HIGHEST_PROTOCOL) 
+        i += 1
+
+def select_best(resultsXV):
+    
+    best_coh = [params for (params,_) in sorted(resultsXV.items(), key=lambda resultsXV: resultsXV[1][0])]
+    best_acc = [params for (params,_) in sorted(resultsXV.items(), key=lambda resultsXV: resultsXV[1][1])]
+
+    T = 1000
+    for C in range(len(best_coh)):
+        A = best_acc.index(best_coh[C])
+        cur = (A-C)**2 - (A+C)/2
+        if cur < T :
+            best_both = best_coh[C]
+            T = cur
+    return [best_coh[0], best_acc[0], best_both]
+    
+'''
+pool = multiprocessing.Pool(4)
+out1, out2, out3 = zip(*pool.map(calc_stuff, range(0, 10 * offset, offset)))
+'''
+
+test()

### 2014-12-21 grid_search.py
grid_search - needs testing

@@ -14,7 +14,7 @@ def test():
     
     frames = [10,20]#5*(n+1) for n in range(50)]
     alphas = [1] #[0.5,1,1.5,2]
-    betas = [0.5,1,1.5,2]
+    betas = [0.5]#,1,1.5,2]
 
     res_M0 = {}
     res_M1 = {}
@@ -24,7 +24,7 @@ def test():
             model = model0.em(f,a,trnData)
             res_M0[(f,a)] = (evaluation.frame_coherency(model,xvData),0)#evaluation.frame_accuracy(model))
             for b in betas:
-                model = model1.gibbs(f,a,b,1000, 1, trnData)
+                model = model1.gibbs(f,a,b,10, 1, trnData)
                 res_M1[(f,a,b)] = (evaluation.frame_coherency(model,xvData),0)#evaluation.frame_accuracy(model))
 
     metrics = ['coh','acc','both']
@@ -34,11 +34,20 @@ def test():
         pickle.dump(model0.em(f,a,tstData), fl , pickle.HIGHEST_PROTOCOL) 
         i += 1
 
+    i=0
+    for (f,a,b) in select_best(res_M1):
+        fl = open(str('mod1_%s_f%d_a%f_b%f.pkl'%(metrics[i],f,a,b)),'wb')
+        pickle.dump(model1.gibbs(f,a,b,1,10,tstData), fl , pickle.HIGHEST_PROTOCOL) 
+        i += 1
+
 def select_best(resultsXV):
     
     best_coh = [params for (params,_) in sorted(resultsXV.items(), key=lambda resultsXV: resultsXV[1][0])]
     best_acc = [params for (params,_) in sorted(resultsXV.items(), key=lambda resultsXV: resultsXV[1][1])]
 
+
+    # best parameters for both:
+    #       euclidian distance in sorted arrays of best coherency/accuracy - average distance to best params of individual metrics
     T = 1000
     for C in range(len(best_coh)):
         A = best_acc.index(best_coh[C])

### 2014-12-21 grid_search.py
grid_search - needs testing

@@ -47,7 +47,7 @@ def select_best(resultsXV):
 
 
     # best parameters for both:
-    #       euclidian distance in sorted arrays of best coherency/accuracy - average distance to best params of individual metrics
+    #     euclidian distance in sorted arrays of best coherency/accuracy - average distance to best params of individual metrics
     T = 1000
     for C in range(len(best_coh)):
         A = best_acc.index(best_coh[C])

### 2014-12-21 evaluation.py
fixed two typos

@@ -48,7 +48,7 @@ def frame_coherency(model, data):
         M = 0
     elif len(model) == 2:
         (verb_dists, word_dists) = model
-        frame_assign  =  {(v,s,o): np.argmax([verb_dists[f][v]*word_dists[f][s]*word_dists[f][o] for f in verbs_dists],axis=0) for (v,s,o) in data}
+        frame_assign  =  {(v,s,o): np.argmax([verb_dists[f][v]*word_dists[f][s]*word_dists[f][o] for f in verb_dists],axis=0) for (v,s,o) in data}
         M = 1
     # initialize variables
     total = 0            # actual number of tested examples (unique entries in model * counts)
@@ -63,8 +63,10 @@ def frame_coherency(model, data):
     if M == 0:
         probs = [frame_dists[frame_assign[(v,s,o)]]['v'][v]*frame_dists[frame_assign[(v,s,o)]]['s'][s]*frame_dists[frame_assign[(v,s,o)]]['o'][o]*theta[frame_assign[(v,s,o)]] for(v,s,o) in data ]
     elif M == 1:
-        frm = frame_assign[(v,s,o)]
-        probs = [verb_dists[frm][v]*word_dists[frm][s]*word_dists[frm][o] for (v,s,o) in data ]
+        probs = []
+        for (v,s,o) in data:
+            frm = frame_assign[(v,s,o)]
+            probs.append(verb_dists[frm][v]*word_dists[frm][s]*word_dists[frm][o])
         #verbDists = {f: {index_to_verb[i]: verbDists[i][f] for i in range(V)} for f in range(F)}
 
     # initialize tuples with verb replaced by random verb

### 2014-12-21 gibbs_c.c

@@ -110,7 +110,7 @@ void gibbs(void *data_void, void *samples_void,
             frame_count_w[f_new][s] += c;
             frame_count_w[f_new][o] += c;
         }
-        printf("Had %d of %lu VSOs change frame.\n", changes, N);
+        printf("Had %d of %lu VSOs change frame.\r", changes, N);
     }
 
     for (int f = 0; f < F; f++) {

### 2014-12-21 grid_search.py

@@ -37,7 +37,7 @@ def test():
     i=0
     for (f,a,b) in select_best(res_M1):
         fl = open(str('mod1_%s_f%d_a%f_b%f.pkl'%(metrics[i],f,a,b)),'wb')
-        pickle.dump(model1.gibbs(f,a,b,1,10,tstData), fl , pickle.HIGHEST_PROTOCOL) 
+        pickle.dump(model1.gibbs(f,a,b,10,1,tstData), fl , pickle.HIGHEST_PROTOCOL) 
         i += 1
 
 def select_best(resultsXV):

### 2014-12-21 runmodel1.py

@@ -2,8 +2,8 @@ import model1
 import pickle
 
 data = pickle.load(open('trainingData.pkl', 'rb'))
-F = 100 
-T = 1000
+F = 50 
+T = 500 
 alpha = 0.50
 beta = 0.50
 burnIn = 50

### 2014-12-21 gibbs_c.c
normalize function for later

@@ -1,6 +1,7 @@
 #include <stdio.h>
 #include <stdlib.h>
 #include <time.h>
+#include <math.h>
 
 enum {
     VERB,
@@ -10,6 +11,17 @@ enum {
     FRAME,
     M 
 };
+
+
+void normalize(double *weights, int len) {
+    double sum = 0;
+    for (int i = 0; i < len; i++) {
+        sum += weights[i];
+    }
+    for (int i = 0; i < len; i++) {
+        weights[i] /= sum;
+    }
+}
 
 long random_weighted(double *weights, int len) {
     double r = (double)rand() / (double)RAND_MAX;
@@ -54,8 +66,8 @@ void gibbs(void *data_void, void *samples_void,
         long o = data[M*i + OBJ];
         long c = data[M*i + COUNT];
         long f = data[M*i + FRAME];
-        frame_count[f] += c;
         doc_count[v] += c;
+        frame_count[f] += c;
         frame_count_v[f][v] += c;
         frame_count_w[f][s] += c;
         frame_count_w[f][o] += c;
@@ -73,6 +85,7 @@ void gibbs(void *data_void, void *samples_void,
             long f = data[M*i + FRAME];
 
             // modify counts to exclude data point i
+            doc_count[v] -= c;
             frame_count[f] -= c;
             frame_count_v[f][v] -= c;
             frame_count_w[f][s] -= c;
@@ -87,8 +100,8 @@ void gibbs(void *data_void, void *samples_void,
                 double o_term = ( (beta + frame_count_w[f][o])
                                  / (beta*W + frame_count[f]) );
                 double f_term  = ( (alpha + frame_count_v[f][v])
-                                 / (F*alpha + c) );
-                posterior[f] = v_term * s_term * o_term * f_term;
+                                 / (F*alpha + doc_count[v]) );
+                posterior[f] = log(v_term * s_term * o_term * f_term);
             }
 
             // assign the new frame randomly
@@ -105,13 +118,15 @@ void gibbs(void *data_void, void *samples_void,
             }
 
             // modify counts to reflect new frame 
+            doc_count[v] += c;
             frame_count[f_new] += c;
             frame_count_v[f_new][v] += c;
             frame_count_w[f_new][s] += c;
             frame_count_w[f_new][o] += c;
         }
-        printf("Had %d of %lu VSOs change frame.\r", changes, N);
+        printf("Had %d of %lu VSOs change frame.\n", changes, N);
[…]

### 2014-12-21 dicesim.py
implementing dicesim (not functioning but check back in a few hours, should give the general idea though)

@@ -1,0 +1,130 @@
+
+from operator import itemgetter
+import pickle
+import framenet
+
+
+##------------
+
+def dicesim(A, B):
+    A = set(A)
+    B = set(B)
+    return (( 2 * len(A & B) ) / ( len(A) + len(B) ))
+
+
+# assume a dict input {frame: list of verbs}
+# finds model frame with best dice score for each FN frame
+def dicematch(model_frameverbs, fn_frameverbs):
+    
+    # dict {FN frameID: {model frame: dicesim score with FN frame}}
+    frame_matches = dict.fromkeys(fn_frameverbs)
+    
+    for fn_frame in fn_frameverbs:
+        dicesims = dict.fromkeys(model_frameverbs)
+        for m_frame in model_frameverbs:
+            dicesims[m_frame] = dicesim(fn_frameverbs[fn_frame], model_frameverbs[m_frame])
+        frame_matches[fn_frame] = dicesims
+
+    return frame_matches
+
+
+def dicemax(model_frameverbs, fn_frameverbs):
+    dicedict = dicematch(model_frameverbs, fn_frameverbs)
+
+    frame_maxes = dict.fromkeys(fn_frameverbs)
+
+    for fn_frame in fn_frameverbs:
+        currentmax = ('',-1)
+        for m_frame in model_frameverbs:
+            if dicedict[fn_frame][m_frame] > currentmax[1]:
+                currentmax = (m_frame, dicedict[fn_frame][m_frame])
+        frame_maxes[fn_frame] = currentmax
+
+    return frame_maxes
+
+
+
+##------------
+
+
+
+# modeled on evaluation.frames_by_frequency
+def frame_freqsort(verbdists):
+    ig1 = itemgetter(1)
+    verbfreqs = {f: list(verbdists[f].items()) for f in verbdists}
+    for f in verbdists:
+        verbfreqs[f].sort(key=ig1, reverse=True)
+
+    return verbfreqs
+
+
+
+
+def verbmembers_topN(verbfreqs, N):
+    verb_rosters = dict.fromkeys(verbfreqs)
+    for f in verbfreqs:
+        verb_rosters[f] = verbfreqs[f][:N]
+        
+    return verb_rosters
+
+def verbmembers_cutoffprob(verbfreqs, q):
+#   ig1 = itemgetter(1)
+    verb_rosters = dict.fromkeys(verbfreqs, list())
+    for f in verbfreqs:
+        i = 0
[…]

### 2014-12-21 framenet.py

@@ -2,6 +2,8 @@
 import xml.etree.ElementTree as ET
 
 
+##------------
+
 lutree = ET.parse('fndata-1.5/luIndex.xml')
 luroot = lutree.getroot()
 luchildren = [i for i in luroot]
@@ -44,44 +46,3 @@ def sort_verbs_to_frames(thresh=0):
     remove_sparse_frames(frameverbs, thresh)
     return frameverbs
 
-
-
-def dicesim(A, B):
-    A = set(A)
-    B = set(B)
-    return (( 2 * len(A & B) ) / ( len(A) + len(B) ))
-
-
-# assume a dict input {frame: list of verbs}
-# finds model frame with best dice score for each FN frame
-def dicematch(model_frameverbs, fn_frameverbs):
-    
-    # dict {FN frameID: {model frame: dicesim score with FN frame}}
-    frame_matches = dict.fromkeys(fn_frameverbs)
-    
-    for fn_frame in fn_frameverbs:
-        dicesims = dict.fromkeys(model_frameverbs)
-        for m_frame in model_frameverbs:
-            dicesims[m_frame] = dicesim(fn_frameverbs[fn_frame], model_frameverbs[m_frame])
-        frame_matches[fn_frame] = dicesims
-
-    return frame_matches
-
-
-def dicemax(model_frameverbs, fn_frameverbs):
-    dicedict = dicematch(model_frameverbs, fn_frameverbs)
-
-    frame_maxes = dict.fromkeys(fn_frameverbs)
-
-    for fn_frame in fn_frameverbs:
-        currentmax = ('',-1)
-        for m_frame in model_frameverbs:
-            if dicedict[fn_frame][m_frame] > currentmax[1]:
-                currentmax = (m_frame, dicedict[fn_frame][m_frame])
-        frame_maxes[fn_frame] = currentmax
-
-    return frame_maxes
-
-
-
-#def get_model_verbsets(frame_assign):

### 2014-12-22 dicesim.py
joy to the world, the dicesim code should be working now

@@ -1,5 +1,6 @@
 
 from operator import itemgetter
+from webbrowser import open as wbopen
 import pickle
 import framenet
 
@@ -12,9 +13,9 @@ def dicesim(A, B):
     return (( 2 * len(A & B) ) / ( len(A) + len(B) ))
 
 
-# assume a dict input {frame: list of verbs}
-# finds model frame with best dice score for each FN frame
-def dicematch(model_frameverbs, fn_frameverbs):
+# assume a dict input {frame: [verbs]}
+# outputs {FN frame f: {model frame m: dicesim(f, m)}}
+def dicescores(model_frameverbs, fn_frameverbs):
     
     # dict {FN frameID: {model frame: dicesim score with FN frame}}
     frame_matches = dict.fromkeys(fn_frameverbs)
@@ -27,20 +28,30 @@ def dicematch(model_frameverbs, fn_frameverbs):
 
     return frame_matches
 
+# this is currently unreadably formatted but I'm working on it
+# def print_dice_table(frame_matches):
+#     print('_______|')
+    
+#     for f in frame_matches:
+#         print(' '.join([f.rjust(6),'|']+[str(round(frame_matches[f][m],4)).rjust(5) for m in frame_matches[f]]))
+#         print('       |')
+        
+        
 
-def dicemax(model_frameverbs, fn_frameverbs):
-    dicedict = dicematch(model_frameverbs, fn_frameverbs)
 
-    frame_maxes = dict.fromkeys(fn_frameverbs)
-
+# outputs {FN frameID f: (ID of best Dice-matched frame m, dicesim(f, m))}
+def dice_maxmatch(model_frameverbs, fn_frameverbs):
+    dicedict = dicescores(model_frameverbs, fn_frameverbs)
+    fn_bestmatches = dict.fromkeys(fn_frameverbs)
     for fn_frame in fn_frameverbs:
         currentmax = ('',-1)
         for m_frame in model_frameverbs:
             if dicedict[fn_frame][m_frame] > currentmax[1]:
                 currentmax = (m_frame, dicedict[fn_frame][m_frame])
-        frame_maxes[fn_frame] = currentmax
+        fn_bestmatches[fn_frame] = currentmax
 
-    return frame_maxes
+    return fn_bestmatches
+
 
 
 
@@ -63,17 +74,18 @@ def frame_freqsort(verbdists):
 def verbmembers_topN(verbfreqs, N):
[…]

### 2014-12-22 framenet.py

@@ -21,7 +21,7 @@ for i in ludicts:
     if i['name'][-2:] == '.v':
         luverbdicts.append(i)
 
-
+fnverbs = {i['ID']: (i['name'][:-2], i['frameID']) for i in luverbdicts}
 
 def print_lu_verbs():
     for i in luverbdicts:
@@ -34,6 +34,7 @@ def remove_sparse_frames(d, thresh=0):
             del d[i]
 
 # returns {frameID: [list of verbs]} dict
+#     ("rosters"?)
 def sort_verbs_to_frames(thresh=0):
     frameverbs = dict.fromkeys([i['ID'] for i in framedicts], [])
     for fID in frameverbs.keys():
@@ -46,3 +47,25 @@ def sort_verbs_to_frames(thresh=0):
     remove_sparse_frames(frameverbs, thresh)
     return frameverbs
 
+
+
+
+##----------
+
+def print_frame_info_via_frameID(frameID):
+    #pull data from XML file?
+    fname = fnframes[frameID]
+    ftree = ET.parse('fndata-1.5/frame/'+fname+'.xml')
+    froot = ftree.getroot()
+
+    print(frameID.rjust(6), fnframes[frameID], "\n")
+    
+#    print("DEFINITION",froot[0].text)
+#    print("LEXICAL UNITS", 
+    
+    return
+
+
+
+
+    

### 2014-12-22 Paper/paper.tex
minor additions/changes

@@
     \and
-    Drumm, Eli\\
+    Drumm, Eli T.\\
     \texttt{etd@dte.li}
@@
 Thus the problem is reduced to maximizing each of the terms in the sum above. Fortunately
-these have closed for solutions using lagrangian multipliers.
+these have closed for solutions using Lagrangian multipliers.
 
@@
 \subsection{Frame Correctness}
+% I (Eli) can expond here on the relation/contrast/etc.
+%   between what we're doing and Framenet;
+%   I think O'Connor brings up some technical and/or methodological points
+%   about ways we can vs. can't use the FN data for evaluating
+%   induction and such, I'll look it over again.
+
 Frame correctness: for the top 25 most probable verbs per frame $TV$ and framenet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
+
 \subsection{Model 0}

### 2014-12-22 dicesim.py

@@ -1,9 +1,8 @@
 
 from operator import itemgetter
-from webbrowser import open as wbopen
 import pickle
-import framenet
 
+import framenet
 
 ##------------
 
@@ -27,6 +26,7 @@ def dicescores(model_frameverbs, fn_frameverbs):
         frame_matches[fn_frame] = dicesims
 
     return frame_matches
+
 
 # this is currently unreadably formatted but I'm working on it
 # def print_dice_table(frame_matches):
@@ -137,7 +137,8 @@ def run_dicesim():
     fn_frameverbs = framenet.sort_verbs_to_frames(fn_threshold)
 
     # for each framenet frame, find the best-matching frame generated by our model
-    #   as determined by dicesim scores
+    #   as determined by dicesim scores --- currently run_dicesim() also returns
+    #   the full dict-of-dicts (dice_scoresheet) along with just the computed matches
     dice_scoresheet = dicescores(model_frameverbs, fn_frameverbs)
     dice_results = dice_maxmatch(model_frameverbs, fn_frameverbs)
 

### 2014-12-22 Paper/paper.tex
Data section and some future work.

--- 2014-12-21 Paper/paper.tex
@@
 
-Dropping terms not dependent on counts, we can calculate the probability 
-required for Gibbs sampling as follows:
+Dropping terms not dependent on counts, we can calculate the proportional
+probability required for Gibbs sampling as follows:
 
@@
 
-Where $\tilde c (d_i, f)$ is the number of VSO's in document $d_i$ assigned to frame $f$,
-$\tilde c(d_i)$ is the number of VSO's in document $i$,
+Where $\tilde c (d_i, f)$ is the number of VSO's in document $d_i$ assigned to frame $f$;
+$\tilde c(d_i)$ is the number of VSO's in document $i$;
 $\tilde c(f,w_{ij}^a)$ is the number of VSOs containing $w_{ij}^a$ as argument $a$ that are
-assigned to frame $f$, and
+assigned to frame $f$; and
 $\tilde c(f)$ is the number of VSOs assigned to frame $f$.
 Note that $\tilde c$ indicates a count that does not consider the contribution of 
-VSO $w_{i,j}$.
+$w_{i,j}$.
 
-We will see that the data used in this probject doesn't contain any document-level
+The data used in this probject (see section \ref{data}) doesn't contain any document-level
 information. As a result, we adapt model 1 by grouping VSOs with the same verb into ``documents''.
@@
 
-\section{Data}
+\section{Dataset - Verbargs}
+\label{data}
 
-\subsection{Google Syntactic-ngrams}
-Here we talk a bit about the syntactic n-grams and all that \citep{ngrams2013}.
-\begin{itemize}
-    \item A syntactic-ngram is a $k$-word rooted subtree for some sentence. 
-    \item Google ngrams come from a corpus of 3.5 million English books.
-    \item We trimmed the ``verb args'' dataset to consider only subject-verb-object triples (VSO's).
-    \item The dataset contains 1,629,120 unique VSO's with a total of 96,245,401 by count.
-    \item In our final results we may only use the most common \%20 of these...
-\end{itemize}
+Verbargs is the subset of Google's syntactic-ngram corpus for training our 
+models and evaluating the reults 
+A syntactic-ngram is a $k$-word rooted subtree of some sentence.
+The ngrams in Google's corpus were extracted from 3.5 million books and are labled with
+Penn Treebank part-of-speech tags Stanford-basic dependency lables \citep{ngrams2013}.
+Each ngram also includes frequency counts by year.
+In this project, used the
 
-\subsection{Pruning}
+The ngrams in the verbargs dataset (130M items) consist of a verb and all of its 
+immediate arguments.
+From this dataset, we consider only VSO's, that is; we pruned verbargs to only
+those ngrams containing a subject (nsubj) and object (dobj) whose immediate parent
+is the ngram's root verb (1.6M items, 96M by count). 
+We further trimmed the data to consider only the \%25 most common verbs 
+(800K items, 78M by count).
 
@@
 \section{Future Work}
-\begin{itemize}
-\item Come up with models that are specifically for independent tuples.
-\item Use more of the arguments in verbargs.
-\item Use year information -- do frames change over time?
-\item Consider subjet/object pairs instead of independent.
-\end{itemize}
+One big weakness of this project over the results of \citet{oconnor2013} is that 
+we could not used document-level context to leverage semantic information.
+A possible direction of future reseach is to create models that take better 
+advantage of the syntax-level context provided by syntactic ngrams. 
+One easy way to do this would be to modify model 1 so that the argument 
+vocabulary ranges over subject/object pairs instead of individual nouns.
+or object.
+More advanced models would take better advantage of the various kinds of arguments
+in verbargs and their relation to one another.
+For example, you might be gleen some semantic information about the relationship between
+verbs and prepositional objects by the preposition that mediates them: 
+That you ''swim \emph{in} the lake'' versus ``ice skate \emph{on} the lake'' 
+indicates that the relationship between swimming and lakes is different from the one between
+ice skating and lakes.
 

### 2014-12-22 Paper/paper.tex
fix typos

@@
 
-Verbargs is the subset of Google's syntactic-ngram corpus for training our 
-models and evaluating the reults 
 A syntactic-ngram is a $k$-word rooted subtree of some sentence.
-The ngrams in Google's corpus were extracted from 3.5 million books and are labled with
-Penn Treebank part-of-speech tags Stanford-basic dependency lables \citep{ngrams2013}.
+Google syntactic-ngrams is a corpus of ngrams extracted from 3.5 million English language 
+books and labled with Penn Treebank part-of-speech tags Stanford-basic dependency 
+lables \citep{ngrams2013}.
 Each ngram also includes frequency counts by year.
-In this project, used the
 
-The ngrams in the verbargs dataset (130M items) consist of a verb and all of its 
+This project uses the verbargs subeset (130M items) of Google syntactic-ngrams.
+An ngram in the verbargs dataset consist of a verb and all of its 
 immediate arguments.
-From this dataset, we consider only VSO's, that is; we pruned verbargs to only
+We considered only the VSO's in this dataset, that is; we pruned verbargs to
 those ngrams containing a subject (nsubj) and object (dobj) whose immediate parent
@@
 One big weakness of this project over the results of \citet{oconnor2013} is that 
-we could not used document-level context to leverage semantic information.
+we could not used document-level context to infer semantic information.
 A possible direction of future reseach is to create models that take better 
@@
 or object.
-More advanced models would take better advantage of the various kinds of arguments
-in verbargs and their relation to one another.
-For example, you might be gleen some semantic information about the relationship between
-verbs and prepositional objects by the preposition that mediates them: 
-That you ''swim \emph{in} the lake'' versus ``ice skate \emph{on} the lake'' 
+More advanced models might take better advantage of the various kinds of arguments
+in the verbargs dataset and their relation to one another.
+For example, you could be gleen some semantic information about the relationship between
+verbs and prepositional objects by looking at the preposition that mediates them: 
+That you ''swim \emph{in} a lake'' versus ``ice skate \emph{on} a lake'' 
 indicates that the relationship between swimming and lakes is different from the one between

### 2014-12-23 Paper/paper.tex
editing.

@@
 We prefer not to consider the subject and object vocabularies independently 
-(i.e., $V^s = V^o$). This is more in line with the theory of semantic frames 
+(i.e., we let $V^s = V^o$). This is more in line with the theory of semantic frames 
 since in principle, a noun playing a particlar semantic role may appear in either 
@@
 
-Dropping terms not dependent on counts, we can calculate the proportional
+Dropping constants not dependent on counts, we can calculate the proportional
 probability required for Gibbs sampling as follows:

### 2014-12-24 framenet.py
some rework of dicesim, added rundicesim wrapper

@@ -70,3 +70,4 @@ def print_frame_info_via_frameID(frameID):
 
 
     
+##------------

### 2014-12-27 Paper/paper.tex
paper with intro

--- 2014-12-22 Paper/paper.tex
@@
 \author{
-    Verdegaal, Jacob\\
-    \texttt{jacob.verdegaal@student.uva.nl}
+    Noble, Bill\\
+    \texttt{winobes@gmail.com}
     \and
@@
     \and
-    Noble, Bill\\
-    \texttt{winobes@gmail.com}
+    Verdegaal, Jacob\\
+    \texttt{jacob.verdegaal@student.uva.nl}
 }
@@
 \section{Introduction}
-Here we provide some background information about what are semantic frames and 
-what it menas to induce them and stuff like that.
+When a machine looks at the sentence \textit{'Alice buys a bread from the baker'} it does not know it descibes the exact same situation as \textit{`The baker sells Alice a bread'}.
+But for a lot of applications it is usefull to have semantic representations of senteces or groups of sentences.
+For example in automatic summarization, some sentences are repaeated with different word choices and orders to express nuances, but since nuances can be left out in summarizations it would be usefull to have techniques to represent and generate semantic content.
 
-\section{Related Work}
-Here we talk mostly about the O'Connor paper \citep{oconnor2013} and the Rooth 
-paper \citep{rooth1999}.
+The Framenet project \citep{framenet} is ongoing on defining frames manually which could be mapped on a text to extrct frames.
+But with the increasing amount of digital information it is usefull to have auomatic semantic frame induction.
+For example for automatic stock trading systems, it would be usefull to know what is published about companies that are traded on.
+
+Semantic content of texts can be represented in frames, where the head of the frame represents the core of the episode and roles in the frame espress involement of things or people, location, time etc.
+For the sentences above the frame would look like this:\\
+
+\begin{tabular}{|l l|}
+  \hline
+  \textit{\small predicate:\normalsize}&Transaction\\
+  \hline
+  \hline
+  \textit{\small role 1:\normalsize} &baker\\
+  \textit{\small role 2:\normalsize} &Alice\\
+  \textit{\small role 3:\normalsize} &bread\\
+  \hline
+\end{tabular}\\
+
+The head of the frame, representing the core of the episode, can naturally be represented as a predicate but the trick is to find out which words have which roles.
+In linguistics this is called case grammar \citep{dowty1991}.
+As the example above shows, the roles are represented by different syntactic parts of speech in both sentences, the object and subject are switched, furthermore, the verbs are different.
+But even with knowledge of specific vebrs which bear the same meaning with switched subject/indirect-object, we need to have technology to let machines generate semantics next to syntacs in order to let machines be able to ( do as if they ) understand language and process new text in a meaningfull way.
+Hence, automatic semantic analysis and representation is required.\\
+
+In this project we investigate wheter probabalistic latent-variable models can cluster verbs (as being a predicate) based on their meaning, which is inferred from the occurences of arguments it is encountered with.
+The clusters then make up the broader meaning of the predicates.
+The data we use contains triples of verb-subject-object (see section\ref{data}), so induced frames contain only two roles.
+The models (described in section \ref{models}) induce frames based on the assumption the meaning of a verb relative to meaning of other verbs can be induced from its context.
+Hence the broader meaning is latent.
+To evaluate our models we use two metrics, one of which uses framenet data, the other to check wheter the resulting frames are coherent.
+See section \ref{results} for more detail.
+
+%\section{Related Work}
+We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}.
+In the first article clustering is realized by applying expectation maximalization on a simple model.
+This model produces frames in the form of 3 distributions, one for the predicate and two for the arguments.
+Frame assignement is result of calculating  probabilities for a given tuple, the frame that gives the highest probaility is then the assigned.
+We will use this model as our baseline (as in the O'Connor paper).
+The second paper covers multliple models of which we implemented one.
+The difference with the baseline model is the assumption that a document uses a set of frames repeatedly as a rsult of a document having a (couple of) topics.
+In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.
 
 \section{Induction Models}
-
+\label{models}
 We consider two probabalistic latent-variable models that learn semantic frames
@@
 \section{Experiments}
+The number of frames in both models must be determined before induction.
+When choosing for a low number of frames the clusters will be big and thus the meaning of a cluster vague.
+But a high number of frames has, next to high computational costs also a danger of overfitting the data.
+When unrelated verbs occur with the same arguments often they will be clustered and maybe will even make up one cluster, while with a lower number of frames other verbs would be included, diinishing one of the unrelated verbs as noise.
+
+The alphas and betas are known \citep{oconnor2013} to be hard to determine, and therefore need experiments to be set to optimal values for a specific problem.
+We used, expensive but easy to implement, grid search to determine all parameters to test with.
+With grid-search a model is build with certain parameters, this model is then evaluated on a cross validation set.
+When all possible models are evaluated the highest scoring model is tested on.
 
 \section{Results}
+\label{results}
 \subsection{Frame Coherency}

### 2014-12-27 evaluation.py
grid search with dicesim

@@ -1,7 +1,8 @@
 import numpy as np
-import model0 as mod0
+import dicesim
 import random as rnd
 import matplotlib.pyplot as pp
+
 
 args = ('v','s','o')
 
@@ -39,17 +40,20 @@ def show_most_common(frame_dists_v, frame_dists_w, top=25):
             j += 1
         print()
 
-
+# frame_coherency: calculates the maximal probability of a tuple and compares it with
+# the maximal probability on the model of same tuple in which the verb is replaced by a random verb
 def frame_coherency(model, data):
 
-    # trained model
+    # determine which model to evaluate 
     if len(model) == 3:
         (frame_dists, frame_assign, theta) = model
         M = 0
+    #if model1: set `frame_assign'
     elif len(model) == 2:
         (verb_dists, word_dists) = model
         frame_assign  =  {(v,s,o): np.argmax([verb_dists[f][v]*word_dists[f][s]*word_dists[f][o] for f in verb_dists],axis=0) for (v,s,o) in data}
         M = 1
+        
     # initialize variables
     total = 0            # actual number of tested examples (unique entries in model * counts)
     coh = 0              # number of tuples with higher probability on model than with random verb
@@ -70,11 +74,13 @@ def frame_coherency(model, data):
         #verbDists = {f: {index_to_verb[i]: verbDists[i][f] for i in range(V)} for f in range(F)}
 
     # initialize tuples with verb replaced by random verb
+    #     first: list all verbs ( with repitition )
     verbs = []
     for (v,s,o) in data.keys():
         for i in range(data[(v,s,o)]):
             verbs.append(v)
 
+    # second: create tuples with some random verb
     tstD = [(rnd.choice(verbs), vso[0], vso[1], vso[2]) for vso in data]
 
     # calculate max probability of tuple with random verb on model
@@ -88,12 +94,13 @@ def frame_coherency(model, data):
          else:
              probsR.append(0)
 
-
+# ----------- other possibilities for probabilities of tuples with random verb
     #probsR = [frame_dists[ frame_assign[(rV,s,o)]]['v'][rV]*frame_dists[frame_assign[(rV,s,o)]]['s'][s]*frame_dists[frame_assign[(rV,s,o)]]['o'][o]*theta[frame_assign[(rV,s,o)]] for (rV,v,s,o) in tstD]
[…]

### 2014-12-27 grid_search.py

@@ -22,10 +22,10 @@ def test():
     for f in frames:
         for a in alphas:
             model = model0.em(f,a,trnData)
-            res_M0[(f,a)] = (evaluation.frame_coherency(model,xvData),0)#evaluation.frame_accuracy(model))
+            res_M0[(f,a)] = (evaluation.frame_coherency(model,xvData),evaluation.frame_accuracy(verb_dists(model), .01, 50 ))
             for b in betas:
-                model = model1.gibbs(f,a,b,10, 1, trnData)
-                res_M1[(f,a,b)] = (evaluation.frame_coherency(model,xvData),0)#evaluation.frame_accuracy(model))
+                model = model1.gibbs(f,a,b,2, 1, trnData)
+                res_M1[(f,a,b)] = (evaluation.frame_coherency(model,xvData),evaluation.frame_accuracy(model[0], .01, 50 ))
 
     metrics = ['coh','acc','both']
     i=0
@@ -61,5 +61,11 @@ def select_best(resultsXV):
 pool = multiprocessing.Pool(4)
 out1, out2, out3 = zip(*pool.map(calc_stuff, range(0, 10 * offset, offset)))
 '''
+
+def verb_dists(model):
+    dists = model[0]
+    verb_dists = {frm: dists[frm]['v'] for frm in dists}
+
+    return verb_dists
 
 test()

### 2014-12-28 evaluation.py
final grid search

@@ -129,7 +129,7 @@ def frame_accuracy(verb_dists,cutOffP,fn_threshold):
     best = 0
     tot = 0
     for modS in mod_sets:
-        for fnS in fn_sets:
+        for fnS in fn_sets.values():
             modS = set(modS)
             fnS = set(fnS)
             cur = (( 2 * len(modS & fnS) ) / ( len(modS) + len(fnS) ))

### 2014-12-28 grid_search.py

@@ -3,41 +3,50 @@ import model0
 import evaluation
 import pickle
 import operator
+import multiprocessing
+import itertools
 
 
 trnData = pickle.load(open('trainingData.pkl', 'rb'))
 tstData = pickle.load(open('testingData.pkl', 'rb'))
 xvData  = pickle.load(open('xvData.pkl', 'rb'))
 
+def train0( prmS ):
+    (f,a) = prmS
+    model = model0.em(f,a,trnData)
+    return ((f,a),(evaluation.frame_coherency(model,xvData),evaluation.frame_accuracy(verb_dists(model), .01, 5 )))
 
+def train1( prmS ):
+    (f,a,b) = prmS
+    model = model1.gibbs(f,a,b,2, 1, trnData)
+    return ((f,a,b), (evaluation.frame_coherency(model,xvData),evaluation.frame_accuracy(model[0], .01, 5)))
+    
 def test():
     
-    frames = [10,20]#5*(n+1) for n in range(50)]
-    alphas = [1] #[0.5,1,1.5,2]
-    betas = [0.5]#,1,1.5,2]
+    frames = [25,50]#,100,150,200]
+    alphas = [.1]#,.5,1,1.5,2]
+    betas = [.1]#,.5,1,1.5,2]
 
-    res_M0 = {}
-    res_M1 = {}
+    params0 = itertools.product(frames,alphas)
+    params1 = itertools.product(frames,alphas,betas)
+
+    pool = multiprocessing.Pool(4)
+    res_M0 = dict(pool.map(train0, params0 ))
+    res_M1 = dict(pool.map(train1, params1 ))
     
-    for f in frames:
-        for a in alphas:
-            model = model0.em(f,a,trnData)
-            res_M0[(f,a)] = (evaluation.frame_coherency(model,xvData),evaluation.frame_accuracy(verb_dists(model), .01, 50 ))
-            for b in betas:
-                model = model1.gibbs(f,a,b,2, 1, trnData)
-                res_M1[(f,a,b)] = (evaluation.frame_coherency(model,xvData),evaluation.frame_accuracy(model[0], .01, 50 ))
-
     metrics = ['coh','acc','both']
     i=0
     for (f,a) in select_best(res_M0):
-        fl = open(str('mod0_%s_f%d_a%f.pkl'%(metrics[i],f,a)),'wb')
[…]

### 2014-12-28 Paper/paperN.tex
NIPS style paper

--- 2014-12-27 Paper/paper.tex
@@
-\documentclass[11pt,twocolumn,DIV=11]{scrartcl}
+%\documentstyle[nips14submit_09,times,art10]{article} % For LaTeX 2.09
+\documentclass{article} % For LaTeX2e
+\usepackage{nips14submit_e,times}
+\usepackage{hyperref}
+\usepackage{url}
 
@@
 
+\title{Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams}
+
 \author{
@@
 
-\title{Inducing Semantic Frames on a Very Large Corpus of Syntactic-Ngrams}
+% The \author macro works with any number of authors. There are two commands
+% used to separate the names and addresses of multiple authors: \And and \AND.
+%
+% Using \And between authors leaves it to \LaTeX{} to determine where to break
+% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
+% puts 3 of 4 authors names on the first line, and the last on the second
+% line, try using \AND instead of \And before the third author name.
+
+\newcommand{\fix}{\marginpar{FIX}}
+\newcommand{\new}{\marginpar{NEW}}
+
+\nipsfinalcopy % Uncomment for camera-ready version
 
@@
 \maketitle
+
+\begin{abstract}
+The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
+right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
+The word \textbf{Abstract} must be centered, bold, and in point size 12. Two
+line spaces precede the abstract. The abstract must be limited to one
+paragraph.
+\end{abstract}
 
@@
 \bibliography{refs.bib}
+
 \end{document}

### 2014-12-28 Paper/paperN.tex
fixed spacing and lines and stuff
added stuff to paper

@@
 \usepackage{url}
-
+\usepackage{subcaption}
+\usepackage{wrapfig}
 \usepackage{amsmath}
@@
 \section{Introduction}
-When a machine looks at the sentence \textit{'Alice buys a bread from the baker'} it does not know it descibes the exact same situation as \textit{`The baker sells Alice a bread'}.
-But for a lot of applications it is usefull to have semantic representations of senteces or groups of sentences.
-For example in automatic summarization, some sentences are repaeated with different word choices and orders to express nuances, but since nuances can be left out in summarizations it would be usefull to have techniques to represent and generate semantic content.
+The growing number of digital publications contains so much information that a single human being cannot process all this text, its even hard to keep up to date on a particular topic.
+It would be usefull to have technology that can create reliable summarizations.
+But not only quantity of information asks for such technology.
+For example for automatic stock trading systems, it would be usefull to know what is published about companies that are traded on the moment of publication.
 
-The Framenet project \citep{framenet} is ongoing on defining frames manually which could be mapped on a text to extrct frames.
-But with the increasing amount of digital information it is usefull to have auomatic semantic frame induction.
-For example for automatic stock trading systems, it would be usefull to know what is published about companies that are traded on.
-
-Semantic content of texts can be represented in frames, where the head of the frame represents the core of the episode and roles in the frame espress involement of things or people, location, time etc.
-For the sentences above the frame would look like this:\\
-
+The problem can be illustrated with a simple example: \textit{'Alice buys a bread from the baker'} descibes the exact same situation as \textit{`The baker sells Alice a bread'}.
+Thus the semantic content of these sentences can be represented in one frame, where the head of the frame represents the core of the episode or situation and involvement is expressed by assigning roles to things or people.
+In general these roles can be anything like location, time, manner etc.
+For the sentences above the frame is depicted in \ref{framex}.
+\begin{wraptable}{r}{.3\textwidth}
+  \centering
+ % \begin{table}
 \begin{tabular}{|l l|}
@@
   \hline
-\end{tabular}\\
+\end{tabular}
+%\end{table}
+\caption{Simple frame}
+\label{framex}
+\end{wraptable}
+The head of the frame, representing the core of the episode, can naturally be represented as a predicate but the trick is to find out which words have which roles.
+In linguistics this is called case grammar \citep{dowty1991} and roles have specific names as \textit{agent - patient}.
+In systems the names are not important and can be asigned when frame induction is complete.
 
-The head of the frame, representing the core of the episode, can naturally be represented as a predicate but the trick is to find out which words have which roles.
-In linguistics this is called case grammar \citep{dowty1991}.
 As the example above shows, the roles are represented by different syntactic parts of speech in both sentences, the object and subject are switched, furthermore, the verbs are different.
 But even with knowledge of specific vebrs which bear the same meaning with switched subject/indirect-object, we need to have technology to let machines generate semantics next to syntacs in order to let machines be able to ( do as if they ) understand language and process new text in a meaningfull way.
-Hence, automatic semantic analysis and representation is required.\\
+Hence, automatic semantic analysis and representation is required.
+
+The Framenet project \citep{framenet} is ongoing on defining frames manually which could be mapped on a text to extrct frames.
+But with the increasing amount of digital information it is usefull to have auomatic semantic frame induction, since new words can be added to a language and meanings can change.
 
@@
 
-\subsection{Model 0}
+\begin{figure}[h]
 
-The approach models each VSO independenly, without considering any further context.
-Word distributions are completely independent between arguments and accross frames.
-Tuples are clustered according to which frame's three distributions best fit the 
-three arguments.
-
-\begin{figure}
+  \begin{subfigure}[b]{0.45\textwidth}
 
@@
 
-    \caption{Model 0 generative story}
+    \caption{Model 0}
     \label{gen0}
 
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}[b]{0.45\textwidth}
+
+    \begin{snugshade}
+    \scriptsize
+    For each frame $f=1..F$:\\
+    \hspace*{15pt} For each argument $a\in\{v,s,o\}$:\\
+    \hspace*{30pt} Draw a distribution $\phi_f^a\sim Dirichlet(\beta)$\\
+    For each document $d=1..D$:\\
+    \hspace*{15pt} Draw a distrbution $\theta_d \sim Dirichlet(\alpha)$\\
+    \hspace*{30pt} For each $i = 1..N^d$:\\
+    \hspace*{30pt} Draw a frame $f \sim \theta^d$.\\
+    \hspace*{30pt} Draw a verb $v \sim \phi_f^v$\\
+    \hspace*{30pt} Draw a subject $s \sim \phi_f^s$\\
+    \hspace*{30pt} Draw an object $o \sim \phi_f^o$
+    \end{snugshade}
+
+    \input{model1plate.tex}
+
+    \caption{Model 1}
+    \label{gen1}
+
+  \end{subfigure}
+
+  \caption{Generative Stories}
+
 \end{figure}
+
+\subsection{Model 0}
+
+The approach models each VSO independenly, without considering any further context.
+Word distributions are completely independent between arguments and accross frames.
+Tuples are clustered according to which frame's three distributions best fit the 
+three arguments.
 
@@
 \begin{align*}
-&P(\mathbf{f},\mathbf{w}|\phi,\theta) 
-  = P(\mathbf{f}|\theta)P(\mathbf{w}|\phi)\\
+P(\mathbf{f},\mathbf{w}|\phi,\theta) 
+  =& P(\mathbf{f}|\theta)P(\mathbf{w}|\phi)\\
   =& \prod_{i=1}^{N}\big[\theta(f_i) \prod_a^{\{v,s,o\}}\phi_{f_i}^a(w_i^a)\big]
@@
 \begin{align*}
-&E_\mu\big[\sum_{i=1}^N\log P(w_i,f_i|\theta,\phi) =\\
+E_\mu\big[\sum_{i=1}^N\log P(w_i,f_i|\theta,\phi)
 =& \sum_{i=1}^N\sum_{f=1}^F\mu_i(f)\log\Big[\theta(f)\prod_a^{\{v,s,o\}}\phi_f^a(w_i^a)\Big]\\
-=& \sum_{i=1}^N\sum_{f=1}^F\mu_i(f)\log\theta(f)\\
-+& \sum_a^{\{v,s,o\}} \sum_{i=1}^N\sum_{f=1}^F\mu_i(f)\log \phi_f^a(w_i^a)
+=& \sum_{i=1}^N\sum_{f=1}^F\mu_i(f)\log\theta(f)
++ \sum_a^{\{v,s,o\}} \sum_{i=1}^N\sum_{f=1}^F\mu_i(f)\log \phi_f^a(w_i^a)
 \end{align*}
@@
 \begin{align}
-&\argmax_{\theta(f)}\sum_{i=1}^N\sum_{f=1}^F\mu_i(f)\log\theta(f)\nonumber\\
-&= \frac{\sum_{i=1}^N\mu_i(f)}{\sum_{f'}^F\sum_{i=1}^N\mu_i(f)}
+\argmax_{\theta(f)}\sum_{i=1}^N\sum_{f=1}^F\mu_i(f)\log\theta(f)
+= \frac{\sum_{i=1}^N\mu_i(f)}{\sum_{f'}^F\sum_{i=1}^N\mu_i(f)}
 \end{align}
@@
 \begin{align}
-&\argmax_{\phi^a(w)}\sum_{i=1}^N\sum_{f=1}^F\mu_i(f)\log \phi_f^a(w_i,a)\nonumber\\
-&= \frac{\sum_{i=1}^N \mu_i(f)\,c(w^a)}{\sum_{w'=1}^{V^a}\sum_{i=1}^N \mu_i(f)\,c(w',a)}
+\argmax_{\phi^a(w)}\sum_{i=1}^N\sum_{f=1}^F\mu_i(f)\log \phi_f^a(w_i,a)
+= \frac{\sum_{i=1}^N \mu_i(f)\,c(w^a)}{\sum_{w'=1}^{V^a}\sum_{i=1}^N \mu_i(f)\,c(w',a)}
 \end{align}
@@
 
-\begin{figure}
-
-    \begin{snugshade}
-    \scriptsize
-    For each frame $f=1..F$:\\
-    \hspace*{15pt} For each argument $a\in\{v,s,o\}$:\\
-    \hspace*{30pt} Draw a distribution $\phi_f^a\sim Dirichlet(\beta)$\\
-    For each document $d=1..D$:\\
-    \hspace*{15pt} Draw a distrbution $\theta_d \sim Dirichlet(\alpha)$\\
-    \hspace*{30pt} For each $i = 1..N^d$:\\
-    \hspace*{30pt} Draw a frame $f \sim \theta^d$.\\
-    \hspace*{30pt} Draw a verb $v \sim \phi_f^v$\\
-    \hspace*{30pt} Draw a subject $s \sim \phi_f^s$\\
-    \hspace*{30pt} Draw an object $o \sim \phi_f^o$
-    \end{snugshade}
-
-    \input{model1plate.tex}
-
-    \caption{Model 1 generative story}
-    \label{gen1}
-
-\end{figure}
-
 The independence assumptions in the generative story for model 1 give us the 
@@
 \begin{align*}
-&P(\mathbf{w},\mathbf{f}|\theta,\phi,\alpha,\beta)\\
+P(\mathbf{w},\mathbf{f}|\theta,\phi,\alpha,\beta)
 &=P(\mathbf{w}|\mathbf{f},\phi)\,P(\mathbf{f}|\theta)\,P(\theta|\alpha)\,P(\phi|\beta)
@@
 \begin{align*}
-& P(\mathbf{w},\mathbf{f}|\alpha,\beta)\\
+ P(\mathbf{w},\mathbf{f}|\alpha,\beta)
 &=\int_\phi\int_\theta P(\mathbf{w},\mathbf{f}|\theta,\phi,\alpha,\beta)\\
 &=     \int_\phi P(\mathbf{w}|\mathbf{f},\phi )\,P(\phi|\beta)
-\times \int_\theta P(\mathbf{f}|\theta)\,P(\theta|\alpha)
+\times \int_\theta P(\mathbf{f}|\theta)\,P(\theta|\alpha)\\
+\intertext{These integrals are both dirichlet multinomials:}
+&=\frac{DCM_i^{frames}(f_{ij}=f, \mathbf{f}_{-ij})}{DCM_i^{frames}(\mathbf{f}_{-ij})}\times
+\prod_a^{\{v,s,o\}}\frac{DCM_i^{vocab^a}(f_{ij}=f, \mathbf{f}_{-ij})}{DCM_i^{vocab^a}(\mathbf{f}_{-ij})}
 \end{align*}
-
-These integrals are both dirichlet multinomials:
-
-\[
-\frac{DCM_i^{frames}(f_{ij}=f, \mathbf{f}_{-ij})}{DCM_i^{frames}(\mathbf{f}_{-ij})}
-\]
-
-and
-
-\[
-\prod_a^{\{v,s,o\}}\frac{DCM_i^{vocab^a}(f_{ij}=f, \mathbf{f}_{-ij})}{DCM_i^{vocab^a}(\mathbf{f}_{-ij})}
-\]
 
@@
 \begin{align}
-& P(f_{ij} = f|\mathbf{f}_{-ij},\mathbf{w}, \alpha,\beta)\nonumber\\
+P(f_{ij} = f|\mathbf{f}_{-ij},\mathbf{w}, \alpha,\beta)
 &=\frac{\alpha + \tilde c(d_i,f)}{F\,\alpha + \tilde c(d_i)}
@@
 The number of frames in both models must be determined before induction.
-When choosing for a low number of frames the clusters will be big and thus the meaning of a cluster vague.
+When choosing for a low number of frames the clusters will be bigger and thus the meaning of a cluster more vague.
 But a high number of frames has, next to high computational costs also a danger of overfitting the data.
-When unrelated verbs occur with the same arguments often they will be clustered and maybe will even make up one cluster, while with a lower number of frames other verbs would be included, diinishing one of the unrelated verbs as noise.
+When unrelated verbs occur with the same arguments often they will be clustered and may even make up one cluster, while with a lower number of frames other verbs would be included, diminishing one of the unrelated verbs as noise.
 
-The alphas and betas are known \citep{oconnor2013} to be hard to determine, and therefore need experiments to be set to optimal values for a specific problem.
+The alphas and betas are known  to be hard to determine \citep{oconnor2013}, and therefore need experiments to be set to optimal values for a specific problem.
 We used, expensive but easy to implement, grid search to determine all parameters to test with.
 With grid-search a model is build with certain parameters, this model is then evaluated on a cross validation set.
-When all possible models are evaluated the highest scoring model is tested on.
+When all possible models are evaluated the highest scoring model is tested with a (kept aside) testset.
+We ran gridsearch for model 0 on 50 - 200 frames, with steps of 50, and $\alpha$ 0.1, 0.5, 1, 1.5, 2.
+Model 1 the same, and $\beta$ with values as $\alpha$
 
@@
 \label{results}
+
 \subsection{Frame Coherency}
-rame coherency: for a datapoint $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random choses verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$  
+The clusters of verbs are based on the arguments with which they are occuring in the data.
+So to test how well the models performed the probability of a triple in the testset, a real triple, should be greater than a triple with the verb replaced by a random one.
+This metric is the same as \citeauthor{rooth1999} used.
+More formally: for a datapoint $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random chosen verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$.
+The results are percentages of datapoints which satisfy this condition.
+Note though that if the random verb-triple is assigned the same frame as its `parent' real triple, this metric loses its meaning, but since the number of frames is high this probabilty is low.
+Furthermore, one can assume that the occurences of same frame assignement cancel eachother out, i.e.
+the random triple has higher probabilty than the real one as many times as vice versa.
+
 \subsection{Frame Correctness}

### 2014-12-31 Paper/paperN.tex
added FrameNet/DiceSim section (can add more or remove/shrink this depending on the pagecount situation), other minor edits

@@
 
-The Framenet project \citep{framenet} is ongoing on defining frames manually which could be mapped on a text to extrct frames.
-But with the increasing amount of digital information it is usefull to have auomatic semantic frame induction, since new words can be added to a language and meanings can change.
+The FrameNet project \citep{framenet} is an ongoing manual effort to define frames which could be mapped on a text to extract frames.
+But with the increasing amount of digital information, not to mention the inherent tediousness of building such a resource one word at a time, the prospect of (partially or completely) automating semantic frame induction is enticing.
+An automatic system could provide more complete descriptions of frames in current document banks and could better adapt to new words and evolving meanings.
 
-In this project we investigate wheter probabalistic latent-variable models can cluster verbs (as being a predicate) based on their meaning, which is inferred from the occurences of arguments it is encountered with.
+In this project we investigate whether probabalistic latent-variable models can cluster verbs (as being a predicate) based on their meaning, which is inferred from the occurences of arguments it is encountered with.
 The clusters then make up the broader meaning of the predicates.
@@
 % I (Eli) can expond here on the relation/contrast/etc.
-%   between what we're doing and Framenet;
+%   between what we're doing and FrameNet;
 %   I think O'Connor brings up some technical and/or methodological points
@@
 
-Frame correctness: for the top 25 most probable verbs per frame $TV$ and framenet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
+%\subsection{Relation to FrameNet}
+
+The FrameNet project is a manually compiled and annotated database for frame semantics.
+It tracks frames, the cast of elements that play specified roles within each frame, individual word-senses (``lexical units'' in FrameNet-speak) that instantiate those elements, certain relationships between frames, examples, etc.
+
+We want to compare our induced frames to FrameNet's manually annotated (i.e. correct) frames.
+In our case, we restrict our attention to sets of verbs.
+The idea is that if the verb groups identified by our model are actually groups that belong together in a frame, there should be a FrameNet frame that includes these verbs as well.
+Inclusion of a word in FrameNet frame for us simply means that the word is a lexical unit for that frame; since lexical units are tagged with parts of speech, extracting verbsets for each frame is simple.
+%Following the example of \citeauthor{oconnor2013}, we do not consider FrameNet frames with a very small number of verbs
+
+We can thus compute a rough ``correctness'' measure for our models' induced frames by comparing their verbsets with the verbsets extracted from FrameNet, using the Dice coefficient as a similarity measure.
+For verbsets $M$ and $F$ of some model-induced frame and some FrameNet frame, respectively, their Dice similarity is \[\frac{2|M\cap F|}{|M|+|F|}\]
+% Dice has certain properties that work well in this situation.
+For each FrameNet frame, we can find the frame given by our model that is most Dice-similar.
+Ideally, we want each FrameNet frame to have a high-scoring match among the frames of our model.
+%and also for these matches not to be identical
+
+One issue with implementing this measure is that our models return probability distributions, not verbsets.
+Specifically, for each induced frame, we have a distribution over all verbs from our dataset.
+To compare these frames with those from FrameNet using Dice, however, we need to turn these distributions into discrete sets, and there is not a clear method to do this.
+%(It is important to keep in mind that the collection of verbsets is not a partition on the set of all verbs appearing in the data, since each verb can appear in more than one frame (indeed, some of the most interesting test cases for automated frame inductors involve such multi-frame verbs).)
+We can take the most probable $n$ (say, five) verbs for each frame, but this will likely run into problems in the case of both high-population and low-population frames.
+Alternatively, we can take verbs within a given frame with a probability greater than some threshold value $p$ (say, $0.02$), which may perform better in certain cases but risks returning empty verbsets for frames with distributions that are particularly spread out.
+
+There are some substantial methodological issues with this approach even if it does function as a general evaluation method.
+
+Although many frames are events and thus commonly feature verbs as core elements, FrameNet is not verb-centric by design. Some frames do not encompass events and include no verbs at all.
+FrameNet also imposes inheritance relations between frames. Our model could potentially identify verbsets that have these relations, though it has no way of recognizing it has done so.
+In short, to use FrameNet's data, we end up discarding most of the information in the annotations and using only a fraction of the frames and lexical units.
+Arguably this is not so much of an issue so long as the extracted verbsets are still useful in evaluating our own model, even if the FrameNet data is being used in an idiosyncratic way.
+
+Perhaps a more important point, though, is that completeness is not a primary goal for FrameNet.
+Not every English word is included as a lexical unit, and not all words that are included are fully annotated with all their senses as lexical units in appropriate frames.
+In practice this means that if our model induces a certain verbset that does constitute a coherent semantic frame, but some of the verbs in the set do not show up in the FrameNet data for whatever reason, that frame's Dice score will suffer.
+%
+
+On a more abstract level, to what extent do lower similarity scores with FrameNet necessarily mean our model has identified frames that are semantically ``incorrect'' as opposed to frames which are in a sense orthogonal?
+% Does this make sense? Maybe this should go in "Discussion"..?
+
+%Frame correctness: for the top 25 most probable verbs per frame $TV$ and framenet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
 
 \subsection{Model 0}
+
 \subsection{Model 1}

### 2015-01-03 Paper/paperN.tex
bit of rewriting

@@
 \section{Introduction}
-The growing number of digital publications contains so much information that a single human being cannot process all this text, its even hard to keep up to date on a particular topic.
-It would be usefull to have technology that can create reliable summarizations.
-But not only quantity of information asks for such technology.
-For example for automatic stock trading systems, it would be usefull to know what is published about companies that are traded on the moment of publication.
+The growing number of digital publications contains too much information for a single human being to process, it is even hard to keep up to date on a particular topic.
+It would be usefull to be aided by technology that creates reliable summarizations.
+To ceate a summary is to extract the semantic content of a text and represent it in a human readable output.
+The first part of such a technology, extract semantic content, could also be an advantage for automatic stock trading systems.
+If it knows what is published about companies that is traded on the moment of publication it can make more profit.
 
-The problem can be illustrated with a simple example: \textit{'Alice buys a bread from the baker'} descibes the exact same situation as \textit{`The baker sells Alice a bread'}.
+Semantic content of a sentence can be represented in a frame.
+The main verbphrase of the sentence is the head of the frame and can be interpreted as predicate, representing the core of the episode described by the sentence, but the trick is to find out what the arguments of the predicate are.
+In linguistics argument selection is called case grammar \citep{dowty1991} and arguments (or roles) have specific names as \textit{agent - patient}.
+In computational systems names are not important and can be asigned when frame induction is complete.
+The problem of semantic content can be illustrated by this simple example: \textit{'Alice buys a bread from the baker'} descibes the exact same situation as \textit{`The baker sells Alice a bread'}.
 Thus the semantic content of these sentences can be represented in one frame, where the head of the frame represents the core of the episode or situation and involvement is expressed by assigning roles to things or people.
@@
 \end{wraptable}
-The head of the frame, representing the core of the episode, can naturally be represented as a predicate but the trick is to find out which words have which roles.
-In linguistics this is called case grammar \citep{dowty1991} and roles have specific names as \textit{agent - patient}.
-In systems the names are not important and can be asigned when frame induction is complete.
-
 As the example above shows, the roles are represented by different syntactic parts of speech in both sentences, the object and subject are switched, furthermore, the verbs are different.
-But even with knowledge of specific vebrs which bear the same meaning with switched subject/indirect-object, we need to have technology to let machines generate semantics next to syntacs in order to let machines be able to ( do as if they ) understand language and process new text in a meaningfull way.
-Hence, automatic semantic analysis and representation is required.
+But even with knowledge of specific vebrs which bear the same meaning with switched subject/indirect-object, we need to have technology to let machines generate semantic representations on top of syntacs in order to let machines be able to ( do as if they ) understand language and process new text in a meaningfull way.
+Hence, automatic semantic analysis and representation is required for further automatization.
 
@@
 
-In this project we investigate whether probabalistic latent-variable models can cluster verbs (as being a predicate) based on their meaning, which is inferred from the occurences of arguments it is encountered with.
-The clusters then make up the broader meaning of the predicates.
-The data we use contains triples of verb-subject-object (see section\ref{data}), so induced frames contain only two roles.
+In this project we investigate whether probabalistic latent-variable models can cluster verbs based on their meaning, which is inferred from the occurences of arguments it is encountered with.
+The clusters then make up a broader, but hopefully distinct, meaning.
+The data we use contains triples of verb-subject-object (see section \ref{data}), so induced frames contain only two roles.
 The models (described in section \ref{models}) induce frames based on the assumption the meaning of a verb relative to meaning of other verbs can be induced from its context.
 Hence the broader meaning is latent.
-To evaluate our models we use two metrics, one of which uses framenet data, the other to check wheter the resulting frames are coherent.
+To evaluate our models we use two metrics, one of which uses framenet data to check wheter the induced frames are similar to clusters of verbs in framenet, the other to check wheter the resulting frames are coherent, i.e.
+wheter the found clusters are not completely random.
 See section \ref{results} for more detail.
@@
 In the first article clustering is realized by applying expectation maximalization on a simple model.
-This model produces frames in the form of 3 distributions, one for the predicate and two for the arguments.
-Frame assignement is result of calculating  probabilities for a given tuple, the frame that gives the highest probaility is then the assigned.
+This model produces frames in the form of 3 distributions, one for the predicate, a distribution over verbs, and two for the arguments, one distribution over subjects one over objects.
+A triple is assigned to a frame if the probability of this triple is highest in this frame.
 We will use this model as our baseline (as in the O'Connor paper).
@@
 The difference with the baseline model is the assumption that a document uses a set of frames repeatedly as a rsult of a document having a (couple of) topics.
-In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.
+[TODO: needs some further explanantion] In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.
 
@@
 \section{Experiments}
-The number of frames in both models must be determined before induction.
+The number of frames in both models mustar to be determined before induction can take place.
 When choosing for a low number of frames the clusters will be bigger and thus the meaning of a cluster more vague.
-But a high number of frames has, next to high computational costs also a danger of overfitting the data.
-When unrelated verbs occur with the same arguments often they will be clustered and may even make up one cluster, while with a lower number of frames other verbs would be included, diminishing one of the unrelated verbs as noise.
+In contrast, a high number of frames bears the danger of overfitting the data, i.e.
+when unrelated verbs occur with the same arguments often they will be clustered and may even make up one cluster, while with a lower number of frames other verbs would be included, diminishing one of the unrelated verbs as noise.
 
@@
 We used, expensive but easy to implement, grid search to determine all parameters to test with.
-With grid-search a model is build with certain parameters, this model is then evaluated on a cross validation set.
-When all possible models are evaluated the highest scoring model is tested with a (kept aside) testset.
+Grid-search build for each posible parameter set a model which is evaluated on a cross validation set.
+The highest scoring model is tested with a (kept aside) testset.
 We ran gridsearch for model 0 on 50 - 200 frames, with steps of 50, and $\alpha$ 0.1, 0.5, 1, 1.5, 2.
@@
 The clusters of verbs are based on the arguments with which they are occuring in the data.
-So to test how well the models performed the probability of a triple in the testset, a real triple, should be greater than a triple with the verb replaced by a random one.
+So to test how well the models performed on clustering, the probability of a triple in the testset, a real triple, should be greater than this triple with a random verb replacing the original one.
 This metric is the same as \citeauthor{rooth1999} used.

### 2015-01-05 Paper/paperN.tex
Some copyedits and add an example.

@@
 \section{Introduction}
-The growing number of digital publications contains too much information for a single human being to process, it is even hard to keep up to date on a particular topic.
-It would be usefull to be aided by technology that creates reliable summarizations.
-To ceate a summary is to extract the semantic content of a text and represent it in a human readable output.
-The first part of such a technology, extract semantic content, could also be an advantage for automatic stock trading systems.
-If it knows what is published about companies that is traded on the moment of publication it can make more profit.
+The growing body of digital publications contains too much information for a single human being to process; it is even hard to keep up to date on a particular topic.
+It would be useful to be aided by technology that creates reliable summarizations.
+As a natural language processing task, summarization consists of two parts: first, extract the semantic content of a text, and then represent it in a condensed human readable output.
+The first part of such a technology, extracting semantic content, is what we deal with in this project.
+This step may also be useful on its own, for example, in automatic stock trading systems.
+Knowing what is published about publicly traded companies at the moment of publication can increase prophet margins for so-called high-frequnecy trading algorithms.
+Semantic representations have applications in other natural language procesing as well.
+For example, interlingua approaches to machine translation try to match sentences in the sorce and target language to a common generic semantic representation \cite{boas2005}.
 
 Semantic content of a sentence can be represented in a frame.
-The main verbphrase of the sentence is the head of the frame and can be interpreted as predicate, representing the core of the episode described by the sentence, but the trick is to find out what the arguments of the predicate are.
-In linguistics argument selection is called case grammar \citep{dowty1991} and arguments (or roles) have specific names as \textit{agent - patient}.
+The main verbphrase of the sentence is the head of the frame and can be interpreted as predicate, representing the core of the episode described by the sentence.
+The trick is to find out what the arguments of the predicate are.
+In linguistics, argument selection is called case grammar \citep{dowty1991} and arguments (or roles) have specific names as \textit{agent - patient}.
 In computational systems names are not important and can be asigned when frame induction is complete.
+
 The problem of semantic content can be illustrated by this simple example: \textit{'Alice buys a bread from the baker'} descibes the exact same situation as \textit{`The baker sells Alice a bread'}.
@@
 In general these roles can be anything like location, time, manner etc.
-For the sentences above the frame is depicted in \ref{framex}.
+The frame for the sentences above is depicted in table \ref{framex}.
 \begin{wraptable}{r}{.3\textwidth}
@@
 \end{wraptable}
-As the example above shows, the roles are represented by different syntactic parts of speech in both sentences, the object and subject are switched, furthermore, the verbs are different.
-But even with knowledge of specific vebrs which bear the same meaning with switched subject/indirect-object, we need to have technology to let machines generate semantic representations on top of syntacs in order to let machines be able to ( do as if they ) understand language and process new text in a meaningfull way.
+As the example above shows, the roles are represented by different syntactic parts of speech in both sentences: the object and subject are switched.
+Furthermore, the verbs are different.
+Even given the knowledge of specific verbs that bear the same meaning with switched subject/indirect-object, we need to generate semantic representations on top of syntax in order to let machines (act as if they) understand language and process new text in a meaningfull way.
 Hence, automatic semantic analysis and representation is required for further automatization.
 
-The FrameNet project \citep{framenet} is an ongoing manual effort to define frames which could be mapped on a text to extract frames.
+The FrameNet project \citep{framenet} is an ongoing manual effort to define frames which could be mapped onto text to give a semantic representation.
 But with the increasing amount of digital information, not to mention the inherent tediousness of building such a resource one word at a time, the prospect of (partially or completely) automating semantic frame induction is enticing.
@@
 
-In this project we investigate whether probabalistic latent-variable models can cluster verbs based on their meaning, which is inferred from the occurences of arguments it is encountered with.
-The clusters then make up a broader, but hopefully distinct, meaning.
+In this project we investigate whether probabalistic latent-variable models can cluster verbs based on their meaning, which is inferred from the arguments with wich it occurs.
+These clusters then make up a broader, but hopefully distinct, meaning.
 The data we use contains triples of verb-subject-object (see section \ref{data}), so induced frames contain only two roles.
@@
 The second paper covers multliple models of which we implemented one.
-The difference with the baseline model is the assumption that a document uses a set of frames repeatedly as a rsult of a document having a (couple of) topics.
+The difference with the baseline model is the assumption that a document uses a set of frames repeatedly as a result of a document having a (couple of) topics.
 [TODO: needs some further explanantion] In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.

### 2015-01-05 Paper/paperN.tex
add some to experiment section

@@
 We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}.
-In the first article clustering is realized by applying expectation maximalization on a simple model.
-This model produces frames in the form of 3 distributions, one for the predicate, a distribution over verbs, and two for the arguments, one distribution over subjects one over objects.
-A triple is assigned to a frame if the probability of this triple is highest in this frame.
+In the first article clustering is realized by applying expectation maximalization on a simple cooccurance model.
+This model produces frames in the form of two distributions, one for the predicate, a distribution over verbs, and one for the arguments, a nouns.
+Following O'Connor, we modify this model slightly to accomodate verb-subject-object triples.
+A triple is assigned to the frame for which is probability of occuring is highest.
 We will use this model as our baseline (as in the O'Connor paper).
-The second paper covers multliple models of which we implemented one.
-The difference with the baseline model is the assumption that a document uses a set of frames repeatedly as a result of a document having a (couple of) topics.
-[TODO: needs some further explanantion] In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.
+The second paper covers two additional models, of which we implemented one.
+This model differs from the baseline model by introducing the assumption that a document generates sentences frome a restricted set of frames.
+This assumption is justified (as in latent Dirichelt allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics.
+In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.
 
@@
 from verb-subject-object tripples (VSO's).
-The goal of these models is to use th syntactic information give by a VSO to
+The goal of these models is to use the syntactic information given by a VSO to
 infer what kind of event it describes (i.e., to which semantic frame it belongs).
@@
 
-The approach models each VSO independenly, without considering any further context.
+This approach models each VSO independenly, without considering any further context.
 Word distributions are completely independent between arguments and accross frames.
 Tuples are clustered according to which frame's three distributions best fit the 
-three arguments.
+three arguments; that is,
 
-Model 0 is based on one originally proposed in \citet{rooth1999}, which 
+\[
+f_{v,s,o} = \argmax_f P(v|\phi_f^v) \times P(s|\phi_f^s) \times P(o|\phi_f^o)
+\]
+
+Model 0 is based on the apporach originally proposed in \citet{rooth1999}, which 
 considers noun-verb pairs. Following \citet{oconnor2013}, we expand the model
@@
 know from topic modeling that LDA with Gibbs sampling can be very successful at
-classifying documents according to some semantic features \citep{griffiths2004}.
+classifying documents according to some semantic features \citep{blei2003}.
 Model 1 leverages this fact by making the assmumption that a given document is 
@@
 \section{Experiments}
-The number of frames in both models mustar to be determined before induction can take place.
+The number of frames in both models must be determined before induction can take place.
 When choosing for a low number of frames the clusters will be bigger and thus the meaning of a cluster more vague.
@@
 when unrelated verbs occur with the same arguments often they will be clustered and may even make up one cluster, while with a lower number of frames other verbs would be included, diminishing one of the unrelated verbs as noise.
+Following \citet{rooth1999}, we estimate that the appropriate number of frames to induce is at most a couple hundred.
+This assumption is based on philosophical arguments of Jerry Fodor, who proposes that there should be a very limited degree of genuine interdefinability between lexical items (here frames), and that the magnitude of the lexicon should therefore be approximately equal to the number of basic concepts \citep{fodor1998}.
 
-The alphas and betas are known  to be hard to determine \citep{oconnor2013}, and therefore need experiments to be set to optimal values for a specific problem.
-We used, expensive but easy to implement, grid search to determine all parameters to test with.
-Grid-search build for each posible parameter set a model which is evaluated on a cross validation set.
-The highest scoring model is tested with a (kept aside) testset.
-We ran gridsearch for model 0 on 50 - 200 frames, with steps of 50, and $\alpha$ 0.1, 0.5, 1, 1.5, 2.
-Model 1 the same, and $\beta$ with values as $\alpha$
+To facilitate the evaluation of our results, we split off two uniform random subsets of the data, the test set (\%10), and the cross-verb validation set (\%20).
+We trained the models on the remaining data (the training set).
+To train the baseline model (model 0), we ran the expectation maximization algorithm until the total change in the posterior probabilities for words plus the prior for frames was less that $0.01$.
+The trained model consists of $3\times|Frames|$ distributions: a distribution for each frame, for each argument.
+Model 1 is implemented using Gibbs sampling.
+We allowed $1000$ iterations of sampling, ignoring the first $50$ as \emph{burn in} (see \citet{raftery1992} for further discussion).
+Since we are less na\"ive about mapping syntactic positions to semantic roles, we combine the subject/object distributions, so model 1 gives $2\times|Frames|$ distributions: for each frame, one for verbs and one for nouns.
 
+The $\alpha$ and $\beta$ hyperparameters in model 1 are known  to be hard to determine \citep{oconnor2013}, and therefore need to be experimentally optimized for our specific problem.
+We used an expensive, but easy to implement grid search to determine the best values for $\alpha$ and $\beta$.
+The grid search builds, for each posible parameter set, a model which is evaluated on the cross validation set.
+The highest scoring model is tested with the test set.
+We ran grid search for model 0 on $50$ - $200$ frames, with steps of $50$, and $\alpha$ of $0.1, 0.5, 1, 1.5$, and $2$.
+The grid search for Model 1 was the the same, additionally testing $\beta$ accross the same values as $\alpha$
 \section{Results}
@@
 \subsection{Frame Coherency}
-The clusters of verbs are based on the arguments with which they are occuring in the data.
-So to test how well the models performed on clustering, the probability of a triple in the testset, a real triple, should be greater than this triple with a random verb replacing the original one.
-This metric is the same as \citeauthor{rooth1999} used.
+Verb clusters are based on the arguments with which they occuring in the data.
+So to test how well the models perform on clustering, the probability that the model generates a triple from the testset, should be greater than this triple with a random verb in place of the real one.
+This metric is the same as the one used by \citeauthor{rooth1999}.
 More formally: for a datapoint $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random chosen verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$.

### 2015-01-05 Paper/paperN.tex
only thing left: conclusion + spell check

@@
 \begin{abstract}
-The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
-right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
-The word \textbf{Abstract} must be centered, bold, and in point size 12. Two
-line spaces precede the abstract. The abstract must be limited to one
-paragraph.
+  Information in text can be represented by frames.
+A frame consists of a predicate with arguments.
+In this report we discuss two probabilistic latent variable models which are trained by resp.
+expectation maximization and Gibbs sampling, to induce frames from syntactic tri-grams of the form: verb, subject, object.
+The latent variable is the frame a verb belongs to.
+In practice, the models cluster verbs based on the occurrences of arguments they are encountered with.
+The frames (or clusters of verbs) are measured by correctness (relative to each other) and correctness (relative to FrameNet clusters).
+The more suffisticated second model performs well and finds clusters of verbs which have a distinct general meaning, the frames induced with the simple model 0 are not as well defined as thos of model 1.
 \end{abstract}
@@
 This model differs from the baseline model by introducing the assumption that a document generates sentences frome a restricted set of frames.
-This assumption is justified (as in latent Dirichelt allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics.
+This assumption is justified (as in latent Dirichelt allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics and thus use a proper subset of the frames.
 In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.
@@
 %Frame correctness: for the top 25 most probable verbs per frame $TV$ and framenet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
+\section{Results}
+These results are experimental, i.e.
+the parameters are guessed and therefor probably not optimal.
+(Since gridsearchis more expensive than planned for the actual results are still in progress.) In this experiment the frames were put on $200$, $\alpha$ and $\beta$ both on $0.5$.\\
+\begin{table}[h]
+\begin{tabular}{|l||c|c|}
+  \hline
+  &dicesim&coherencey\\
+  \hline
+  \hline
+  model 0& 0.28&19\%  \\
+  \hline
+  model 1&0.29 &71\%  \\
+  \hline
+\end{tabular}
+\caption{results}
+\label{results}
+\end{table}
 
-\subsection{Model 0}
-
-\subsection{Model 1}
+\begin{table}
+\begin{tabular}{|p{.3\textwidth}|p{.7\textwidth}|}
+  \hline
+  \textit{frame predicate} & \textit{verbs in frame}\\
+  \hline
+  \hline
+  knowledge transfer & explain, assure, arrange, acquaint\\
+  \hline
+  legal accusation & prove, bother, condemn, accuse, dislike, gainsay, hypnotize\\
+  \hline
+  things to do with problems & solve, create, design, acquit, administer, invest, exit, recount, preview, consist\\
+  \hline
+  affection & love, hate\\
+  \hline
+  harming anotherly &fight, shoot, invite, harm, commend, chase, seem, favour, reconstruct, pitch, request, inconvenience, redress, hitch, air, slow, disarm, strive, despoil, pique, tote, halt, bit, implicate\\
+  \hline
+  enjoyment & enjoy, please, bow, amount\\
+  \hline
+\end{tabular}
+\label{exframes}
+\caption{Frame examples}
+\end{table}
 
 \section{Discussion}
+As table \ref{results} show, coherency  improved significantly, whereas the frame correctness did not so much.
+But the frames induced by model 0 do not cover all verbs, actually only 3 verbs are asigned to a frame.
+It is not clear why this happens, but this are still only experimental results.
+Since there are 200 frames it is obvious that the coherency is so low.
+Other experiments have shown that it is possible to cluster with model 0 though.
+
+The frames in table \ref{exframes} are frames induced by model 1 and are meaningfull in the sense that they consist of clusters of verbs that seem to have a similar meaning.
+Nontheless, in \textit{harming anotherly} there are verbs which would be better left out.
+They are assigned this frame though because they occurred in company of the same arguments often.
+The affection frame is remarkable since these are exactly opposites.
+This happens in some form in more frames though and can be explained by the fact that verbs with opposite meanings are used with the same arguments, this can be seen as a weakness of the model.
+
+Furthermore auxilary verbs get mostly assigned a complete frame, i.e.
+they are the only verb assigned to a frame.
+Other verbs like \textit{(say, get, find, bring, make, see, ask, take, have, mean, use, like, hear, understand, afford, help, call, know, give, do, tell, find)} also get assigned a complete frame.
+This is most likely caused by the fact that these verbs can have a wide range of arguments, and are in the sense of meaning-of-a-verb by nouns it is encountered with, sort of meaningless.
+This is again a weakness of the model, but could possibly be diminished with more data.
 
@@
 
+\section*{Who did what}
+We all tried to work as much as possible and neccesary on the project.
+Bill had a leading role in building the models.
+Model 1 is completely build and implemented by Bill.
+Jacob implemented frame coherency and Eli frame correctness.
+Everybody ran some experiments and Jacob is still running grid search (made a big estimation error in cost of gridsearch).
+Any section is written by the one who implemented this particular part.
+The rest of the sections are composed of bits of everybody.
+
 \bibliography{refs.bib}

### 2015-01-05 Paper/paperN.tex
spell check, abstract

--- 2015-01-05 Paper/paperN.tex
@@
 \begin{abstract}
-The abstract paragraph should be indented 1/2~inch (3~picas) on both left and
-right-hand margins. Use 10~point type, with a vertical spacing of 11~points.
-The word \textbf{Abstract} must be centered, bold, and in point size 12. Two
-line spaces precede the abstract. The abstract must be limited to one
-paragraph.
+We explore two models for the unsupervised induction of semantic frames on a 
+very large corpus of verb-subject-object triples. Our work is bade on previous 
+research that has had success on smaller, more focused data sets. By encouraging 
+verb sparsity with a Dirichlet prior, one can improve on the results of our 
+baseline model. We give some analysis of the frames that the improved model 
+discovers, and suggest areas for further development.
 \end{abstract}
@@
 This step may also be useful on its own, for example, in automatic stock trading systems.
-Knowing what is published about publicly traded companies at the moment of publication can increase prophet margins for so-called high-frequnecy trading algorithms.
-Semantic representations have applications in other natural language procesing as well.
-For example, interlingua approaches to machine translation try to match sentences in the sorce and target language to a common generic semantic representation \cite{boas2005}.
+Knowing what is published about publicly traded companies at the moment of publication can increase prophet margins for so-called high-frequency trading algorithms.
+Semantic representations have applications in other natural language processing as well.
+For example, interlingua approaches to machine translation try to match sentences in the source and target language to a common generic semantic representation \cite{boas2005}.
 
 Semantic content of a sentence can be represented in a frame.
-The main verbphrase of the sentence is the head of the frame and can be interpreted as predicate, representing the core of the episode described by the sentence.
+The main verb phrase of the sentence is the head of the frame and can be interpreted as predicate, representing the core of the episode described by the sentence.
 The trick is to find out what the arguments of the predicate are.
 In linguistics, argument selection is called case grammar \citep{dowty1991} and arguments (or roles) have specific names as \textit{agent - patient}.
-In computational systems names are not important and can be asigned when frame induction is complete.
+In computational systems names are not important and can be assigned when frame induction is complete.
 
-The problem of semantic content can be illustrated by this simple example: \textit{'Alice buys a bread from the baker'} descibes the exact same situation as \textit{`The baker sells Alice a bread'}.
+The problem of semantic content can be illustrated by this simple example: \textit{'Alice buys a bread from the baker'} describes the exact same situation as \textit{`The baker sells Alice a bread'}.
 Thus the semantic content of these sentences can be represented in one frame, where the head of the frame represents the core of the episode or situation and involvement is expressed by assigning roles to things or people.
@@
 Furthermore, the verbs are different.
-Even given the knowledge of specific verbs that bear the same meaning with switched subject/indirect-object, we need to generate semantic representations on top of syntax in order to let machines (act as if they) understand language and process new text in a meaningfull way.
+Even given the knowledge of specific verbs that bear the same meaning with switched subject/indirect-object, we need to generate semantic representations on top of syntax in order to let machines (act as if they) understand language and process new text in a meaningful way.
 Hence, automatic semantic analysis and representation is required for further automatization.
@@
 
-In this project we investigate whether probabalistic latent-variable models can cluster verbs based on their meaning, which is inferred from the arguments with wich it occurs.
+In this project we investigate whether probabilistic latent-variable models can cluster verbs based on their meaning, which is inferred from the arguments with which it occurs.
 These clusters then make up a broader, but hopefully distinct, meaning.
@@
 Hence the broader meaning is latent.
-To evaluate our models we use two metrics, one of which uses framenet data to check wheter the induced frames are similar to clusters of verbs in framenet, the other to check wheter the resulting frames are coherent, i.e.
-wheter the found clusters are not completely random.
+To evaluate our models we use two metrics, one of which uses framenet data to check whether the induced frames are similar to clusters of verbs in framenet, the other to check whether the resulting frames are coherent, i.e.
+whether the found clusters are not completely random.
 See section \ref{results} for more detail.
@@
 We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}.
-In the first article clustering is realized by applying expectation maximalization on a simple cooccurance model.
+In the first article clustering is realized by applying expectation maximization on a simple cooccurance model.
 This model produces frames in the form of two distributions, one for the predicate, a distribution over verbs, and one for the arguments, a nouns.
-Following O'Connor, we modify this model slightly to accomodate verb-subject-object triples.
-A triple is assigned to the frame for which is probability of occuring is highest.
+Following O'Connor, we modify this model slightly to accommodate verb-subject-object triples.
+A triple is assigned to the frame for which is probability of occurring is highest.
 We will use this model as our baseline (as in the O'Connor paper).
 The second paper covers two additional models, of which we implemented one.
-This model differs from the baseline model by introducing the assumption that a document generates sentences frome a restricted set of frames.
-This assumption is justified (as in latent Dirichelt allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics.
+This model differs from the baseline model by introducing the assumption that a document generates sentences frame a restricted set of frames.
+This assumption is justified (as in latent Dirichlet allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics.
 In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.
@@
 \label{models}
-We consider two probabalistic latent-variable models that learn semantic frames
-from verb-subject-object tripples (VSO's).
+We consider two probabilistic latent-variable models that learn semantic frames
+from verb-subject-object triples (VSO's).
 The goal of these models is to use the syntactic information given by a VSO to
@@
     For each document $d=1..D$:\\
-    \hspace*{15pt} Draw a distrbution $\theta_d \sim Dirichlet(\alpha)$\\
+    \hspace*{15pt} Draw a distribution $\theta_d \sim Dirichlet(\alpha)$\\
     \hspace*{30pt} For each $i = 1..N^d$:\\
@@
 
-This approach models each VSO independenly, without considering any further context.
-Word distributions are completely independent between arguments and accross frames.
+This approach models each VSO independently, without considering any further context.
+Word distributions are completely independent between arguments and across frames.
 Tuples are clustered according to which frame's three distributions best fit the 
@@
 
-Model 0 is based on the apporach originally proposed in \citet{rooth1999}, which 
+Model 0 is based on the approach originally proposed in \citet{rooth1999}, which 
 considers noun-verb pairs. Following \citet{oconnor2013}, we expand the model
@@
 classifying documents according to some semantic features \citep{blei2003}.
-Model 1 leverages this fact by making the assmumption that a given document is 
+Model 1 leverages this fact by making the assumption that a given document is 
 likely to have a sparse distribution of frames. As in LDA, the document-level
-sparsity is enforced by a dirichlet prior on frame distributions (see figure
+sparsity is enforced by a Dirichlet prior on frame distributions (see figure
 \ref{gen1} for details). This assumption breaks the independence between tuples 
@@
 \times \int_\theta P(\mathbf{f}|\theta)\,P(\theta|\alpha)\\
-\intertext{These integrals are both dirichlet multinomials:}
+\intertext{These integrals are both Dirichlet multinomials:}
 &=\frac{DCM_i^{frames}(f_{ij}=f, \mathbf{f}_{-ij})}{DCM_i^{frames}(\mathbf{f}_{-ij})}\times
@@
 (i.e., $V^s = V^o$). This is more in line with the theory of semantic frames 
-since in principle, a noun playing a particlar semantic role may appear in either 
+since in principle, a noun playing a particular semantic role may appear in either 
 syntactic position.
@@
 
-The data used in this probject (see section \ref{data}) doesn't contain any document-level
+The data used in this project (see section \ref{data}) doesn't contain any document-level
 information. As a result, we adapt model 1 by grouping VSOs with the same verb into ``documents''.
-This move leverages the dirichlet prior $\alpha$ to enforce sparcity of frames 
-accross verbs, but of course cannot capture the information given by the kind of
+This move leverages the Dirichlet prior $\alpha$ to enforce sparsity of frames 
+across verbs, but of course cannot capture the information given by the kind of
 document-level semantic sparsity seen in LDA.\footnote{When we use verbs as
@@
 books and labled with Penn Treebank part-of-speech tags Stanford-basic dependency 
-lables \citep{ngrams2013}.
+labels \citep{ngrams2013}.
 Each ngram also includes frequency counts by year.
@@
 When choosing for a low number of frames the clusters will be bigger and thus the meaning of a cluster more vague.
-In contrast, a high number of frames bears the danger of overfitting the data, i.e.
+In contrast, a high number of frames bears the danger of over-fitting the data, i.e.
 when unrelated verbs occur with the same arguments often they will be clustered and may even make up one cluster, while with a lower number of frames other verbs would be included, diminishing one of the unrelated verbs as noise.
@@
 We ran grid search for model 0 on $50$ - $200$ frames, with steps of $50$, and $\alpha$ of $0.1, 0.5, 1, 1.5$, and $2$.
-The grid search for Model 1 was the the same, additionally testing $\beta$ accross the same values as $\alpha$
+The grid search for Model 1 was the the same, additionally testing $\beta$ across the same values as $\alpha$
 \section{Results}
@@
 \subsection{Frame Coherency}
-Verb clusters are based on the arguments with which they occuring in the data.
+Verb clusters are based on the arguments with which they occurring in the data.
 So to test how well the models perform on clustering, the probability that the model generates a triple from the testset, should be greater than this triple with a random verb in place of the real one.
@@
 More formally: for a datapoint $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random chosen verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$.
-The results are percentages of datapoints which satisfy this condition.
-Note though that if the random verb-triple is assigned the same frame as its `parent' real triple, this metric loses its meaning, but since the number of frames is high this probabilty is low.
-Furthermore, one can assume that the occurences of same frame assignement cancel eachother out, i.e.
-the random triple has higher probabilty than the real one as many times as vice versa.
+The results are percentages of data points which satisfy this condition.
+Note though that if the random verb-triple is assigned the same frame as its `parent' real triple, this metric loses its meaning, but since the number of frames is high this probability is low.
+Furthermore, one can assume that the occurrences of same frame assignment cancel each other out, i.e.
+the random triple has higher probability than the real one as many times as vice versa.
 
@@
 we could not used document-level context to infer semantic information.
-A possible direction of future reseach is to create models that take better 
+A possible direction of future research is to create models that take better 
 advantage of the syntax-level context provided by syntactic ngrams. 
@@
 in the verbargs dataset and their relation to one another.
-For example, you could be gleen some semantic information about the relationship between
+For example, you could be glean some semantic information about the relationship between
 verbs and prepositional objects by looking at the preposition that mediates them: 

### 2015-01-05 evaluation.py

@@ -13,6 +13,24 @@ def frames_by_frequency(frame_dists):
         frame_freq[f].sort(key=lambda x: x[1], reverse=True)
     return frame_freq
 
+def m0_to_dists(m0):
+    frame_dists = m0[0]
+    F = len(frame_dists)
+    frame_dists_v = {f:{} for f in range(F)}
+    frame_dists_w = {f:{} for f in range(F)}
+    for f in range(F):
+        for v in frame_dists[f]['v']:
+            frame_dists_v[f][v] = frame_dists[f]['v'][v]
+        for s in frame_dists[f]['s']:
+            frame_dists_w[f][s] = frame_dists[f]['s'][s]/2
+        for o in frame_dists[f]['o']:
+            if o in frame_dists_w[f]:
+                frame_dists_w[f][o] += frame_dists[f]['o'][o]/2
+            else:
+                frame_dists_w[f][o] = frame_dists[f]['o'][o]/2
+    return(frame_dists_v, frame_dists_w)
+
+
 def show_most_common(frame_dists_v, frame_dists_w, top=25):
 
     frame_freq_v = frames_by_frequency(frame_dists_v)

### 2015-01-05 grid_search.py

@@ -72,4 +72,4 @@ def verb_dists(model):
 
     return verb_dists
 
-test()
+#test()

### 2015-01-05 runmodel0.py

@@ -1,4 +1,5 @@
 
+import pickle
 import argparse
 import model0
 
@@ -6,5 +7,11 @@ argparser = argparse.ArgumentParser()
 argparser.add_argument("-f","-F","--frames", help="number of frames to induce", type=int, required=True)
 argparser.add_argument("-a","--alpha", help="dirichlet prior for initializing word distributions", type=float, required=True)
 args = argparser.parse_args()
+frames = args.frames
+alpha = args.alpha
 
-model0.em(args.frames, args.alpha)
+data = pickle.load(open('trainingData.pkl', 'rb'))
+filename = "sample_m0_F"+str(frames)+"_alpha"+str(alpha)+".pkl"
+
+result = model0.em(frames, alpha, data)
+pickle.dump(result, open(filename, 'wb'))

### 2015-01-05 Paper/paperN.tex

@@
 discovers, and suggest areas for further development.
+
+  Information in text can be represented by frames.
+A frame consists of a predicate with arguments.
+In this report we discuss two probabilistic latent variable models which are trained by resp.
+expectation maximization and Gibbs sampling, to induce frames from syntactic tri-grams of the form: verb, subject, object.
+The latent variable is the frame a verb belongs to.
+In practice, the models cluster verbs based on the occurrences of arguments they are encountered with.
+The frames (or clusters of verbs) are measured by correctness (relative to each other) and correctness (relative to FrameNet clusters).
+The more suffisticated second model performs well and finds clusters of verbs which have a distinct general meaning, the frames induced with the simple model 0 are not as well defined as thos of model 1.
 \end{abstract}
@@
 We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}.
-In the first article clustering is realized by applying expectation maximization on a simple cooccurance model.
+In the first article clustering is realized by applying expectation maximalization on a simple cooccurance model.
 This model produces frames in the form of two distributions, one for the predicate, a distribution over verbs, and one for the arguments, a nouns.
-Following O'Connor, we modify this model slightly to accommodate verb-subject-object triples.
-A triple is assigned to the frame for which is probability of occurring is highest.
+Following O'Connor, we modify this model slightly to accomodate verb-subject-object triples.
+A triple is assigned to the frame for which is probability of occuring is highest.
 We will use this model as our baseline (as in the O'Connor paper).
 The second paper covers two additional models, of which we implemented one.
-This model differs from the baseline model by introducing the assumption that a document generates sentences frame a restricted set of frames.
-This assumption is justified (as in latent Dirichlet allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics.
+This model differs from the baseline model by introducing the assumption that a document generates sentences frome a restricted set of frames.
+This assumption is justified (as in latent Dirichelt allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics and thus use a proper subset of the frames.
 In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.

### 2015-01-05 Paper/paperN.tex
final version

@@
 \begin{abstract}
-We explore two models for the unsupervised induction of semantic frames on a 
-very large corpus of verb-subject-object triples. Our work is bade on previous 
-research that has had success on smaller, more focused data sets. By encouraging 
-verb sparsity with a Dirichlet prior, one can improve on the results of our 
-baseline model. We give some analysis of the frames that the improved model 
-discovers, and suggest areas for further development.
-
   Information in text can be represented by frames.
@@
 The frames (or clusters of verbs) are measured by correctness (relative to each other) and correctness (relative to FrameNet clusters).
-The more suffisticated second model performs well and finds clusters of verbs which have a distinct general meaning, the frames induced with the simple model 0 are not as well defined as thos of model 1.
+The more sophisticated second model performs well and finds clusters of verbs which have a distinct general meaning, the frames induced with the simple model 0 are not as well defined as those of model 1.
 \end{abstract}
@@
 Semantic content of a sentence can be represented in a frame.
-The main verb phrase of the sentence is the head of the frame and can be interpreted as predicate, representing the core of the episode described by the sentence.
+The main verbphrase of the sentence is the head of the frame and can be interpreted as predicate, representing the core of the episode described by the sentence.
 The trick is to find out what the arguments of the predicate are.
@@
 We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}.
-In the first article clustering is realized by applying expectation maximalization on a simple cooccurance model.
+In the first article clustering is realized by applying expectation maximalization on a simple co-occurance model.
 This model produces frames in the form of two distributions, one for the predicate, a distribution over verbs, and one for the arguments, a nouns.
-Following O'Connor, we modify this model slightly to accomodate verb-subject-object triples.
-A triple is assigned to the frame for which is probability of occuring is highest.
+Following O'Connor, we modify this model slightly to accommodate verb-subject-object triples.
+A triple is assigned to the frame for which is probability of occurring is highest.
 We will use this model as our baseline (as in the O'Connor paper).
 The second paper covers two additional models, of which we implemented one.
-This model differs from the baseline model by introducing the assumption that a document generates sentences frome a restricted set of frames.
-This assumption is justified (as in latent Dirichelt allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics and thus use a proper subset of the frames.
+This model differs from the baseline model by introducing the assumption that a document generates sentences from a restricted set of frames.
+This assumption is justified (as in latent Dirichlet allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics and thus use a proper subset of the frames.
 In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.
@@
 likely to have a sparse distribution of frames. As in LDA, the document-level
-sparsity is enforced by a Dirichlet prior on frame distributions (see figure
+sparsity is enforced by a dirichlet prior on frame distributions (see figure
 \ref{gen1} for details). This assumption breaks the independence between tuples 
@@
 \times \int_\theta P(\mathbf{f}|\theta)\,P(\theta|\alpha)\\
-\intertext{These integrals are both Dirichlet multinomials:}
+\intertext{These integrals are both dirichlet multinomials:}
 &=\frac{DCM_i^{frames}(f_{ij}=f, \mathbf{f}_{-ij})}{DCM_i^{frames}(\mathbf{f}_{-ij})}\times
@@
 information. As a result, we adapt model 1 by grouping VSOs with the same verb into ``documents''.
-This move leverages the Dirichlet prior $\alpha$ to enforce sparsity of frames 
+This move leverages the dirichlet prior $\alpha$ to enforce sparcity of frames 
 across verbs, but of course cannot capture the information given by the kind of
@@
 Google syntactic-ngrams is a corpus of ngrams extracted from 3.5 million English language 
-books and labled with Penn Treebank part-of-speech tags Stanford-basic dependency 
+books and labeled with Penn Treebank part-of-speech tags Stanford-basic dependency 
 labels \citep{ngrams2013}.
@@
 
-This project uses the verbargs subeset (130M items) of Google syntactic-ngrams.
+This project uses the verbargs subset (130M items) of Google syntactic-ngrams.
 An ngram in the verbargs dataset consist of a verb and all of its 
@@
 
-The $\alpha$ and $\beta$ hyperparameters in model 1 are known  to be hard to determine \citep{oconnor2013}, and therefore need to be experimentally optimized for our specific problem.
+The $\alpha$ and $\beta$ hyper-parameters in model 1 are known  to be hard to determine \citep{oconnor2013}, and therefore need to be experimentally optimized for our specific problem.
 We used an expensive, but easy to implement grid search to determine the best values for $\alpha$ and $\beta$.
-The grid search builds, for each posible parameter set, a model which is evaluated on the cross validation set.
+The grid search builds, for each possible parameter set, a model which is evaluated on the cross validation set.
 The highest scoring model is tested with the test set.
@@
 Verb clusters are based on the arguments with which they occurring in the data.
-So to test how well the models perform on clustering, the probability that the model generates a triple from the testset, should be greater than this triple with a random verb in place of the real one.
+So to test how well the models perform on clustering, the probability that the model generates a triple from the test-set, should be greater than this triple with a random verb in place of the real one.
 This metric is the same as the one used by \citeauthor{rooth1999}.
-More formally: for a datapoint $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random chosen verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$.
-The results are percentages of data points which satisfy this condition.
+More formally: for a data-point $(v,s,o)$ and a tuple $(v^r,s,o)$ where $v^r$ is a random chosen verb: $P(v\mid s,o) \geq P(v^r\mid s,o)$.
+The results are percentages of data-points which satisfy this condition.
 Note though that if the random verb-triple is assigned the same frame as its `parent' real triple, this metric loses its meaning, but since the number of frames is high this probability is low.
@@
 the parameters are guessed and therefor probably not optimal.
-(Since gridsearchis more expensive than planned for the actual results are still in progress.) In this experiment the frames were put on $200$, $\alpha$ and $\beta$ both on $0.5$.\\
+(Since grid-search is more expensive than planned for the actual results are still in progress.) In this experiment the frames were put on $200$, $\alpha$ and $\beta$ both on $0.5$.\\
 \begin{table}[h]
@@
   \hline
-  &dicesim&coherencey\\
+  &dicesim&coherency\\
   \hline
@@
 As table \ref{results} show, coherency  improved significantly, whereas the frame correctness did not so much.
-But the frames induced by model 0 do not cover all verbs, actually only 3 verbs are asigned to a frame.
+But the frames induced by model 0 do not cover all verbs, actually only 3 verbs are assigned to a frame.
 It is not clear why this happens, but this are still only experimental results.
@@
 
-The frames in table \ref{exframes} are frames induced by model 1 and are meaningfull in the sense that they consist of clusters of verbs that seem to have a similar meaning.
-Nontheless, in \textit{harming anotherly} there are verbs which would be better left out.
+The frames in table \ref{exframes} are frames induced by model 1 and are meaningful in the sense that they consist of clusters of verbs that seem to have a similar meaning.
+Nonetheless, in \textit{harming anotherly} there are verbs which would be better left out.
 They are assigned this frame though because they occurred in company of the same arguments often.
@@
 
-Furthermore auxilary verbs get mostly assigned a complete frame, i.e.
+Furthermore auxiliary verbs get mostly assigned a complete frame, i.e.
 they are the only verb assigned to a frame.
@@
 in the verbargs dataset and their relation to one another.
-For example, you could be glean some semantic information about the relationship between
+For example, you could glean some semantic information about the relationship between
 verbs and prepositional objects by looking at the preposition that mediates them: 
@@
 \section{Conclusion}
+Model 1 did find clusters of verbs of which the meaning can be covered by 1 predicate.
+Although the induced frames have often vague or broad meaning the approach works well if data is abundant.
+The improvement of model 1 on model 0 has a significant effect and implicates even better results can be acquired by further improvements.
+The kind of clustering done by these models, with opposites assigned to the same frame, can be usefull for automatic stock trading systems if implemented with sentiment analysis to split on opposites.
+The frames are too vague to use for summarizations though.
 
 \section*{Who did what}
-We all tried to work as much as possible and neccesary on the project.
+We all tried to work as much as possible and necessary on the project.
 Bill had a leading role in building the models.
@@
 Jacob implemented frame coherency and Eli frame correctness.
-Everybody ran some experiments and Jacob is still running grid search (made a big estimation error in cost of gridsearch).
+Everybody ran some experiments and Jacob is still running grid search (made a big estimation error in cost of grid-search).
 Any section is written by the one who implemented this particular part.

### 2015-01-05 Paper/paperN.tex
spelling, add to abstract

--- 2015-01-05 Paper/paperN.tex
@@
 \begin{abstract}
-We explore two models for the unsupervised induction of semantic frames on a 
-very large corpus of verb-subject-object triples. Our work is bade on previous 
-research that has had success on smaller, more focused data sets. By encouraging 
-verb sparsity with a Dirichlet prior, one can improve on the results of our 
-baseline model. We give some analysis of the frames that the improved model 
-discovers, and suggest areas for further development.
-
-  Information in text can be represented by frames.
-A frame consists of a predicate with arguments.
-In this report we discuss two probabilistic latent variable models which are trained by resp.
-expectation maximization and Gibbs sampling, to induce frames from syntactic tri-grams of the form: verb, subject, object.
-The latent variable is the frame a verb belongs to.
-In practice, the models cluster verbs based on the occurrences of arguments they are encountered with.
-The frames (or clusters of verbs) are measured by correctness (relative to each other) and correctness (relative to FrameNet clusters).
-The more suffisticated second model performs well and finds clusters of verbs which have a distinct general meaning, the frames induced with the simple model 0 are not as well defined as thos of model 1.
+  Semantic frames can be used to give a basic representation of a sentence's meaning.
+A frame consists of a predicate and its arguments.
+In this report we discuss two probabilistic latent variable models, which are trained by resp.
+expectation maximization and Gibbs sampling, to induce frames on syntactic tri-grams of the form verb, subject, object.
+The latent variable is the frame that the triple belongs to.
+In practice, the models cluster verbs based on the arguments with which they occur.
+The frames (or clusters of verbs) are measured for coherence (relative to each other) and correctness (relative to FrameNet clusters).
+By encouraging verb sparsity with a Dirichlet prior, the more sophisticated second model improves on our baseline.
+These results support similar findings in research where much smaller, more topically focused datasets were used.
+Finally, we give some analysis of the frames that our improved model discovers and suggest areas for further development.
 \end{abstract}
@@
 We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}.
-In the first article clustering is realized by applying expectation maximalization on a simple cooccurance model.
+In the first article clustering is realized by applying expectation maximization on a simple co-occurance model.
 This model produces frames in the form of two distributions, one for the predicate, a distribution over verbs, and one for the arguments, a nouns.
-Following O'Connor, we modify this model slightly to accomodate verb-subject-object triples.
-A triple is assigned to the frame for which is probability of occuring is highest.
+Following O'Connor, we modify this model slightly to accommodate verb-subject-object triples.
+A triple is assigned to the frame for which is probability of occurring is highest.
 We will use this model as our baseline (as in the O'Connor paper).
 The second paper covers two additional models, of which we implemented one.
-This model differs from the baseline model by introducing the assumption that a document generates sentences frome a restricted set of frames.
-This assumption is justified (as in latent Dirichelt allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics and thus use a proper subset of the frames.
+This model differs from the baseline model by introducing the assumption that a document generates sentences frame a restricted set of frames.
+This assumption is justified (as in latent Dirichlet allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics and thus use a proper subset of the frames.
 In our data the tuples are not annotated with documents so we used this assumption in such a way that each verb covers one document.
@@
 We used an expensive, but easy to implement grid search to determine the best values for $\alpha$ and $\beta$.
-The grid search builds, for each posible parameter set, a model which is evaluated on the cross validation set.
+The grid search builds, for each possible parameter set, a model which is evaluated on the cross validation set.
 The highest scoring model is tested with the test set.
@@
   \hline
-  harming anotherly &fight, shoot, invite, harm, commend, chase, seem, favour, reconstruct, pitch, request, inconvenience, redress, hitch, air, slow, disarm, strive, despoil, pique, tote, halt, bit, implicate\\
+  harming another &fight, shoot, invite, harm, commend, chase, seem, favour, reconstruct, pitch, request, inconvenience, redress, hitch, air, slow, disarm, strive, despoil, pique, tote, halt, bit, implicate\\
   \hline
@@
 
-The frames in table \ref{exframes} are frames induced by model 1 and are meaningfull in the sense that they consist of clusters of verbs that seem to have a similar meaning.
-Nontheless, in \textit{harming anotherly} there are verbs which would be better left out.
+The frames in table \ref{exframes} are frames induced by model 1 and are meaningful in the sense that they consist of clusters of verbs that seem to have a similar meaning.
+Nonetheless, in \textit{harming another} there are verbs which would be better left out.
 They are assigned this frame though because they occurred in company of the same arguments often.
@@
 or object.
-More advanced models might take better advantage of the various kinds of arguments
-in the verbargs dataset and their relation to one another.
+More advanced models might use detailed syntactic context to make more fine-grained
+distinctions between syntactic contexts.
 For example, you could be glean some semantic information about the relationship between
 verbs and prepositional objects by looking at the preposition that mediates them: 
-That you ''swim \emph{in} a lake'' versus ``ice skate \emph{on} a lake'' 
+That you ``swim \emph{in} a lake'' versus ``ice skate \emph{on} a lake'' 
 indicates that the relationship between swimming and lakes is different from the one between
 ice skating and lakes.
+
+More generally, VSO models don't take full advantage of the various kinds of argumens
+in the verbargs dataset. 
+As we have seen, only a fraction of verbs actually occur as part of a VSO subtree.
+By considering only VSOs, we may introduce some bias in the frames that we can induce,
+since frames with particular role configurationts (such as \emph{agent, patient}) may
+lend themselves better to transitive verbs.
+
+Finally, the models that we consider are essentially performing verb \emph{clustering}.
+This is a good first step, but a more sophisticated version of semantic frame induction
+would also be able to identify semantic \emph{roles}, and assign verb arguments to those
+roles. 
+That model 1 performs well on such a large, diverse dataset as Google syntactic ngrams is
+encouraging since such a corpus would be necessary to induce semantic roles on top of frames.
 
@@
 \section*{Who did what}
-We all tried to work as much as possible and neccesary on the project.
+We all tried to work as much as possible and necessary on the project.
 Bill had a leading role in building the models.
@@
 Jacob implemented frame coherency and Eli frame correctness.
-Everybody ran some experiments and Jacob is still running grid search (made a big estimation error in cost of gridsearch).
+Everybody ran some experiments and Jacob is still running grid search (made a big estimation error in cost of grid search).
 Any section is written by the one who implemented this particular part.

### 2015-01-05 Paper/paperN.tex
slight mod in who did what and some sentences rephrased

--- 2015-01-05 Paper/paperN.tex
@@
 \end{tabular}
+\caption{Frame examples}
 \label{exframes}
-\caption{Frame examples}
 \end{table}
@@
 \section{Discussion}
-As table \ref{results} show, coherency  improved significantly, whereas the frame correctness did not so much.
+As table \ref{results} shows, coherency  improved significantly, whereas the frame correctness did not so much.
 But the frames induced by model 0 do not cover all verbs, actually only 3 verbs are assigned to a frame.
@@
 
-The frames in table \ref{exframes} are frames induced by model 1 and are meaningful in the sense that they consist of clusters of verbs that seem to have a similar meaning.
+Table \ref{exframes} showes some frames induced by model 1 and are meaningful in the sense that they primarily consist of clusters of verbs that seem to have a similar meaning.
 Nonetheless, in \textit{harming anotherly} there are verbs which would be better left out.
@@
 they are the only verb assigned to a frame.
-Other verbs like \textit{(say, get, find, bring, make, see, ask, take, have, mean, use, like, hear, understand, afford, help, call, know, give, do, tell, find)} also get assigned a complete frame.
-This is most likely caused by the fact that these verbs can have a wide range of arguments, and are in the sense of meaning-of-a-verb by nouns it is encountered with, sort of meaningless.
+Other verbs like \textit{say, get, find, bring, make, see, ask, take, have, mean, use, like, hear, understand, afford, help, call, know, give, do, tell, find} also get assigned a complete frame.
+This is most likely caused by the fact that these verbs can have a wide range of arguments, and are in the sense of meaning-of-a-verb-by-nouns-it-is-encountered-with, sort of meaningless.
 This is again a weakness of the model, but could possibly be diminished with more data.
@@
 Any section is written by the one who implemented this particular part.
-The rest of the sections are composed of bits of everybody.
+The rest of the sections are composed of bits of everybody, but most important and precise work is done by Bill.
 

### 2015-01-05 Paper/paperN.tex

--- 2015-01-05 Paper/paperN.tex
@@
 
-The FrameNet project \citep{framenet} is an ongoing manual effort to define frames which could be mapped onto text to give a semantic representation.
+The FrameNet project \citep{FrameNet} is an ongoing manual effort to define frames which could be mapped onto text to give a semantic representation.
 But with the increasing amount of digital information, not to mention the inherent tediousness of building such a resource one word at a time, the prospect of (partially or completely) automating semantic frame induction is enticing.
@@
 Hence the broader meaning is latent.
-To evaluate our models we use two metrics, one of which uses framenet data to check whether the induced frames are similar to clusters of verbs in framenet, the other to check whether the resulting frames are coherent, i.e.
+To evaluate our models we use two metrics, one of which uses FrameNet data to check whether the induced frames are similar to clusters of verbs in FrameNet, the other to check whether the resulting frames are coherent, i.e.
 whether the found clusters are not completely random.
@@
 We based our work on two papers: \textit{`Inducing a semantically annotated lexicon via em-based clustering.'} by \citeauthor{rooth1999} and \textit{`Learning frames from text with an unsupervised latent variable model.'} by \citeauthor{oconnor2013}.
-In the first article clustering is realized by applying expectation maximization on a simple co-occurance model.
+In the first article clustering is realized by applying expectation maximalization on a simple co-occurance model.
 This model produces frames in the form of two distributions, one for the predicate, a distribution over verbs, and one for the arguments, a nouns.
@@
 The second paper covers two additional models, of which we implemented one.
-This model differs from the baseline model by introducing the assumption that a document generates sentences frame a restricted set of frames.
+This model differs from the baseline model by introducing the assumption that a document generates sentences from a restricted set of frames.
 This assumption is justified (as in latent Dirichlet allocation) \cite{blei2003} by the intuition that documents generally have a limited number of topics and thus use a proper subset of the frames.
@@
 
-A syntactic-ngram is a $k$-word rooted subtree of some sentence.
+A syntactic-ngram is a $k$-word rooted sub-tree of some sentence.
 Google syntactic-ngrams is a corpus of ngrams extracted from 3.5 million English language 
@@
 
-The $\alpha$ and $\beta$ hyperparameters in model 1 are known  to be hard to determine \citep{oconnor2013}, and therefore need to be experimentally optimized for our specific problem.
+The $\alpha$ and $\beta$ hyper-parameters in model 1 are known  to be hard to determine \citep{oconnor2013}, and therefore need to be experimentally optimized for our specific problem.
 We used an expensive, but easy to implement grid search to determine the best values for $\alpha$ and $\beta$.
@@
 
-%Frame correctness: for the top 25 most probable verbs per frame $TV$ and framenet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
+%Frame correctness: for the top 25 most probable verbs per frame $TV$ and FrameNet classes of verbs $FN$: \[\frac{2|TV\cap FN|}{|TV|+|FN|}\]
 \section{Results}
@@
 the parameters are guessed and therefor probably not optimal.
-(Since gridsearchis more expensive than planned for the actual results are still in progress.) In this experiment the frames were put on $200$, $\alpha$ and $\beta$ both on $0.5$.\\
+(Since grid-search is more expensive than planned for the actual results are still in progress.) In this experiment the frames were put on $200$, $\alpha$ and $\beta$ both on $0.5$.\\
 \begin{table}[h]
+\centering
 \begin{tabular}{|l||c|c|}
   \hline
-  &dicesim&coherencey\\
+  &dicesim&coherency\\
   \hline
@@
 
-More generally, VSO models don't take full advantage of the various kinds of argumens
+More generally, VSO models don't take full advantage of the various kinds of arguments
 in the verbargs dataset. 
@@
 By considering only VSOs, we may introduce some bias in the frames that we can induce,
-since frames with particular role configurationts (such as \emph{agent, patient}) may
+since frames with particular role configurations (such as \emph{agent, patient}) may
 lend themselves better to transitive verbs.
@@
 \section{Conclusion}
+Model 1 did find clusters of verbs of which the meaning can be covered by 1 predicate.
+Although the induced frames have often vague or broad meaning the approach works well if data is abundant.
+The improvement of model 1 on model 0 has a significant effect and implicates even better results can be acquired by further improvements.
+The kind of clustering done by these models, with opposites assigned to the same frame, can be useful for automatic stock trading systems if implemented with sentiment analysis to split on opposites.
+The frames are too vague to use for summarizations though.
 
@@
 Jacob implemented frame coherency and Eli frame correctness.
-Everybody ran some experiments and Jacob is still running grid search (made a big estimation error in cost of grid search).
+Everybody ran some experiments and Jacob is still running grid search (made a big estimation error in cost of grid-search).
 Any section is written by the one who implemented this particular part.

### 2015-01-11 Paper/paperN.tex
paper with gridsearch results

@@
 \section{Results}
-These results are experimental, i.e.
-the parameters are guessed and therefor probably not optimal.
-(Since grid-search is more expensive than planned for the actual results are still in progress.) In this experiment the frames were put on $200$, $\alpha$ and $\beta$ both on $0.5$.\\
+Grid search found the following parameter sets for the 2 measures. 
+\begin{itemize}
+  \item Best coherency with 100 frames - $\alpha$: 0.5 - $\beta$: 0.5
+  \item Best accuracy with 200 frames - $\alpha$: 2 - $\beta$: 0.5
+  \item Best both with 150 frames - $\alpha$: 0.1 - $\beta$: 0.5
+\end{itemize}
+The results on the testset are displayed in table \ref{results}.
+As this table shows, model 1 performs better in every case.
+The reslts are coherent with the above, but differences between parameter sets on model 1 are small.
+
  \begin{table}[h]
@@
   \hline
-  &dicesim&coherency\\
+  &accuracy&coherency\\
   \hline
   \hline
-  model 0& 0.28&19\%  \\
+  model 0 F=100 $\alpha$=.5&0.2853 & 27.12\%  \\
   \hline
-  model 1&0.29 &71\%  \\
+  model 1 F=100 $\alpha$=.5 $\beta$=.5& 0.3053 & 87.38\%  \\
+  \hline
+  model 0 F=150 $\alpha$=.1&0.2857 & 0.63\%  \\
+  \hline
+  model 1 F=150 $\alpha$=.1 $\beta$=.5& 0.3150 & 87.30\%  \\
+  \hline
+  model 0 F=200 $\alpha$=.5&0.2857 & 46.61\%  \\
+  \hline
+  model 1 F=200 $\alpha$=.5 $\beta$=.5&  0.3151& 87.74\%  \\
   \hline
@@
 \section{Discussion}
-As table \ref{results} show, coherency  improved significantly, whereas the frame correctness did not so much.
-But the frames induced by model 0 do not cover all verbs, actually only 3 verbs are assigned to a frame.
-It is not clear why this happens, but this are still only experimental results.
-Since there are 200 frames it is obvious that the coherency is so low.
-Other experiments have shown that it is possible to cluster with model 0 though.
+As table \ref{results} shows, coherency  improved significantly, whereas the frame accuracy only marginally.
+Furthermore note that $\beta$ has the same value in each parameter set.
+In Model 1 a higher $\beta$ argues for fewer verbs per frame, with this in mind one could argue that this particular value for $\beta$ is direct resultof the number of verbs in our data.
+So in this case, a low $\beta$ indicates a skewed distribution of verbs over frames.
+This is intuitively correct, since some broader meanings can be expressed by many verbs, while others only by a few.
+Furthermore the results are approximately the same as \citeauthor{oconnor2013} found.
 
